### 2018-07-29 other_R_code/article_selection_process.Rnw
write up results

\documentclass{article}

\begin{document}

We only have access to a big data set via boolean search.

Sub-sets of the data set returned by a single key word on a single day are large.For example for the single search term `election' for the single day of 1 August 1868 returns 1982 articles. The search term `riot' for the same day (close to the 1868 General Election) returns 360 articles, 228 of which do not also contain the word election.

With even a small number of search terms it quicly becomes impractical to examine all the documents even for a single day.

Following King et al we define
$S$ - the search set of all documents in the British Newspaper Archive
$T$ - the target set of all documents in the British Newspaper Archive which are about election violence
$R$ - a reference set of documents which are about election violence

The task is to identify $T$ from $S$ in a form where $T$ can be

It is trivial to define an algorithm which obtains a subset of $S$ which contains $T$, because $S \subseteq S$ and $T \subset S$. Algorithms which aim to maximise the chances of obtaining all of $T$ will tend to return $S$.

Our task is to find a good method for returning $T$ from $S$ in a form which we can analyse. By a \textit{good} method we mean a method which returns a greater proportion of $T$, and a greater ratio of $T$ to $\neg T$ than alternative methods. The main alternative method is manual searching by historians.

\section{Keyword Identification}
How difficult is it to find search terms which return all of

\end{document}

### 2018-07-29 other_R_code/article_selection_process.tex
write up results

\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

We only have access to a big data set via boolean search.

Sub-sets of the data set returned by a single key word on a single day are large.For example for the single search term `election' for the single day of 1 August 1868 returns 1982 articles. The search term `riot' for the same day (close to the 1868 General Election) returns 360 articles, 228 of which do not also contain the word election.

With even a small number of search terms it quicly becomes impractical to examine all the documents even for a single day.

Following King et al we define
$S$ - the search set of all documents in the British Newspaper Archive
$T$ - the target set of all documents in the British Newspaper Archive which are about election violence
$R$ - a reference set of documents which are about election violence

The task is to identify $T$ from $S$ in a form where $T$ can be

It is trivial to define an algorithm which obtains a subset of $S$ which contains $T$, because $S \subseteq S$ and $T \subset S$. Algorithms which aim to maximise the chances of obtaining all of $T$ will tend to return $S$.

Our task is to find a good method for returning $T$ from $S$ in a form which we can analyse. By a \textit{good} method we mean a method which returns a greater proportion of $T$ than alternative methods, and a greater ratio of $T$ to $\neg T$

\end{document}

### 2018-07-29 other_R_code/firststage_code.R

@@ -25,18 +25,98 @@ train<-quanteda::corpus(sets$training[,c("fakeid", "ocr", "EV_article")], text_f
 test<-quanteda::corpus(sets$test[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
 
 #Preprocess corpus and create DFM (without n-grams); preprocessing choices can be adapted in function
-train_nograms_dfm<-preprocess_corpus(train, stem=FALSE)
-test_nograms_dfm<-preprocess_corpus(test, stem=FALSE)
+train_nograms_dfm<-preprocess_corpus(train, stem=FALSE, min_termfreq = 20, min_docfreq = 5)
+test_nograms_dfm<-preprocess_corpus(test, stem=FALSE, min_termfreq = 20, min_docfreq = 5)
 
 #Preprocess corpus and create DFM (with specific n-grams); preprocessing choices can be adapted in function
 ev_grams<-list(c('election','riot'),c('election','disturbance'),c('election','incident'))
 
-train_grams_dfm<-preprocess_sgrams(train, wseq=ev_grams, stem=FALSE)
-test_grams_dfm<-preprocess_sgrams(test, wseq=ev_grams, stem=FALSE)
+train_grams_dfm<-preprocess_sgrams(train, wseq=ev_grams, stem=FALSE, min_termfreq = 20, min_docfreq = 5)
+test_grams_dfm<-preprocess_sgrams(test, wseq=ev_grams, stem=FALSE, min_termfreq = 20, min_docfreq = 5)
 
 #Extract keywords from naive bayes classifier run on training dfm
 kw_nograms<-nb_keywords(train_nograms_dfm, classvar="EV_article")
-head(kw_nograms, 10)
+head(kw_nograms, 50)
+tail(kw_nograms, 50)
 
 kw_grams<-nb_keywords(train_grams_dfm, classvar="EV_article")
 head(kw_grams, 10)
+tail(kw_grams, 50)
+
+head(train_grams_dfm[,"telegram"]==1)
+
+riot_dfm<-quanteda::dfm_(train_grams_dfm, "riot")
+as.logical(train_grams_dfm[,"riot"]==1)
+quanteda::docvars(train_grams_dfm[as.logical(train_grams_dfm[,"elector"]==1),], "EV_article")
+
+
+
+
+##----King et al algorithm attempt----
+
[…]

### 2018-07-30 other_R_code/article_selection_process.Rnw
write up revisons

@@
 \section{Keyword Identification}
-How difficult is it to find search terms which return all of
+Note it is important to make keyword identification somewhat selective of $T$ from $S$ otherwise even very good stage 2 \& 3 selection processes the false positives will overwhelm the true positives.
+
+Algorithm:
+\begin{enumerate}
+  \item use classifier on $R$ and $S$ to identify two lists of keywords
+  \item generate probability from classifier parameters
+  \item add to keyword list based on probability
+\end{enumerate}
 

### 2018-07-30 R/firststage_functions.R
adjusting keyword retrieval function

@@ -72,7 +72,7 @@ nb_keywords<-function(training, classvar){
   #' @param training Training data feature matrix
   #' @param classvar Classification variable name, entered as string
   #' @export
-  nb<-quanteda::textmodel_nb(training,quanteda::docvars(training, classvar))
+  nb<-quanteda::textmodel_nb(training,quanteda::docvars(training, classvar), distribution="Bernoulli")
   post<-as.data.frame(t(nb$PcGw))
   post<-tibble::rownames_to_column(post)
   post$id<-seq.int(nrow(post))

### 2018-07-30 R/firststage_functions.R
get first stage process working

@@ -67,12 +67,12 @@ preprocess_sgrams<-function(the_corpus, wseq, stem=TRUE, min_termfreq=2, min_doc
   the_dfm
 }
 
-nb_keywords<-function(training, classvar){
+nb_keywords<-function(training, classvar, distribution="Bernoulli"){
   #' Train a naive bayes classifier and extract keywords as data.frame object ordered by most predictive word of class on top (wrapper function around Quanteda commands). The returned data.frame has three columns: word, 0(=posterior prob of word indicating that document in classvar==0), 1(=posterior prob of word predicting word indicating that document in classvar==1), and id.
   #' @param training Training data feature matrix
   #' @param classvar Classification variable name, entered as string
   #' @export
-  nb<-quanteda::textmodel_nb(training,quanteda::docvars(training, classvar))
+  nb<-quanteda::textmodel_nb(training,quanteda::docvars(training, classvar), distribution=distribution)
   post<-as.data.frame(t(nb$PcGw))
   post<-tibble::rownames_to_column(post)
   post$id<-seq.int(nrow(post))

### 2018-07-30 R/text_analysis_patrick.R

@@ -39,7 +39,7 @@ check_sngrams<-function(toks, wseq, wseqc){
   print(grams)
 }
 
-nb_test<-function(training, testing, classvar){
+nb_test<-function(training, testing, classvar, distribution="Bernoulli"){
   #' Train a naive bayes classifier on a training dfm and asses its performance on a test dfm reporting test statistics (wrapper function aroudn Quanteda commands)
   #' @param training Training data frequency matrix
   #' @param testing Testing data frequency matrix

### 2018-07-30 other_R_code/firststage_code.R

@@ -35,21 +35,23 @@ train_grams_dfm<-preprocess_sgrams(train, wseq=ev_grams, stem=FALSE, min_termfre
 test_grams_dfm<-preprocess_sgrams(test, wseq=ev_grams, stem=FALSE, min_termfreq = 20, min_docfreq = 5)
 
 #Extract keywords from naive bayes classifier run on training dfm
-kw_nograms<-nb_keywords(train_nograms_dfm, classvar="EV_article")
-head(kw_nograms, 50)
+kw_nograms<-nb_keywords(train_nograms_dfm, classvar="EV_article", distribution = "multinomial")
+head(kw_nograms, 10)
 tail(kw_nograms, 50)
 
-kw_grams<-nb_keywords(train_grams_dfm, classvar="EV_article")
+kw_grams<-nb_keywords(train_grams_dfm, classvar="EV_article", distribution = "multinomial")
 head(kw_grams, 10)
 tail(kw_grams, 50)
 
-head(train_grams_dfm[,"telegram"]==1)
-
 riot_dfm<-quanteda::dfm_(train_grams_dfm, "riot")
-as.logical(train_grams_dfm[,"riot"]==1)
 quanteda::docvars(train_grams_dfm[as.logical(train_grams_dfm[,"elector"]==1),], "EV_article")
 
+dfm_boolean<-quanteda::dfm_weight(train_grams_dfm, scheme="boolean")
 
+kw_boolean<-nb_keywords(train_nograms_dfm, classvar="EV_article", distribution="Bernoulli")
+head(kw_boolean, 10)
+tail(kw_nograms, 50)
+quanteda::textmodel_nb(dfm_boolean, quanteda::docvars(dfm_boolean, "EV_article"), distribution="multinomial")
 
 
 ##----King et al algorithm attempt----
@@ -120,3 +122,6 @@ sum((ev_dfm[,"mr"]==0 & ev_dfm[,"one"]==0 & ev_dfm[,"day"]==0 & ev_dfm[,"riot"]=
 d2<-quanteda::dfm_subset(ev_dfm, ev_dfm[,"mr"]==0 & ev_dfm[,"one"]==0 & ev_dfm[,"day"]==0 & ev_dfm[,"riot"]==0 & ev_dfm[,"police"]==0 & ev_dfm[,"last"]==0 & ev_dfm[,"night"]==0)
 
 ev_docfreq<-quanteda::docfreq(d2)
+
[…]

### 2018-07-30 R/text_analysis.R
update split_corpus

@@ -44,11 +44,11 @@ split_dfm <- function(dfm, n_train){
 
 split_corpus<-function(the_corpus, n_train, min_termfreq=2, min_docfreq=2,
                        remove_punct=TRUE, remove_numbers=TRUE, remove_hyphens=TRUE,
-                       dfm_tfidf=FALSE){
+                       dfm_tfidf=FALSE, stem=TRUE){
   #' Preprocess a text corpus and divide it into training and testing sets based on number of training items.
   #' Note: it is more efficient to preprocess and split separately, especially if running in a loop.
   #' @export
-  the_dfm <- quanteda::dfm(the_corpus, stem=TRUE, remove=quanteda::stopwords("english"), remove_punct=remove_punct, remove_numbers=remove_numbers, remove_hyphens=remove_hyphens)
+  the_dfm <- quanteda::dfm(the_corpus, stem=stem, remove=quanteda::stopwords("english"), remove_punct=remove_punct, remove_numbers=remove_numbers, remove_hyphens=remove_hyphens)
   the_dfm <- quanteda::dfm_trim(the_dfm, min_termfreq=min_termfreq, min_docfreq = min_docfreq)
   if(dfm_tfidf){
     the_dfm<-quanteda::dfm_tfidf(the_dfm)

### 2018-07-30 R/text_analysis.R
debug

@@ -160,7 +160,7 @@ get_classified_docs <- function (){
                                ev_docs)
   the_corpus$general_corpus<-1
 
-  the_corpus<-the_corpus[,c("id", "title", "description", "type", "page", "publication_date", "word_count", "ocr", "election_article", "EV_article", "corpus_election", "electoral_nature", "violent_nature", "candidate_document_id")]
+  the_corpus<-the_corpus[,c("id", "title", "description", "type", "page", "publication_date", "word_count", "ocr", "election_article", "EV_article", "just_election", "corpus_election", "electoral_nature", "violent_nature", "candidate_document_id")]
   the_corpus <- tibble::rowid_to_column(the_corpus, "fakeid")
 
   the_corpus

### 2018-07-30 other_R_code/article_selection_process.Rnw
further result classification write-up

@@
 \begin{document}
+<<loadpackages, echo=FALSE, warning=FALSE, message=FALSE>>=
+library(durhamevp)
+library(tidyverse)
+@
 
@@
 
+\section{The data}
+<<loaddata, cache=TRUE, tidy=TRUE>>=
+classdocs<-durhamevp::get_classified_docs()
+classified_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
+classified_dfm <- preprocess_corpus(classified_corpus, stem=FALSE, min_termfreq=20, min_docfreq = 10)
+@
+
+In the data there are \Sexpr{nrow(classdocs)} cases:
+\begin{itemize}
+  \item \textbf{\Sexpr{sum(classdocs$election_article==0)}} non-election articles.
+  \item \textbf{\Sexpr{sum(classdocs$EV_article==1)}} election violence articles.
+  \item \textbf{\Sexpr{sum(classdocs$just_election==1)}} election (but not violent) articles.
+\end{itemize}
+
 \section{Keyword Identification}
@@
 \end{enumerate}
+<<findkeywords>>=
+keywords<-nb_keywords(classified_dfm, "EV_article")
+knitr::kable(head(keywords, 20))
+@
+
+\section{Refinement Using Description}
+
+<<usingdescription>>=
+description_corpus<-quanteda::corpus(classdocs[,c("fakeid", "description", "EV_article")], text_field = "description")
+description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)
+
+both_dfms<-split_dfm(description_dfm, n_train = 1500)
+nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
+prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
+pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
+res<-data.frame(predict_nb=pred_nb, prob_nb)
+names(res)<-c("predict_nb", "prob_notev", "prob_ev")
+assess_classification(organise_results(both_dfms$test, res)) %>%
+  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
+  kable()
+@
+
+\section{Refinement Using OCR}
+
+<<usingocr>>=
+ocr_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
+ocr_dfm <- preprocess_corpus(ocr_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)
+
+both_dfms<-split_dfm(ocr_dfm, n_train = 1500)
+nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
+prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
+pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
+res<-data.frame(predict_nb=pred_nb, prob_nb)
+names(res)<-c("predict_nb", "prob_notev", "prob_ev")
+assess_classification(organise_results(both_dfms$test, res)) %>%
+  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
+  kable()
+@
 

### 2018-07-31 other_R_code/article_selection_process.Rnw
Further development of alogorithm description

--- 2018-07-30 other_R_code/article_selection_process.Rnw
@@
 
-With even a small number of search terms it quicly becomes impractical to examine all the documents even for a single day.
+With even a small number of search terms it quickly becomes impractical to examine all the documents even for a single day.
 
@@
 \end{enumerate}
+<<findkeywords>>=
+keywords<-nb_keywords(classified_dfm, "EV_article")
+knitr::kable(head(keywords, 20))
+@
 
+\section{Refinement Using Description}
+
+<<usingdescription, warning=FALSE>>=
+description_corpus<-quanteda::corpus(classdocs[,c("fakeid", "description", "EV_article")], text_field = "description")
+description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)
+
+both_dfms<-split_dfm(description_dfm, n_train = 1000)
+
+nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
+prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
+pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
+res<-data.frame(predict_nb=pred_nb, prob_nb)
+names(res)<-c("predict_nb", "prob_notev", "prob_ev")
+assess_classification(organise_results(both_dfms$test, res)) %>%
+  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
+  kable()
+@
+
+Note: this way of creating the dfm does make dfms terms equal because one overall dfm is created and then it is subset. You can see below that the number of features in both dfms is the same:
+
+<<equaldfms>>=
+print(both_dfms$train)
+print(both_dfms$test)
+@
+
+\section{Refinement Using OCR}
+
+<<usingocr>>=
+ocr_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
+ocr_dfm <- preprocess_corpus(ocr_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)
+
+both_dfms<-split_dfm(ocr_dfm, n_train = 1000)
+nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
+prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
+pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
+res<-data.frame(predict_nb=pred_nb, prob_nb)
+names(res)<-c("predict_nb", "prob_notev", "prob_ev")
+assess_classification(organise_results(both_dfms$test, res)) %>%
+  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
+  kable()
+@
+
+\section{King Algorithm: implementation}
+
+\subsection{Incrementally Define $R$ and $S$}
+$R$ is our reference set. [King suggestions: could define $R$ based on one simple keyword search].
+\subsubsection{Intermediate step}
+Take keywords in $R$, $K_R$, ranked by simple statistic such as document frequency or frequency-inverse document frequency.
+User examines elements of $K_R$ apart from those used to define the set and chooses some keywords to define $Q_S$, which in turn generates a definition for $S$ so that we can run the rest of the algorithm.
+The user can continue to add keywords from $K_R$ into the final desired query $Q_RT$.
+This step also mitigates the issue of how to define a search set in large data sets that do not fit into memory all at once or may not even be able to be retrieved all at onece. is the BNA.
+
+\subsection{Partition $S$ into $T$ and $S \backslash T$}
+
+\subsection{Discovering Keywords to Classify Documents}
+
+\subsection{Human Input and Human-Computer Iteration}
 \end{document}

### 2018-07-31 R/text_analysis.R
add results column as a parameter to organise results function

@@ -81,10 +81,10 @@ my_wordscores<-function(train, test){
   pred_wordscores
 
 }
-organise_results <- function (testset, pred_nb, pred_aff=NULL, pred_wordscores=NULL){
+organise_results <- function (testset, pred_nb, pred_aff=NULL, pred_wordscores=NULL, res_col="EV_article"){
   #' @export
-  this_res<-dplyr::as.tbl(data.frame(actual=quanteda::docvars(testset, "EV_article"),
-                              actual_f=factor(quanteda::docvars(testset, "EV_article")),
+  this_res<-dplyr::as.tbl(data.frame(actual=quanteda::docvars(testset, res_col),
+                              actual_f=factor(quanteda::docvars(testset, res_col)),
                               nb_ev_cat=pred_nb$predict_nb,
                               nb_ev_prob=pred_nb$prob_ev,
                               nb_notev_prob=pred_nb$prob_notev

### 2018-07-31 other_R_code/article_selection_process.Rnw
Further development of classification write-up

@@
 classdocs<-durhamevp::get_classified_docs()
-classified_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
-classified_dfm <- preprocess_corpus(classified_corpus, stem=FALSE, min_termfreq=20, min_docfreq = 10)
+# just some candidate document for speed/space reasons
+unclassdocs<-durhamevp::get_candidate_documents(3000:6000)
+
 @
@@
 <<findkeywords>>=
+classified_corpus<-quanteda::corpus(classdocs[,c("fakeid", "ocr", "EV_article")], text_field = "ocr")
+classified_dfm <- preprocess_corpus(classified_corpus, stem=FALSE, min_termfreq=20, min_docfreq = 10)
+
 keywords<-nb_keywords(classified_dfm, "EV_article")
@@
   kable()
+
+description_corpus<-quanteda::corpus(classdocs[,c("fakeid", "description", "EV_article")], text_field = "description")
+description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)
+
+both_dfms<-split_dfm(description_dfm, n_train = 1000)
+
 @
@@
 print(both_dfms$test)
+@
+
+\subsection{More realistic use case}
+Exclude non-election cases which would not be returned by our keywords:
+
+<<usingdescriptionrealistic, warning=FALSE>>=
+description_corpus<-quanteda::corpus(classdocs[classdocs$election_article==1,c("fakeid", "description", "EV_article")], text_field = "description")
+description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)
+
+both_dfms<-split_dfm(description_dfm, n_train = 1000)
+
+nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
+prob_nb<-predict(nb, newdata = both_dfms$test, type="probability")
+pred_nb<-data.frame(predict(nb, newdata = both_dfms$test, type="class"))
+res<-data.frame(predict_nb=pred_nb, prob_nb)
+names(res)<-c("predict_nb", "prob_notev", "prob_ev")
+assess_classification(organise_results(both_dfms$test, res)) %>%
+  filter(rowname %in% c("Precision", "Recall", "F1")) %>%
+  kable()
+
+description_corpus<-quanteda::corpus(classdocs[,c("fakeid", "description", "EV_article")], text_field = "description")
+description_dfm <- preprocess_corpus(description_corpus, stem=FALSE, min_termfreq=5, min_docfreq = 2)
+
+both_dfms<-split_dfm(description_dfm, n_train = 1000)
+
 @
@@
 \subsection{Partition $S$ into $T$ and $S \backslash T$}
+To partition $S$ into $T$ and $S \backslash T$, we first define a `training' set by sampling from $S$ and $R$.
+Since $R$ is typically much smaller than $S$ our test set for our classifiers is all all of $S$, we often use the entire $R$ set and a sample of $S$ as our training set.
+<<fitkingtrain>>=
+R <- classdocs[classdocs$EV_article==1,]
+R$R <- 1
+R$in_sample<-1
+S <- unclassdocs
+S$R <- 0
+
+n_sample_S <- 1000
+S$in_sample<-0
+S$in_sample[sample(1:nrow(S), n_sample_S)]<-1
+
+R_S <- dplyr::bind_rows(R, S)
+R_S$fakeid<-1:nrow(R_S)
+
+R_S_corpus<-quanteda::corpus(R_S[,c("fakeid", "ocr", "in_sample", "R")], text_field = "ocr")
+R_S_dfm <- preprocess_corpus(R_S_corpus, stem=FALSE, min_termfreq=20, min_docfreq = 20)
+
+king_train_dfm<-quanteda::dfm_subset(R_S_dfm, quanteda::docvars(R_S_dfm, "in_sample")==1)
+king_nb <- quanteda::textmodel_nb(king_train_dfm, y=quanteda::docvars(king_train_dfm, "R"), prior="uniform")
+keywords<-nb_keywords(king_train_dfm, "R")
+knitr::kable(head(keywords, 20))
+@
+
+After fitting the classifiers, we use the estimated parameters to generate predicted probabilities of $R$ membership for all documents in $S$.
+Of cource, all the search set documents in fact fall within $S$ but our interest in in learning from the \textit{mistakes} these classifiers make.
+
+<<learnclassmistakes>>=
+S_dfm <- quanteda::dfm_subset(R_S_dfm, quanteda::docvars(R_S_dfm, "R")==0)
+quanteda::docvars(S_dfm, "T")<-predict(king_nb, newdata = S_dfm, type="class")
+@
 
 \subsection{Discovering Keywords to Classify Documents}
+After partitioning $S$ into estimated target $T$ and non-target set $S \backslash T$, we must find and rank keywords which best discriminate $T$ and $S \backslash T$.
+King does this in three stages:
+\subsubsection{identify keywords in S}
 
+\subsubsection{sort them into those that predict each of the two steps}
+
+My suggestion here is simply to use binary\_dfm
+
+<<>>=
+S_dfm_binary<-quanteda::dfm_weight(S_dfm, scheme="boolean")
+king_stage2 <- quanteda::textmodel_nb(S_dfm, y=quanteda::docvars(S_dfm_binary, "T"), distribution="Bernoulli")
+king_stage2 <- nb_keywords(S_dfm, "T")
+knitr::kable(head(king_stage2, 30))
+
+knitr::kable(tail(king_stage2, 30))
+@
+
+\subsection{rank them by degree of discriminatory power}
+We already seem to have done this in the step above
 \subsection{Human Input and Human-Computer Iteration}
+Now present
+
 \end{document}

### 2018-07-31 R/database_interactivity.R
commit

@@ -385,6 +385,52 @@ get_user_mode <- function(user_id="all"){
   profiles
 }
 
+get_archivesearches<-function(archive_search_id="all"){
+  #' Returns the crawler search table
+  #'
+  #' @param archive_search_id archive_search id or ids to filter by.
+  #' @export
+
+  con <- manage_dbcons()
+
+  this_sql<-"SELECT * FROM portal_archivesearch" # base query
+
+  res<-build_where_condition("id", archive_search_id, this_sql, NULL)
+  res[["condition"]] <- paste(res[["condition"]], ";")
+  this_sql<-res[["condition"]]
+  interpolate_list <- res[["interpolate_list"]]
+  this_safe_sql<-DBI::sqlInterpolate(DBI::ANSI(), this_sql,
+                                     .dots = interpolate_list)
+  archivesearch<-DBI::dbGetQuery(con, this_safe_sql)
+
+
+
+  archivesearch
+}
+
+get_archivesearchresults<-function(archivesearchresults_id="all", archive_search_id="all"){
+  #' Returns the crawler search table
+  #'
+  #' @param archivesearch_id archive_search id or ids to filter by.
+  #' @export
+
+  con <- manage_dbcons()
+
+  this_sql<-"SELECT * FROM portal_archivesearchresult" # base query
+
+  res<-build_where_condition("id", archivesearchresults_id, this_sql, NULL)
+  res<-build_where_condition("archive_search_id", archive_search_id, res$condition, res$interpolate_list)
+  res[["condition"]] <- paste(res[["condition"]], ";")
+  this_sql<-res[["condition"]]
+  interpolate_list <- res[["interpolate_list"]]
+  this_safe_sql<-DBI::sqlInterpolate(DBI::ANSI(), this_sql,
+                                     .dots = interpolate_list)
+  archivesearch<-DBI::dbGetQuery(con, this_safe_sql)
+
+
+
+  archivesearch
+}
 set_user_mode <- function (user_id, new_mode){
   #' Sets user mode
   #'

### 2018-07-31 R/database_interactivity.R
help file ammendment

@@ -386,7 +386,7 @@ get_user_mode <- function(user_id="all"){
 }
 
 get_archivesearches<-function(archive_search_id="all"){
-  #' Returns the crawler search table
+  #' Returns the table of searches which have been passed to the crawler.
   #'
   #' @param archive_search_id archive_search id or ids to filter by.
   #' @export

### 2018-07-31 vignettes/search_data_structures.R
Automated documentation changes

@@ -1,0 +1,14 @@
+## ----setup, include = FALSE----------------------------------------------
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>"
+)
+library(durhamevp)
+
+## ----getarchivesearches, eval=TRUE---------------------------------------
+
+archivesearches<-get_archivesearches()
+
+knitr::kable(tail(archivesearches, 3))
+
+

### 2018-07-31 other_R_code/article_selection_process.tex

@@
 Our task is to find a good method for returning $T$ from $S$ in a form which we can analyse.
-By a \textit{good} method we mean a method which returns a greater proportion of $T$ than alternative methods, and a greater ratio of $T$ to $\neg T$
+By a \textit{good} method we mean a method which returns a greater proportion of $T$, and a greater ratio of $T$ to $\neg T$ than alternative methods.
+The main alternative method is manual searching by historians.
+
+\section{The data}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{classdocs} \hlkwb{<-} \hlstd{durhamevp}\hlopt{::}\hlkwd{get_classified_docs}\hlstd{()}
+\hlcom{# just some candidate document for speed/space reasons}
+\hlstd{unclassdocs} \hlkwb{<-} \hlstd{durhamevp}\hlopt{::}\hlkwd{get_candidate_documents}\hlstd{(}\hlnum{3000}\hlopt{:}\hlnum{6000}\hlstd{)}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
+
+In the data there are 1894 cases:
+\begin{itemize}
+  \item \textbf{703} non-election articles.
+  \item \textbf{769} election violence articles.
+  \item \textbf{422} election (but not violent) articles.
+\end{itemize}
+
+\section{Keyword Identification}
+Note it is important to make keyword identification somewhat selective of $T$ from $S$ otherwise even very good stage 2 \& 3 selection processes the false positives will overwhelm the true positives.
+
+Algorithm:
+\begin{enumerate}
+  \item use classifier on $R$ and $S$ to identify two lists of keywords
+  \item generate probability from classifier parameters
+  \item add to keyword list based on probability
+\end{enumerate}
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{classified_corpus}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{corpus}\hlstd{(classdocs[,}\hlkwd{c}\hlstd{(}\hlstr{"fakeid"}\hlstd{,} \hlstr{"ocr"}\hlstd{,} \hlstr{"EV_article"}\hlstd{)],} \hlkwc{text_field} \hlstd{=} \hlstr{"ocr"}\hlstd{)}
+\hlstd{classified_dfm} \hlkwb{<-} \hlkwd{preprocess_corpus}\hlstd{(classified_corpus,} \hlkwc{stem}\hlstd{=}\hlnum{FALSE}\hlstd{,} \hlkwc{min_termfreq}\hlstd{=}\hlnum{20}\hlstd{,} \hlkwc{min_docfreq} \hlstd{=} \hlnum{10}\hlstd{)}
+
+\hlstd{keywords}\hlkwb{<-}\hlkwd{nb_keywords}\hlstd{(classified_dfm,} \hlstr{"EV_article"}\hlstd{)}
+\hlstd{knitr}\hlopt{::}\hlkwd{kable}\hlstd{(}\hlkwd{head}\hlstd{(keywords,} \hlnum{20}\hlstd{))}
+\end{alltt}
+\end{kframe}
+\begin{tabular}{l|l|r|r|r}
+\hline
+  & rowname & 0 & 1 & id\\
+\hline
+12299 & roughly & 0.0277149 & 0.9722851 & 12299\\
+\hline
+12300 & riotously & 0.0315492 & 0.9684508 & 12300\\
+\hline
+12280 & smashing & 0.0336163 & 0.9663837 & 12280\\
+\hline
+12298 & bicycle & 0.0347548 & 0.9652452 & 12298\\
+\hline
+12302 & pontypool & 0.0366149 & 0.9633851 & 12302\\
+\hline
+11621 & smashed & 0.0468791 & 0.9531209 & 11621\\
+\hline
+12303 & bedminster & 0.0499935 & 0.9500065 & 12303\\
+\hline
+12279 & p.c & 0.0528924 & 0.9471076 & 12279\\
+\hline
+12289 & roughs & 0.0548967 & 0.9451033 & 12289\\
+\hline
+12257 & rioters & 0.0579995 & 0.9420005 & 12257\\
+\hline
+12044 & stoned & 0.0585510 & 0.9414490 & 12044\\
+\hline
+12301 & abersychan & 0.0585510 & 0.9414490 & 12301\\
+\hline
+12304 & lofts & 0.0585510 & 0.9414490 & 12304\\
+\hline
+12295 & missile & 0.0611686 & 0.9388314 & 12295\\
+\hline
+11754 & supt & 0.0744892 & 0.9255108 & 11754\\
+\hline
+11959 & foley & 0.0744892 & 0.9255108 & 11959\\
+\hline
+11977 & missiles & 0.0776601 & 0.9223399 & 11977\\
+\hline
+9149 & staves & 0.0819225 & 0.9180775 & 9149\\
+\hline
+12094 & panes & 0.0835908 & 0.9164092 & 12094\\
+\hline
+12268 & terrell & 0.0835908 & 0.9164092 & 12268\\
+\hline
+\end{tabular}
+
+\end{knitrout}
+
+\section{Refinement Using Description}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{description_corpus}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{corpus}\hlstd{(classdocs[,}\hlkwd{c}\hlstd{(}\hlstr{"fakeid"}\hlstd{,} \hlstr{"description"}\hlstd{,} \hlstr{"EV_article"}\hlstd{)],} \hlkwc{text_field} \hlstd{=} \hlstr{"description"}\hlstd{)}
+\hlstd{description_dfm} \hlkwb{<-} \hlkwd{preprocess_corpus}\hlstd{(description_corpus,} \hlkwc{stem}\hlstd{=}\hlnum{FALSE}\hlstd{,} \hlkwc{min_termfreq}\hlstd{=}\hlnum{5}\hlstd{,} \hlkwc{min_docfreq} \hlstd{=} \hlnum{2}\hlstd{)}
+
+\hlstd{both_dfms}\hlkwb{<-}\hlkwd{split_dfm}\hlstd{(description_dfm,} \hlkwc{n_train} \hlstd{=} \hlnum{1000}\hlstd{)}
+
+\hlstd{nb}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{textmodel_nb}\hlstd{(both_dfms}\hlopt{$}\hlstd{train,} \hlkwc{y}\hlstd{=quanteda}\hlopt{::}\hlkwd{docvars}\hlstd{(both_dfms}\hlopt{$}\hlstd{train,} \hlstr{"EV_article"}\hlstd{),} \hlkwc{prior}\hlstd{=}\hlstr{"uniform"}\hlstd{)}
+\hlstd{prob_nb}\hlkwb{<-}\hlkwd{predict}\hlstd{(nb,} \hlkwc{newdata} \hlstd{= both_dfms}\hlopt{$}\hlstd{test,} \hlkwc{type}\hlstd{=}\hlstr{"probability"}\hlstd{)}
+\hlstd{pred_nb}\hlkwb{<-}\hlkwd{data.frame}\hlstd{(}\hlkwd{predict}\hlstd{(nb,} \hlkwc{newdata} \hlstd{= both_dfms}\hlopt{$}\hlstd{test,} \hlkwc{type}\hlstd{=}\hlstr{"class"}\hlstd{))}
+\hlstd{res}\hlkwb{<-}\hlkwd{data.frame}\hlstd{(}\hlkwc{predict_nb}\hlstd{=pred_nb, prob_nb)}
+\hlkwd{names}\hlstd{(res)}\hlkwb{<-}\hlkwd{c}\hlstd{(}\hlstr{"predict_nb"}\hlstd{,} \hlstr{"prob_notev"}\hlstd{,} \hlstr{"prob_ev"}\hlstd{)}
+\hlkwd{assess_classification}\hlstd{(}\hlkwd{organise_results}\hlstd{(both_dfms}\hlopt{$}\hlstd{test, res))} \hlopt{%>%}
+  \hlkwd{filter}\hlstd{(rowname} \hlopt{%in%} \hlkwd{c}\hlstd{(}\hlstr{"Precision"}\hlstd{,} \hlstr{"Recall"}\hlstd{,} \hlstr{"F1"}\hlstd{))} \hlopt{%>%}
+  \hlkwd{kable}\hlstd{()}
+\end{alltt}
+\end{kframe}
+\begin{tabular}{l|r|l}
+\hline
+rowname & value & model\\
+\hline
+Precision & 0.7842105 & naive bayes\\
+\hline
+Recall & 0.8370787 & naive bayes\\
+\hline
+F1 & 0.8097826 & naive bayes\\
+\hline
+\end{tabular}
+
+\begin{kframe}\begin{alltt}
+\hlstd{description_corpus}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{corpus}\hlstd{(classdocs[,}\hlkwd{c}\hlstd{(}\hlstr{"fakeid"}\hlstd{,} \hlstr{"description"}\hlstd{,} \hlstr{"EV_article"}\hlstd{)],} \hlkwc{text_field} \hlstd{=} \hlstr{"description"}\hlstd{)}
+\hlstd{description_dfm} \hlkwb{<-} \hlkwd{preprocess_corpus}\hlstd{(description_corpus,} \hlkwc{stem}\hlstd{=}\hlnum{FALSE}\hlstd{,} \hlkwc{min_termfreq}\hlstd{=}\hlnum{5}\hlstd{,} \hlkwc{min_docfreq} \hlstd{=} \hlnum{2}\hlstd{)}
+
+\hlstd{both_dfms}\hlkwb{<-}\hlkwd{split_dfm}\hlstd{(description_dfm,} \hlkwc{n_train} \hlstd{=} \hlnum{1000}\hlstd{)}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
+
+Note: this way of creating the dfm does make dfms terms equal because one overall dfm is created and then it is subset. You can see below that the number of features in both dfms is the same:
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlkwd{print}\hlstd{(both_dfms}\hlopt{$}\hlstd{train)}
+\end{alltt}
+\begin{verbatim}
+## Document-feature matrix of: 1,000 documents, 1,647 features (99.2% sparse).
+\end{verbatim}
+\begin{alltt}
+\hlkwd{print}\hlstd{(both_dfms}\hlopt{$}\hlstd{test)}
+\end{alltt}
+\begin{verbatim}
+## Document-feature matrix of: 894 documents, 1,647 features (99.2% sparse).
+\end{verbatim}
+\end{kframe}
+\end{knitrout}
+
+\subsection{More realistic use case}
+Exclude non-election cases which would not be returned by our keywords:
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{description_corpus}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{corpus}\hlstd{(classdocs[classdocs}\hlopt{$}\hlstd{election_article}\hlopt{==}\hlnum{1}\hlstd{,}\hlkwd{c}\hlstd{(}\hlstr{"fakeid"}\hlstd{,} \hlstr{"description"}\hlstd{,} \hlstr{"EV_article"}\hlstd{)],} \hlkwc{text_field} \hlstd{=} \hlstr{"description"}\hlstd{)}
+\hlstd{description_dfm} \hlkwb{<-} \hlkwd{preprocess_corpus}\hlstd{(description_corpus,} \hlkwc{stem}\hlstd{=}\hlnum{FALSE}\hlstd{,} \hlkwc{min_termfreq}\hlstd{=}\hlnum{5}\hlstd{,} \hlkwc{min_docfreq} \hlstd{=} \hlnum{2}\hlstd{)}
+
+\hlstd{both_dfms}\hlkwb{<-}\hlkwd{split_dfm}\hlstd{(description_dfm,} \hlkwc{n_train} \hlstd{=} \hlnum{1000}\hlstd{)}
+
+\hlstd{nb}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{textmodel_nb}\hlstd{(both_dfms}\hlopt{$}\hlstd{train,} \hlkwc{y}\hlstd{=quanteda}\hlopt{::}\hlkwd{docvars}\hlstd{(both_dfms}\hlopt{$}\hlstd{train,} \hlstr{"EV_article"}\hlstd{),} \hlkwc{prior}\hlstd{=}\hlstr{"uniform"}\hlstd{)}
+\hlstd{prob_nb}\hlkwb{<-}\hlkwd{predict}\hlstd{(nb,} \hlkwc{newdata} \hlstd{= both_dfms}\hlopt{$}\hlstd{test,} \hlkwc{type}\hlstd{=}\hlstr{"probability"}\hlstd{)}
+\hlstd{pred_nb}\hlkwb{<-}\hlkwd{data.frame}\hlstd{(}\hlkwd{predict}\hlstd{(nb,} \hlkwc{newdata} \hlstd{= both_dfms}\hlopt{$}\hlstd{test,} \hlkwc{type}\hlstd{=}\hlstr{"class"}\hlstd{))}
+\hlstd{res}\hlkwb{<-}\hlkwd{data.frame}\hlstd{(}\hlkwc{predict_nb}\hlstd{=pred_nb, prob_nb)}
+\hlkwd{names}\hlstd{(res)}\hlkwb{<-}\hlkwd{c}\hlstd{(}\hlstr{"predict_nb"}\hlstd{,} \hlstr{"prob_notev"}\hlstd{,} \hlstr{"prob_ev"}\hlstd{)}
+\hlkwd{assess_classification}\hlstd{(}\hlkwd{organise_results}\hlstd{(both_dfms}\hlopt{$}\hlstd{test, res))} \hlopt{%>%}
+  \hlkwd{filter}\hlstd{(rowname} \hlopt{%in%} \hlkwd{c}\hlstd{(}\hlstr{"Precision"}\hlstd{,} \hlstr{"Recall"}\hlstd{,} \hlstr{"F1"}\hlstd{))} \hlopt{%>%}
+  \hlkwd{kable}\hlstd{()}
+\end{alltt}
+\end{kframe}
+\begin{tabular}{l|r|l}
+\hline
+rowname & value & model\\
+\hline
+Precision & 0.9019608 & naive bayes\\
+\hline
+Recall & 0.7076923 & naive bayes\\
+\hline
+F1 & 0.7931034 & naive bayes\\
+\hline
+\end{tabular}
+
+\begin{kframe}\begin{alltt}
+\hlstd{description_corpus}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{corpus}\hlstd{(classdocs[,}\hlkwd{c}\hlstd{(}\hlstr{"fakeid"}\hlstd{,} \hlstr{"description"}\hlstd{,} \hlstr{"EV_article"}\hlstd{)],} \hlkwc{text_field} \hlstd{=} \hlstr{"description"}\hlstd{)}
+\hlstd{description_dfm} \hlkwb{<-} \hlkwd{preprocess_corpus}\hlstd{(description_corpus,} \hlkwc{stem}\hlstd{=}\hlnum{FALSE}\hlstd{,} \hlkwc{min_termfreq}\hlstd{=}\hlnum{5}\hlstd{,} \hlkwc{min_docfreq} \hlstd{=} \hlnum{2}\hlstd{)}
+
+\hlstd{both_dfms}\hlkwb{<-}\hlkwd{split_dfm}\hlstd{(description_dfm,} \hlkwc{n_train} \hlstd{=} \hlnum{1000}\hlstd{)}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
+
+\section{Refinement Using OCR}
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{ocr_corpus}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{corpus}\hlstd{(classdocs[,}\hlkwd{c}\hlstd{(}\hlstr{"fakeid"}\hlstd{,} \hlstr{"ocr"}\hlstd{,} \hlstr{"EV_article"}\hlstd{)],} \hlkwc{text_field} \hlstd{=} \hlstr{"ocr"}\hlstd{)}
+\hlstd{ocr_dfm} \hlkwb{<-} \hlkwd{preprocess_corpus}\hlstd{(ocr_corpus,} \hlkwc{stem}\hlstd{=}\hlnum{FALSE}\hlstd{,} \hlkwc{min_termfreq}\hlstd{=}\hlnum{5}\hlstd{,} \hlkwc{min_docfreq} \hlstd{=} \hlnum{2}\hlstd{)}
+
+\hlstd{both_dfms}\hlkwb{<-}\hlkwd{split_dfm}\hlstd{(ocr_dfm,} \hlkwc{n_train} \hlstd{=} \hlnum{1000}\hlstd{)}
+\hlstd{nb}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{textmodel_nb}\hlstd{(both_dfms}\hlopt{$}\hlstd{train,} \hlkwc{y}\hlstd{=quanteda}\hlopt{::}\hlkwd{docvars}\hlstd{(both_dfms}\hlopt{$}\hlstd{train,} \hlstr{"EV_article"}\hlstd{),} \hlkwc{prior}\hlstd{=}\hlstr{"uniform"}\hlstd{)}
+\hlstd{prob_nb}\hlkwb{<-}\hlkwd{predict}\hlstd{(nb,} \hlkwc{newdata} \hlstd{= both_dfms}\hlopt{$}\hlstd{test,} \hlkwc{type}\hlstd{=}\hlstr{"probability"}\hlstd{)}
+\hlstd{pred_nb}\hlkwb{<-}\hlkwd{data.frame}\hlstd{(}\hlkwd{predict}\hlstd{(nb,} \hlkwc{newdata} \hlstd{= both_dfms}\hlopt{$}\hlstd{test,} \hlkwc{type}\hlstd{=}\hlstr{"class"}\hlstd{))}
+\hlstd{res}\hlkwb{<-}\hlkwd{data.frame}\hlstd{(}\hlkwc{predict_nb}\hlstd{=pred_nb, prob_nb)}
+\hlkwd{names}\hlstd{(res)}\hlkwb{<-}\hlkwd{c}\hlstd{(}\hlstr{"predict_nb"}\hlstd{,} \hlstr{"prob_notev"}\hlstd{,} \hlstr{"prob_ev"}\hlstd{)}
+\hlkwd{assess_classification}\hlstd{(}\hlkwd{organise_results}\hlstd{(both_dfms}\hlopt{$}\hlstd{test, res))} \hlopt{%>%}
+  \hlkwd{filter}\hlstd{(rowname} \hlopt{%in%} \hlkwd{c}\hlstd{(}\hlstr{"Precision"}\hlstd{,} \hlstr{"Recall"}\hlstd{,} \hlstr{"F1"}\hlstd{))} \hlopt{%>%}
+  \hlkwd{kable}\hlstd{()}
+\end{alltt}
+\end{kframe}
+\begin{tabular}{l|r|l}
+\hline
+rowname & value & model\\
+\hline
+Precision & 0.6456212 & naive bayes\\
+\hline
+Recall & 0.9031339 & naive bayes\\
+\hline
+F1 & 0.7529691 & naive bayes\\
+\hline
+\end{tabular}
+
+\end{knitrout}
+
+\section{King Algorithm: implementation}
+
+\subsection{Incrementally Define $R$ and $S$}
+$R$ is our reference set. [King suggestions: could define $R$ based on one simple keyword search].
+\subsubsection{Intermediate step}
+Take keywords in $R$, $K_R$, ranked by simple statistic such as document frequency or frequency-inverse document frequency.
+User examines elements of $K_R$ apart from those used to define the set and chooses some keywords to define $Q_S$, which in turn generates a definition for $S$ so that we can run the rest of the algorithm.
+The user can continue to add keywords from $K_R$ into the final desired query $Q_RT$.
+This step also mitigates the issue of how to define a search set in large data sets that do not fit into memory all at once or may not even be able to be retrieved all at onece. is the BNA.
+
+\subsection{Partition $S$ into $T$ and $S \backslash T$}
+To partition $S$ into $T$ and $S \backslash T$, we first define a `training' set by sampling from $S$ and $R$.
+Since $R$ is typically much smaller than $S$ our test set for our classifiers is all all of $S$, we often use the entire $R$ set and a sample of $S$ as our training set.
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{R} \hlkwb{<-} \hlstd{classdocs[classdocs}\hlopt{$}\hlstd{EV_article}\hlopt{==}\hlnum{1}\hlstd{,]}
+\hlstd{R}\hlopt{$}\hlstd{R} \hlkwb{<-} \hlnum{1}
+\hlstd{R}\hlopt{$}\hlstd{in_sample}\hlkwb{<-}\hlnum{1}
+\hlstd{S} \hlkwb{<-} \hlstd{unclassdocs}
+\hlstd{S}\hlopt{$}\hlstd{R} \hlkwb{<-} \hlnum{0}
+
+\hlstd{n_sample_S} \hlkwb{<-} \hlnum{1000}
+\hlstd{S}\hlopt{$}\hlstd{in_sample}\hlkwb{<-}\hlnum{0}
+\hlstd{S}\hlopt{$}\hlstd{in_sample[}\hlkwd{sample}\hlstd{(}\hlnum{1}\hlopt{:}\hlkwd{nrow}\hlstd{(S), n_sample_S)]}\hlkwb{<-}\hlnum{1}
+
+\hlstd{R_S} \hlkwb{<-} \hlstd{dplyr}\hlopt{::}\hlkwd{bind_rows}\hlstd{(R, S)}
+\hlstd{R_S}\hlopt{$}\hlstd{fakeid}\hlkwb{<-}\hlnum{1}\hlopt{:}\hlkwd{nrow}\hlstd{(R_S)}
+
+\hlstd{R_S_corpus}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{corpus}\hlstd{(R_S[,}\hlkwd{c}\hlstd{(}\hlstr{"fakeid"}\hlstd{,} \hlstr{"ocr"}\hlstd{,} \hlstr{"in_sample"}\hlstd{,} \hlstr{"R"}\hlstd{)],} \hlkwc{text_field} \hlstd{=} \hlstr{"ocr"}\hlstd{)}
+\hlstd{R_S_dfm} \hlkwb{<-} \hlkwd{preprocess_corpus}\hlstd{(R_S_corpus,} \hlkwc{stem}\hlstd{=}\hlnum{FALSE}\hlstd{,} \hlkwc{min_termfreq}\hlstd{=}\hlnum{20}\hlstd{,} \hlkwc{min_docfreq} \hlstd{=} \hlnum{20}\hlstd{)}
+
+\hlstd{king_train_dfm}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{dfm_subset}\hlstd{(R_S_dfm, quanteda}\hlopt{::}\hlkwd{docvars}\hlstd{(R_S_dfm,} \hlstr{"in_sample"}\hlstd{)}\hlopt{==}\hlnum{1}\hlstd{)}
+\hlstd{king_nb} \hlkwb{<-} \hlstd{quanteda}\hlopt{::}\hlkwd{textmodel_nb}\hlstd{(king_train_dfm,} \hlkwc{y}\hlstd{=quanteda}\hlopt{::}\hlkwd{docvars}\hlstd{(king_train_dfm,} \hlstr{"R"}\hlstd{),} \hlkwc{prior}\hlstd{=}\hlstr{"uniform"}\hlstd{)}
+\hlstd{keywords}\hlkwb{<-}\hlkwd{nb_keywords}\hlstd{(king_train_dfm,} \hlstr{"R"}\hlstd{)}
+\hlstd{knitr}\hlopt{::}\hlkwd{kable}\hlstd{(}\hlkwd{head}\hlstd{(keywords,} \hlnum{20}\hlstd{))}
+\end{alltt}
+\end{kframe}
+\begin{tabular}{l|l|r|r|r}
+\hline
+  & rowname & 0 & 1 & id\\
+\hline
+3 & generated & 0.0221304 & 0.9778696 & 3\\
+\hline
+14 & legible & 0.0227857 & 0.9772143 & 14\\
+\hline
+8 & technology & 0.0250073 & 0.9749927 & 8\\
+\hline
+13 & deciphering & 0.0250073 & 0.9749927 & 13\\
+\hline
+2919 & chartist & 0.0267458 & 0.9732542 & 2919\\
+\hline
+2670 & detective & 0.0337936 & 0.9662064 & 2670\\
+\hline
+2271 & roughs & 0.0350241 & 0.9649759 & 2271\\
+\hline
+9415 & telegraphed & 0.0353459 & 0.9646541 & 9415\\
+\hline
+12921 & gutted & 0.0370477 & 0.9629523 & 12921\\
+\hline
+2501 & p.c & 0.0449904 & 0.9550096 & 2501\\
+\hline
+1079 & cobden & 0.0458847 & 0.9541153 & 1079\\
+\hline
+3421 & smashing & 0.0495804 & 0.9504196 & 3421\\
+\hline
+10653 & worker & 0.0558817 & 0.9441183 & 10653\\
+\hline
+9331 & schoolroom & 0.0579874 & 0.9420126 & 9331\\
+\hline
+13218 & gladstone's & 0.0579874 & 0.9420126 & 13218\\
+\hline
+3510 & ratepayers & 0.0602579 & 0.9397421 & 3510\\
+\hline
+8408 & telegram & 0.0632289 & 0.9367711 & 8408\\
+\hline
+1167 & disraeli & 0.0653778 & 0.9346222 & 1167\\
+\hline
+5 & optical & 0.0714484 & 0.9285516 & 5\\
+\hline
+12923 & pontypool & 0.0787619 & 0.9212381 & 12923\\
+\hline
+\end{tabular}
+
+\end{knitrout}
+
+After fitting the classifiers, we use the estimated parameters to generate predicted probabilities of $R$ membership for all documents in $S$.
+Of cource, all the search set documents in fact fall within $S$ but our interest in in learning from the \textit{mistakes} these classifiers make.
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{S_dfm} \hlkwb{<-} \hlstd{quanteda}\hlopt{::}\hlkwd{dfm_subset}\hlstd{(R_S_dfm, quanteda}\hlopt{::}\hlkwd{docvars}\hlstd{(R_S_dfm,} \hlstr{"R"}\hlstd{)}\hlopt{==}\hlnum{0}\hlstd{)}
+\hlstd{quanteda}\hlopt{::}\hlkwd{docvars}\hlstd{(S_dfm,} \hlstr{"T"}\hlstd{)}\hlkwb{<-}\hlkwd{predict}\hlstd{(king_nb,} \hlkwc{newdata} \hlstd{= S_dfm,} \hlkwc{type}\hlstd{=}\hlstr{"class"}\hlstd{)}
+\end{alltt}
+\end{kframe}
+\end{knitrout}
+
+\subsection{Discovering Keywords to Classify Documents}
+After partitioning $S$ into estimated target $T$ and non-target set $S \backslash T$, we must find and rank keywords which best discriminate $T$ and $S \backslash T$.
+King does this in three stages:
+\subsubsection{identify keywords in S}
+
+\subsubsection{sort them into those that predict each of the two steps}
+
+My suggestion here is simply to use binary\_dfm
+
+\begin{knitrout}
+\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}
+\begin{alltt}
+\hlstd{S_dfm_binary}\hlkwb{<-}\hlstd{quanteda}\hlopt{::}\hlkwd{dfm_weight}\hlstd{(S_dfm,} \hlkwc{scheme}\hlstd{=}\hlstr{"boolean"}\hlstd{)}
+\hlstd{king_stage2} \hlkwb{<-} \hlstd{quanteda}\hlopt{::}\hlkwd{textmodel_nb}\hlstd{(S_dfm,} \hlkwc{y}\hlstd{=quanteda}\hlopt{::}\hlkwd{docvars}\hlstd{(S_dfm_binary,} \hlstr{"T"}\hlstd{),} \hlkwc{distribution}\hlstd{=}\hlstr{"Bernoulli"}\hlstd{)}
+\hlstd{king_stage2} \hlkwb{<-} \hlkwd{nb_keywords}\hlstd{(S_dfm,} \hlstr{"T"}\hlstd{)}
+\hlstd{knitr}\hlopt{::}\hlkwd{kable}\hlstd{(}\hlkwd{head}\hlstd{(king_stage2,} \hlnum{30}\hlstd{))}
+\end{alltt}
+\end{kframe}
+\begin{tabular}{l|l|r|r|r}
+\hline
+  & rowname & 0 & 1 & id\\
+\hline
+8722 & unionism & 0.0113223 & 0.9886777 & 8722\\
+\hline
+8429 & horden & 0.0141129 & 0.9858871 & 8429\\
+\hline
+1208 & protectionist & 0.0173133 & 0.9826867 & 1208\\
+\hline
+9203 & suffragists & 0.0203970 & 0.9796030 & 9203\\
+\hline
+9590 & nationalist & 0.0223910 & 0.9776090 & 9590\\
+\hline
+8485 & motor & 0.0237863 & 0.9762137 & 8485\\
+\hline
+10142 & socialism & 0.0290080 & 0.9709920 & 10142\\
+\hline
+8420 & nationalists & 0.0296335 & 0.9703665 & 8420\\
+\hline
+9858 & socialist & 0.0296335 & 0.9703665 & 9858\\
+\hline
+2335 & dump & 0.0302866 & 0.9697134 & 2335\\
+\hline
+9120 & bicycle & 0.0316832 & 0.9683168 & 9120\\
+\hline
+9011 & truncheons & 0.0399786 & 0.9600214 & 9011\\
+\hline
+3074 & asquith & 0.0427787 & 0.9572213 & 3074\\
+\hline
+8737 & industries & 0.0438013 & 0.9561987 & 8737\\
+\hline
+9286 & rowdyism & 0.0438013 & 0.9561987 & 9286\\
+\hline
+9331 & schoolroom & 0.0438013 & 0.9561987 & 9331\\
+\hline
+9415 & telegraphed & 0.0438013 & 0.9561987 & 9415\\
+\hline
+8994 & batons & 0.0455433 & 0.9544567 & 8994\\
+\hline
+8421 & socialists & 0.0460006 & 0.9539994 & 8421\\
+\hline
+2417 & workers & 0.0471852 & 0.9528148 & 2417\\
+\hline
+8747 & candidature & 0.0491752 & 0.9508248 & 8747\\
+\hline
+2631 & unionist & 0.0495718 & 0.9504282 & 2631\\
+\hline
+9138 & railings & 0.0502017 & 0.9497983 & 9138\\
+\hline
+9205 & barricaded & 0.0502017 & 0.9497983 & 9205\\
+\hline
+1993 & witness's & 0.0541586 & 0.9458414 & 1993\\
+\hline
+2919 & chartist & 0.0541586 & 0.9458414 & 2919\\
+\hline
+8609 & drafted & 0.0541586 & 0.9458414 & 8609\\
+\hline
+9043 & booing & 0.0541586 & 0.9458414 & 9043\\
+\hline
+8398 & hartlepool & 0.0575614 & 0.9424386 & 8398\\
+\hline
+8430 & sacked & 0.0598163 & 0.9401837 & 8430\\
+\hline
+\end{tabular}
+
+\begin{kframe}\begin{alltt}
+\hlstd{knitr}\hlopt{::}\hlkwd{kable}\hlstd{(}\hlkwd{tail}\hlstd{(king_stage2,} \hlnum{30}\hlstd{))}
+\end{alltt}
+\end{kframe}
+\begin{tabular}{l|l|r|r|r}
+\hline
+  & rowname & 0 & 1 & id\\
+\hline
+16564 & despised & 0.9361369 & 0.0638631 & 16564\\
+\hline
+97 & fruits & 0.9370575 & 0.0629425 & 97\\
+\hline
+16555 & breaching & 0.9370575 & 0.0629425 & 16555\\
+\hline
+5001 & candidly & 0.9379520 & 0.0620480 & 5001\\
+\hline
+16375 & fortress & 0.9379520 & 0.0620480 & 16375\\
+\hline
+4632 & citadel & 0.9381717 & 0.0618283 & 4632\\
+\hline
+16237 & scrip & 0.9388215 & 0.0611785 & 16237\\
+\hline
+7969 & lunette & 0.9392471 & 0.0607529 & 7969\\
+\hline
+4023 & aspire & 0.9420685 & 0.0579315 & 4023\\
+\hline
+7970 & laurent & 0.9428271 & 0.0571729 & 7970\\
+\hline
+13935 & shells & 0.9449882 & 0.0550118 & 13935\\
+\hline
+15303 & carolina & 0.9449882 & 0.0550118 & 15303\\
+\hline
+6762 & combat & 0.9463404 & 0.0536596 & 6762\\
+\hline
+7376 & batteries & 0.9504040 & 0.0495960 & 7376\\
+\hline
+4633 & belgians & 0.9537326 & 0.0462674 & 4633\\
+\hline
+14316 & belgian & 0.9556141 & 0.0443859 & 14316\\
+\hline
+7397 & repose & 0.9560607 & 0.0439393 & 7397\\
+\hline
+4619 & antwerp & 0.9562807 & 0.0437193 & 4619\\
+\hline
+11134 & senate & 0.9564985 & 0.0435015 & 11134\\
+\hline
+12926 & prussia & 0.9564985 & 0.0435015 & 12926\\
+\hline
+2897 & gerard & 0.9566425 & 0.0433575 & 2897\\
+\hline
+15893 & frontiers & 0.9577611 & 0.0422389 & 15893\\
+\hline
+4618 & capitulation & 0.9581658 & 0.0418342 & 4618\\
+\hline
+16545 & lillo & 0.9611442 & 0.0388558 & 16545\\
+\hline
+6394 & belgium & 0.9623721 & 0.0376279 & 6394\\
+\hline
+4623 & chasse & 0.9626404 & 0.0373596 & 4623\\
+\hline
+7977 & bombs & 0.9672625 & 0.0327375 & 7977\\
+\hline
+7981 & scheldt & 0.9679827 & 0.0320173 & 7981\\
+\hline
+7973 & besiegers & 0.9727743 & 0.0272257 & 7973\\
+\hline
+4625 & forts & 0.9769438 & 0.0230562 & 4625\\
+\hline
+\end{tabular}
+
+\end{knitrout}
+
+\subsection{rank them by degree of discriminatory power}
+We already seem to have done this in the step above
+\subsection{Human Input and Human-Computer Iteration}
+Now present
 

### 2018-08-02 R/text_analysis.R
Add url to classified document results

@@ -160,7 +160,7 @@ get_classified_docs <- function (){
                                ev_docs)
   the_corpus$general_corpus<-1
 
-  the_corpus<-the_corpus[,c("id", "title", "description", "type", "page", "publication_date", "word_count", "ocr", "election_article", "EV_article", "just_election", "corpus_election", "electoral_nature", "violent_nature", "candidate_document_id")]
+  the_corpus<-the_corpus[,c("id", "title", "url", "description", "type", "page", "publication_date", "word_count", "ocr", "election_article", "EV_article", "just_election", "corpus_election", "electoral_nature", "violent_nature", "candidate_document_id")]
   the_corpus <- tibble::rowid_to_column(the_corpus, "fakeid")
 
   the_corpus

### 2018-08-02 other_R_code/article_selection_process.Rnw
automated doc changes

@@
 \documentclass{article}
+\usepackage{amsmath}
 
@@
 classdocs<-durhamevp::get_classified_docs()
+
 # just some candidate document for speed/space reasons
 unclassdocs<-durhamevp::get_candidate_documents(3000:6000)
-
 @
 
-In the data there are \Sexpr{nrow(classdocs)} cases:
+In the classified data there are \Sexpr{nrow(classdocs)} cases:
 \begin{itemize}
@@
 
-both_dfms<-split_dfm(description_dfm, n_train = 1000)
+both_dfms<-split_dfm(description_dfm, n_train = 700)
 
@@
 
-both_dfms<-split_dfm(ocr_dfm, n_train = 1000)
+both_dfms<-split_dfm(ocr_dfm, n_train = 700)
 nb<-quanteda::textmodel_nb(both_dfms$train, y=quanteda::docvars(both_dfms$train, "EV_article"), prior="uniform")
@@
 
-n_sample_S <- 1000
+n_sample_S <- 700
 S$in_sample<-0
@@
 \subsection{Human Input and Human-Computer Iteration}
-Now present
+
+The King et al suggestion is to present the above lists to humans who then choose additional keywords from these lists.
+That might be fine if the final goal is develop keywords.
+However, this does not work so well if the final goal is to obtain sets of documents based on those keywords.
+Some problems with this approach for obtaining documents
+\begin{enumerate}
+  \item the set of documents will keep on growing without limit (with many irrelevant documents)
+  \item there is no guidance about which keywords to select from the lists presented
+\end{enumerate}
+
+An alternative proposal is to continue with a classification approach. That is to treat the classifer as informative about two separate matters: keywords retrival as potentially informative
+
+The stage II classifier is informative about the following issues:
+\begin{enumerate}
+  \item terms which are in $S$ but not in $R$ which may be positively predictive of election violence.
+  \item terms which are very differently predictive of election violence between stage I and stage II classification.
+  \item
+\end{enumerate}
+
+Idea 1: For keyword $t$ in keywords $1 \dots n$, $Q_t$ is the Boolean query which returns document $d$ from $S$ if $d$ contains $t$.
+$S\prime$ is the set of documents returned by the set of queries $Q_{T_1} \dots Q_{T_n}$.
+The probability that document $d$ is an example of the concept of interest is given by the set of queries which return that document.
+We run independent queries with each of the keywords.
+We have different sets returned from
+
+Idea 2: King's stage II classification can be thought of of the first part of an EM process which augments information from labelled data with information from unlabelled data.
+See for a classic example Nigam et.
+al.
+2000 - Semi-supervised parameter estimation: can learn from a combination of labeled and unlabeled data in a loop.
+First train a classifier using available labeled documents, and probabilistically label the unlabeled documents.
+Then train a new classifier using the labels for all the documents, iterate to convergence.
+This basic EM procedure works well when the data conform to the generative assumptions of the model.
+However, these assumptions are often violated in practice, and poor performance can result.
+Two extension improve classification accuracy (1) a weighting factor to modulate the contribution of the unlabeled data and (2) the use of multiple mixture components per class.
+
+How can unlabeled data increase classification accuracy?
+Unlabelled data provide information about the joint probability distribution over words.
+Suppose that using only the labeled data we determine that documents containing the word `riot' belongs to the election violence class.
+If we use this fact to estimate the classification of the many unlabeled documents, we might find the word `bludgeon' occurs frequently with the word `riot' and we might construct a more accurate classifier that considers both `riot' and `bludgeon' as indicators of positive examples.
+
+Given a training set ($x^{(i)}, y^{(i)}$) for $i=1 \dots n$, where $\theta$ is a paramter vector consiting of the values for all parameters $q(y)$ [the probability of seeing the label $y$] and $q_i(x \vert y)$ [the probability of attribute $j$ taking the value $x$ conditional on the underlying label being $y$] the log-likelihood function is:
+\begin{equation}
+\begin{split}
+      L\left(\theta\right) & = \sum_{i=1}^{n} \log p\left(x^{(i)}, y^{(i)}\right) \\
+           & =  \sum_{i=1}^{n} \log q(y^{(i)}) + \sum_{i=1}^{n} \sum_{j=1}^{d} \log q_j \left(x_j^{(i)} \vert y^{(i)}\right)
+           \end{split}
+\end{equation}
+Idea 3: to find a set of keywords searches which returns $T$ - when you have a set of keywords which returns $T$ - adding new keywords will change $S$ but not reveal more cases of $T$ - so will not see large changes in individual word predictivity of class in Naive Bayes classifier.
+encompasses the add search terms until revised data set $S\prime$ is not substantially changed by addition of new
+When new search terms are added this changes the nature of $S$ - at each iteration new information added - consider changes to $S\prime$
+
+<<>>=
+names(king_stage2)<-c("rowname", "stage2_0", "stage2_1", "stage2_id")
+names(keywords)<-c("rowname", "stage1_0", "stage1_1", "stage1_id")
+left_join(king_stage2, keywords, by="rowname") %>%
+  mutate(logit_stage1 =log(stage1_1/stage1_0), logit_stage2=log(stage2_1/stage2_0)) %>%
+  ggplot(aes(logit_stage1, logit_stage2))+
+  geom_point()
+@
 

### 2018-08-02 other_R_code/article_selection_pilot_writeup.Rnw
add article selection pilot code

\documentclass{article}
\usepackage{amsmath}

\begin{document}

<<setuppath, echo=FALSE, results="hide">>=
dropbox.path<-switch (Sys.info()["nodename"],
                      "DM-GIA-051"="D:/Dropbox",
                      "DM-GIA-055"="D:/Dropbox",
                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")

project.path<-paste0(dropbox.path, "/ESRC Grant EV 19th Century")

knitr::read_chunk(paste0(project.path, "/Code/durhamevp/other_R_code/article_selection_pilot.R"))
@

<<pilot.packages, warning=FALSE, message=FALSE>>=

@

<<download.R.set, cache=TRUE>>=

@

<<initial.1832.results>>=

@

\end{document}

### 2018-08-02 other_R_code/article_selection_pilot.R

@@ -1,0 +1,99 @@
+##----pilot.packages----
+
+library(durhamevp)
+library(tidyverse)
+library(quanteda)
+
+##----initial.keywords----
+# election riot, election incident, election disturbance
+
+##----download.R.set----
+# In fact we have some classified docs non-EV cases here King's R set doesn't contain any non-cases
+# I think we should use our more extensive information here
+
+classdocs<-durhamevp::get_classified_docs()
+
+classdocs<-classdocs %>%
+  dplyr::mutate(std_url = sub("download/", "", url)) %>%
+  dplyr::mutate(unclass=0, classified=1)
+
+##----initial.1832.results----
+head(classdocs)
+all_searches<-get_archivesearches()
+initial_1832_searches<-all_searches%>%
+  dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
+  filter(archive_date_start>lubridate::ymd("1832-01-01"), archive_date_start<lubridate::ymd("1832-12-31")) %>%
+  filter(search_text %in% c("election riot", "election incident", "election disturbance"))
+
+# a number of precisely duplicated searches here which return precisely duplicated results - we could handle this later on but here probably simplest to just use three distinct ones
+# election riot - id 73
+# election disturbance - id 81
+# election incident - id 85
+res_i_1832<-get_archivesearchresults(archive_search_id = c(73, 81, 85)) %>%
+  left_join(all_searches, by=c("archive_search_id"="id")) %>%
+  mutate(std_url = sub("download/", "", url))
+
+is_classified <-res_i_1832$std_url %in% classdocs$std_url
+
+unclass_i_1832 <- res_i_1832[!is_classified,] %>%
+  mutate(unclass=1, classified=0)
+
+all_docs<- bind_rows(classdocs,
+                     unclass_i_1832)
+all_docs$fakeid<-1:nrow(all_docs)
+
+##----first.stage.classification----
+all_corpus_d<-corpus(all_docs[c("fakeid", "description", "EV_article", "classified")], text_field="description")
+all_corpus_o<-corpus(all_docs[c("fakeid", "ocr", "EV_article", "classified")], text_field = "ocr")
+
[…]

### 2018-08-02 other_R_code/article_selection_pilot.R
Further write up of article selection pilot

@@ -18,7 +18,6 @@ classdocs<-classdocs %>%
   dplyr::mutate(unclass=0, classified=1)
 
 ##----initial.1832.results----
-head(classdocs)
 all_searches<-get_archivesearches()
 initial_1832_searches<-all_searches%>%
   dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
@@ -42,58 +41,92 @@ all_docs<- bind_rows(classdocs,
                      unclass_i_1832)
 all_docs$fakeid<-1:nrow(all_docs)
 
+##----descriptives.1832----
+res_32_des<-res_i_1832 %>%
+  group_by(url) %>%
+  mutate(search_text=sub(" ", "_", search_text)) %>%
+  select(url, search_text) %>%
+  mutate(value=1) %>%
+  spread(search_text, value, fill=0) %>%
+  mutate(tot_art=nrow(.))
+
+knitr::kable(res_32_des %>%
+  group_by(election_riot, election_incident, election_disturbance) %>%
+  summarize(n=length(tot_art), prop=n/tot_art[1])%>%
+    arrange(-prop), digits = 2)
+
+knitr::kable(res_32_des %>%
+               group_by(election_riot) %>%
+               summarize(n=length(tot_art), prop=n/tot_art[1]) %>%
+               arrange(-election_riot),
+             digits = 2)
+
+knitr::kable(res_32_des %>%
+               group_by(election_incident) %>%
+               summarize(n=length(tot_art), prop=n/tot_art[1])%>%
+               arrange(-election_incident),
+             digits = 2)
+
+knitr::kable(res_32_des %>%
+               group_by(election_disturbance) %>%
+               summarize(n=length(tot_art), prop=n/tot_art[1])%>%
+               arrange(-election_disturbance),
+             digits = 2)
+
+
 ##----first.stage.classification----
 all_corpus_d<-corpus(all_docs[c("fakeid", "description", "EV_article", "classified")], text_field="description")
-all_corpus_o<-corpus(all_docs[c("fakeid", "ocr", "EV_article", "classified")], text_field = "ocr")
 
[…]

### 2018-08-07 R/firststage_functions.R
Test run of the first stage function; adding first stage function and increasing default timing parameters in the preprocessing function

@@ -13,7 +13,7 @@ create_docsets<-function(alldocs, size, seed){
   return(list(training=training, testing=testing))
 }
 
-preprocess_corpus<-function(the_corpus, stem=TRUE, min_termfreq=2, min_docfreq=2, max_termfreq=NULL, max_docfreq=NULL,
+preprocess_corpus<-function(the_corpus, stem=TRUE, min_termfreq=20, min_docfreq=20, max_termfreq=NULL, max_docfreq=NULL,
                             remove_punct=TRUE, remove_numbers=TRUE, remove_hyphens=TRUE, termfreq_type="count", docfreq_type="count",
                             dfm_tfidf=FALSE){
   #' Preprocess a text corpus and return a document feature matrix (wrapper round quanteda functions).
@@ -22,8 +22,8 @@ preprocess_corpus<-function(the_corpus, stem=TRUE, min_termfreq=2, min_docfreq=2
   #' @param remove_punct default TRUE
   #' @param remove_numbers default TRUE
   #' @param remove_hyphens default TRUE
-  #' @param min_termfreq default 2
-  #' @param min_docfreq default 2
+  #' @param min_termfreq default 20
+  #' @param min_docfreq default 20
   #' @param max_termfreq default NULL
   #' @param max_docfreq default NULL
   #' @param termfreq_type default "count"
@@ -79,4 +79,57 @@ nb_keywords<-function(training, classvar, distribution="Bernoulli"){
   post$id<-seq.int(nrow(post))
   post<-post[order(post[,3], decreasing=TRUE),]
   return(post)
+}
+
+run_firststage<-function(docs, docidvar="fakeid", classvar="classified", typevar="EV_article", textvar="description",
+                         stem=TRUE, min_termfreq=20, min_docfreq=20, max_termfreq=NULL, max_docfreq=NULL,
+                         remove_punct=TRUE, remove_numbers=TRUE, remove_hyphens=TRUE, termfreq_type="count", docfreq_type="count",
+                         dfm_tfidf=FALSE,
+                         cutpoint=0.8){
+  #' First stage function of the article selection process taking in a set of documents and returning a set of potential keywords
+  #' @param docs Data frame of documents containing classified cases (R-set) and unclassified cases (S-set)
+  #' @param docidvar Unique document id variable; default = "fakeid"
[…]

### 2018-08-07 other_R_code/firststage_code.R

@@ -14,6 +14,46 @@ rm(list=ls())
 #keyring::key_set(service="evp", user="data_writer")
 #con<-evdb_connect(password_method = "keyring")
 
+#Create clean document set for the 1832 election to run first stage function
+classdocs<-durhamevp::get_classified_docs()
+
+classdocs<-classdocs %>%
+  dplyr::mutate(std_url = sub("download/", "", url)) %>%
+  dplyr::mutate(unclass=0, classified=1)
+
+##----initial.1832.results----
+all_searches<-get_archivesearches()
+initial_1832_searches<-all_searches%>%
+  dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
+  filter(archive_date_start>lubridate::ymd("1832-01-01"), archive_date_start<lubridate::ymd("1832-12-31")) %>%
+  filter(search_text %in% c("election riot", "election incident", "election disturbance"))
+
+# a number of precisely duplicated searches here which return precisely duplicated results - we could handle this later on but here probably simplest to just use three distinct ones
+# election riot - id 73
+# election disturbance - id 81
+# election incident - id 85
+res_i_1832<-get_archivesearchresults(archive_search_id = c(73, 81, 85)) %>%
+  left_join(all_searches, by=c("archive_search_id"="id")) %>%
+  mutate(std_url = sub("download/", "", url))
+
+is_classified <-res_i_1832$std_url %in% classdocs$std_url
+
+unclass_i_1832 <- res_i_1832[!is_classified,] %>%
+  mutate(unclass=1, classified=0)
+
+all_docs<- bind_rows(classdocs,
+                     unclass_i_1832)
+all_docs$fakeid<-1:nrow(all_docs)
+
+#Run the first stage function
+kwsuggestions<-run_firststage(docs=all_docs,min_termfreq=50, min_docfreq=50)
+kwsuggestions
+
+
+
+
+##----OLD CODE----
+
 #Get candidate documents
 classdoc<-get_classified_docs()
 

### 2018-08-07 R/database_interactivity.R
select candidate documents by url

@@ -251,16 +251,18 @@ get_document<-function(document_id){
   documents
 }
 
-get_candidate_documents<-function(cand_document_id){
+get_candidate_documents<-function(cand_document_id, url="all"){
   #' Returns the candidate document table filtered by candidate document id
   #'
   #' @param cand_document_id Candidate document id or ids to filter by.
+  #' @param url document url or urls to filter by.
   #' @export
 
   con <- manage_dbcons()
   this_sql<-"SELECT * FROM portal_candidatedocument" # base query
 
   res<-build_where_condition("id", cand_document_id, this_sql, NULL)
+  res<-build_where_condition("url", url, res$condition, res$interpolate_list)
   res[["condition"]] <- paste(res[["condition"]], ";")
   this_sql<-res[["condition"]]
   interpolate_list <- res[["interpolate_list"]]

### 2018-08-07 R/text_analysis.R
Add functions to select documents based on classifier (description and ocr)

@@ -186,3 +186,47 @@ contains_words <- function(the_dataframe, contains_words, text_col="ocr", result
 
   res_set
 }
+
+
+classifier_select_docs <- function(classifier, new_docs, text_field="description", class_to_keep=1){
+  #' Subsets a dataframe of documents based on a classifier.
+  #'
+  #' @param classifier The quanteda naive bayes classifier to perform the classification
+  #' @param new_docs A data frame containing the documents to classify
+  #' @param text_field The field containing the text to classify
+  #' @param class_to_keep The classifier class to keep
+  #' @param ... arguments to be passed to \code{preprocess_corpus}
+  #' @return The subset of the \code{docs_df} which is classified as \code{class_to_keep}
+  #' @export
+
+  the_corpus <- quanteda::corpus(new_docs[,c(text_field), drop=FALSE], text_field = text_field)
+  the_dfm<-durhamevp::preprocess_corpus(the_corpus)
+  the_dfm<-quanteda::dfm_select(the_dfm, classifier$x)
+  want_these<-predict(classifier, newdata = the_dfm, type="class")==class_to_keep
+
+
+  new_docs[want_these,]
+}
+
+stage2<-function(train, new_docs, text_field="description", class_to_keep=1, training_classify_var="EV_article", prior="uniform"){
+  #'
+  #' @export
+
+  train_corpus<-quanteda::corpus(train[,c(text_field, training_classify_var)], text_field = text_field)
+  train_dfm<-durhamevp::preprocess_corpus(train_corpus)
+  classifier<-quanteda::textmodel_nb(train_dfm, y=quanteda::docvars(train_dfm, training_classify_var), prior=prior)
+  new_docs_subset<-durhamevp::classifier_select_docs(classifier=classifier, new_docs=new_docs, text_field = text_field, class_to_keep = class_to_keep)
+
+  new_docs_subset
+}
+
+stage3<-function(train, new_docs, text_field="ocr", class_to_keep=1, training_classify_var="EV_article", prior="uniform"){
+  #'
+  #' @export
+  train_corpus<-quanteda::corpus(train[,c(text_field, training_classify_var)], text_field = text_field)
+  train_dfm<-durhamevp::preprocess_corpus(train_corpus)
+  classifier<-quanteda::textmodel_nb(train_dfm, y=quanteda::docvars(train_dfm, training_classify_var), prior=prior)
[…]

### 2018-08-07 other_R_code/article_selection_pilot_withfunctions.Rnw
write up implementation of classification selection functions

\documentclass{article}
\title{Election Violence Newspaper Article Selection Process Pilot}
\begin{document}
\maketitle
\section{Summary}
The document below provides code to implement the keyword selection process (and later the plan is that it will describe the whole workflow of article selection).

The main point so far is to use classifier suggestions to expand keywords so that we capture cases of election violence. The highly predictive keyword lists can be found in Section \ref{sect:keysuggest}.

Should we use highly predictive keywords (which might reinforce patterns we have found) or should we use words whose predictivity is changing between first and second stage classification.

As a first attempt (not particularly principled) I suggest taking:
\begin{description}
 \item [one from highly predictive in stage 1 classification] rough
 \item [one from highly predictive in stage 2 classification] mob
 \item [one from becomes highly predictive from stage 1 to stage 2] stone
\end{description}

Note: Here the highly predictive keywords are taken only from the description (not the full ocr). If we want to use the King method then this is necessary because we won't have the full ocr for unclassified cases in general. However, if we use the first stage classifier we could use the full ocr. Lists from first stage classifier with full ocr can be found in Section \ref{sect:ocrclass}

\section{Packages used}
<<setuppath, echo=FALSE, results="hide">>=
dropbox.path<-switch (Sys.info()["nodename"],
                      "DM-GIA-051"="D:/Dropbox",
                      "DM-GIA-055"="D:/Dropbox",
                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")

project.path<-paste0(dropbox.path, "/ESRC Grant EV 19th Century")

knitr::read_chunk(paste0(project.path, "/Code/durhamevp/other_R_code/article_selection_pilot.R"))
options(tidy=TRUE, width=50)
@

<<resetdb, echo=FALSE, warning=FALSE, message=FALSE, results="hide">>=
# Is this necessary because of cached results below? Otherwise sometime get error messages like Corrupt MySQL handle
durhamevp::killDbConnections()

@

<<pilot.packages, warning=FALSE, message=FALSE>>=

@

\section{Download Classified Cases}
There is an initial set of cases which represent the concept (in this case `election violence'). We also have a set of cases which do not represent the concept (Note: King et al do not have the non-election violence cases).

I also add indicators that this material is classified (\texttt{classified==1}) and that it is not unclassified (\texttt{unclass==0}) which will be useful when added to subsequent material.
<<download.R.set, cache=TRUE>>=

@

\section{Download Initial 1832 Cases}
We run three searches on the BNA. election riot, election incident, election disturbance. The code below returns these search results (including the description text) as stored on the database.

A (slightly adjusted) version of the url is used to detect and remove material which is in the classified set above.

I also add indicators that this material is not classified (\texttt{classified==0}) and that it is unclassified (\texttt{unclass==1}) which will be useful when added to the classified material above.

(Note: infact these searches have been run multiple times in 1832 probably for experimentation reasons - presumably because they were run very close in time to each other with no new material added the results are identical - for this reason I have just chosen one instance of each of the three searches).
<<initial.1832.results>>=

@

\section{First stage classification}
Here I use the classified non-election violence cases which we have. King et al do not have the equivalent - so they use the unclassified cases as non-cases.
<<first.stage.classification>>=

@

\section{Second stage classification}
<<second.stage.classification>>=

@

\section{Connect results}
Connect results from the two classification stages.
<<join.stages>>=

@

\section{Keyword suggestions}
\label{sect:keysuggest}
From the first stage classifier (words most predictive of election violence articles)
From the second stage classifier (words most predictive of predicted election violence articles)
From the difference between the first and second stage classifers (words which become much more and much less predicitive of election violence articles between the two classification stages).
<<classification.results>>=

@

\section{Some descriptives of search returns and overlaps}
The 1832 searches with the three terms (election riot, election disturbance, election incident) returned a total of \Sexpr{length(unique(res_i_1832$url))} unique articles. Below are the numbers and proportion of total returns from combinations of the initial search terms and from each search term independently.
<<descriptives.1832, results='asis'>>=

@

\section{First stage classification on full OCR}
\label{sect:ocrclass}
<<first.stage.classification.ocr>>=

@

\end{document}

### 2018-08-07 other_R_code/article_selection_pilot.R

@@ -130,3 +130,80 @@ class_nb_ocr <- quanteda::textmodel_nb(class_dfm_o, y=quanteda::docvars(class_df
 first_stage_keywords_ocr<-nb_keywords(class_dfm_o, "EV_article")
 
 knitr::kable(head(first_stage_keywords_ocr, 30), digits = 2)
+
+
+##----secondround.1832.results----
+all_searches<-get_archivesearches()
+initial_1832_searches<-all_searches%>%
+  dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
+  filter(archive_date_start>lubridate::ymd("1832-01-01"), archive_date_start<lubridate::ymd("1832-12-31")) %>%
+  filter(search_text %in% c("election riot", "election incident", "election disturbance", "rough", "stone", "mob"))
+
+# a number of precisely duplicated searches here which return precisely duplicated results - we could handle this later on but here probably simplest to just use three distinct ones
+# election riot - id 73
+# election disturbance - id 81
+# election incident - id 85
+# rough - id 170
+# stone - id 171
+# mob - id 172
+
+res_2_1832<-get_archivesearchresults(archive_search_id = c(73, 81, 85, 170, 171, 172)) %>%
+  left_join(all_searches, by=c("archive_search_id"="id")) %>%
+  mutate(std_url = sub("download/", "", url))
+res_2_1832 <- res_2_1832[!duplicated(paste(res_2_1832$search_text, res_2_1832$description)),]
+is_classified <-res_2_1832$std_url %in% classdocs$std_url
+
+unclass_2_1832 <- res_2_1832[!is_classified,] %>%
+  mutate(unclass=1, classified=0)
+
+all_docs2<- bind_rows(classdocs,
+                     unclass_2_1832)
+all_docs2$fakeid<-1:nrow(all_docs)
+
+##----descriptives.1832----
+
+res_32_des<-res_2_1832[!duplicated(paste(res_2_1832$search_text, res_2_1832$description)),] %>%
+  group_by(url) %>%
+  mutate(search_text=sub(" ", "_", search_text)) %>%
+  dplyr::select(url, search_text) %>%
+  mutate(value=1) %>%
+  tidyr::spread(search_text, value, fill=0) %>%
+  mutate(tot_art=nrow(.))
+
+knitr::kable(res_32_des %>%
[…]

### 2018-08-07 R/text_analysis.R
change function names

@@ -208,7 +208,7 @@ classifier_select_docs <- function(classifier, new_docs, text_field="description
   new_docs[want_these,]
 }
 
-stage2<-function(train, new_docs, text_field="description", class_to_keep=1, training_classify_var="EV_article", prior="uniform"){
+classifier_selection_description<-function(train, new_docs, text_field="description", class_to_keep=1, training_classify_var="EV_article", prior="uniform"){
   #'
   #' @export
 
@@ -220,7 +220,7 @@ stage2<-function(train, new_docs, text_field="description", class_to_keep=1, tra
   new_docs_subset
 }
 
-stage3<-function(train, new_docs, text_field="ocr", class_to_keep=1, training_classify_var="EV_article", prior="uniform"){
+classifier_selection_ocr<-function(train, new_docs, text_field="ocr", class_to_keep=1, training_classify_var="EV_article", prior="uniform"){
   #'
   #' @export
   train_corpus<-quanteda::corpus(train[,c(text_field, training_classify_var)], text_field = text_field)

### 2018-08-08 R/text_analysis.R
add get_candidates_from_archivesearchresults

@@ -230,3 +230,17 @@ classifier_selection_ocr<-function(train, new_docs, text_field="ocr", class_to_k
 
   new_docs_subset
 }
+
+get_candidates_fromarchivesearchresults<-function(archivesearchresults){
+  #' Gets candidate documents from archivesearchresults.
+  #' This is somewhat challenging because sometimes the url has 'download' in sometimes it doesn't
+  #' This function is really a hack to find either case.
+  #' @param archivesearchresults The archive search results (including a url column)
+  #' @return Candidate documents with urls matching the urls in archivesearchresults
+  #' @export
+
+  archivesearchresults$url_std<-sub("/viewer/download", "/viewer", archivesearchresults$url)
+  the_candidates<-get_candidate_documents(cand_document_id = "all", c(archivesearchresults$url, archivesearchresults$url_std))
+
+  the_candidates
+}

### 2018-08-08 other_R_code/article_selection_pilot_withfunctions.Rnw
add keyword selection routines

@@
 \documentclass{article}
-\title{Election Violence Newspaper Article Selection Process Pilot}
+\title{Election Violence Newspaper Article Selection Process Pilot: Using Classifier to Select Documents}
 \begin{document}
@@
 \section{Summary}
-The document below provides code to implement the keyword selection process (and later the plan is that it will describe the whole workflow of article selection).
-
-The main point so far is to use classifier suggestions to expand keywords so that we capture cases of election violence.
-The highly predictive keyword lists can be found in Section \ref{sect:keysuggest}.
-
-Should we use highly predictive keywords (which might reinforce patterns we have found) or should we use words whose predictivity is changing between first and second stage classification.
-
-As a first attempt (not particularly principled) I suggest taking:
-\begin{description}
- \item [one from highly predictive in stage 1 classification] rough
- \item [one from highly predictive in stage 2 classification] mob
- \item [one from becomes highly predictive from stage 1 to stage 2] stone
-\end{description}
-
-Note: Here the highly predictive keywords are taken only from the description (not the full ocr).
-If we want to use the King method then this is necessary because we won't have the full ocr for unclassified cases in general.
-However, if we use the first stage classifier we could use the full ocr.
-Lists from first stage classifier with full ocr can be found in Section \ref{sect:ocrclass}
+The document below provides code to implement the selection of articles based first on a classification of the description text, and second based on the full OCR.
+The implementation is actually in Sections \ref{sect:whichdownloadocr} and \ref{sect:whichcode}.
 
@@
 durhamevp::killDbConnections()
+
+@
+
+<<selection.pilot.custom.functions, echo=FALSE>>=
 
@@
 
-\section{First stage classification}
-Here I use the classified non-election violence cases which we have. King et al do not have the equivalent - so they use the unclassified cases as non-cases.
-<<first.stage.classification>>=
+\section{Use classifier to decide which documents to download full ocr}
+\label{sect:whichdownloadocr}
+
+<<subset.on.description>>=
 
@@
 
-\section{Second stage classification}
-<<second.stage.classification>>=
+\section{Use classifier to decide which of the downloaded documents to code}
+\label{sect:whichcode}
+
+<<subset.on.ocr>>=
 
@@
 
-\section{Connect results}
-Connect results from the two classification stages.
-<<join.stages>>=
-
-@
-
-\section{Keyword suggestions}
-\label{sect:keysuggest}
-From the first stage classifier (words most predictive of election violence articles)
-From the second stage classifier (words most predictive of predicted election violence articles)
-From the difference between the first and second stage classifers (words which become much more and much less predicitive of election violence articles between the two classification stages).
-<<classification.results>>=
-
-@
-
-\section{Some descriptives of search returns and overlaps}
-The 1832 searches with the three terms (election riot, election disturbance, election incident) returned a total of \Sexpr{length(unique(res_i_1832$url))} unique articles.
-Below are the numbers and proportion of total returns from combinations of the initial search terms and from each search term independently.
-<<descriptives.1832, results='asis'>>=
-
-@
-
-\section{First stage classification on full OCR}
-\label{sect:ocrclass}
-<<first.stage.classification.ocr>>=
+\section{Some Case: These}
+<<print.random.not.code.cases, results='asis'>>=
 

### 2018-08-08 R/text_analysis.R

@@ -244,3 +244,31 @@ get_candidates_fromarchivesearchresults<-function(archivesearchresults){
 
   the_candidates
 }
+
+searches_to_dfm<- function(archivesearches){
+  #' Convert a set of search results to a dfm.
+  #' @param archivesearches the results of archivesearches
+  searches_to_string<-archivesearches %>%
+    dplyr::mutate(std_url = sub("download/", "", url)) %>%
+    group_by(std_url) %>%
+    dplyr::summarise(search_string=paste(search_text, collapse = " "))
+  searchstring_corpus <- quanteda::corpus(searches_to_string, text_field="search_string")
+  searchstring_dfm<-quanteda::dfm(searchstring_corpus)
+
+  searchstring_dfm
+}
+
+classifier_selection_keywords<-function(train, archivesearches, class_to_keep=1, training_classify_var="EV_article", prior="uniform", text_field="ocr"){
+  #'
+  #' @export
+
+  search_dfm<-searches_to_dfm(archivesearchresults)
+  train_corpus<-quanteda::corpus(train[,c(text_field, training_classify_var)], text_field = text_field)
+  train_dfm<-quanteda::dfm(train_corpus, select=colnames(search_dfm))
+  search_dfm<-quanteda::dfm_select(search_dfm, train_dfm)
+  classifier<-quanteda::textmodel_nb(train_dfm, y=quanteda::docvars(train_dfm, training_classify_var), prior=prior)
+  want_these<-predict(classifier, newdata = search_dfm, type="class")==class_to_keep
+
+
+  archivesearches[want_these,]
+}

### 2018-08-08 R/text_analysis.R
typo

@@ -279,7 +279,7 @@ searches_to_dfm<- function(archivesearches){
   searchstring_dfm
 }
 
-classifier_selection_keywords<-function(train, archivesearches, class_to_keep=1, training_classify_var="EV_article", prior="uniform", text_field="ocr"){
+classifier_selection_keywords<-function(train, archivesearchresults, class_to_keep=1, training_classify_var="EV_article", prior="uniform", text_field="ocr"){
   #'
   #' @export
 

### 2018-08-08 R/text_analysis.R
typo

@@ -291,5 +291,5 @@ classifier_selection_keywords<-function(train, archivesearchresults, class_to_ke
   want_these<-predict(classifier, newdata = search_dfm, type="class")==class_to_keep
 
 
-  archivesearches[want_these,]
+  archivesearchresults[want_these,]
 }

### 2018-08-09 other_R_code/firststage_code.R
Adding a new first stage function using feature co-ouccence to determine search terms to add

@@ -12,7 +12,7 @@ rm(list=ls())
 
 #One Time Connection to the Database (necesary for Patrick to connect to database)
 #keyring::key_set(service="evp", user="data_writer")
-#con<-evdb_connect(password_method = "keyring")
+con<-evdb_connect(password_method = "keyring")
 
 #Create clean document set for the 1832 election to run first stage function
 classdocs<-durhamevp::get_classified_docs()
@@ -45,11 +45,39 @@ all_docs<- bind_rows(classdocs,
                      unclass_i_1832)
 all_docs$fakeid<-1:nrow(all_docs)
 
-#Run the first stage function
-kwsuggestions<-run_firststage(docs=all_docs,min_termfreq=50, min_docfreq=50)
-kwsuggestions
+#Run the first stage function focusing on change of predictability
+kw_nbchng<-run_firststage_nbchng(docs=all_docs,min_termfreq=50, min_docfreq=50)
+kw_nbchng
 
+#Run the first stage function focusing on feature co-ouccerence
+kw_fcm<-run_firststage_fcm(docs=all_docs,min_termfreq=50, min_docfreq=50)
+kw_fcm
 
+#DEVELOPMENT OF FIRST STAGE FCM
+full_corpus<-quanteda::corpus(all_docs[c("fakeid", "classified", "EV_article", "description")], text_field="description")
+full_dfm <- durhamevp::preprocess_corpus(full_corpus, stem=TRUE, remove_punct=TRUE, remove_numbers=TRUE, remove_hyphens=TRUE,
+                                         min_termfreq=20, min_docfreq = 20, termfreq_type="count", docfreq_type="count")
+topfeatures(full_dfm)
+nfeat(full_dfm)
+
+class_dfm<-quanteda::dfm_subset(full_dfm, quanteda::docvars(full_dfm, "classified")==1)
+class_nb <- quanteda::textmodel_nb(class_dfm, y=quanteda::docvars(class_dfm, "EV_article"), prior="uniform")
+keywords1<-durhamevp::nb_keywords(class_dfm, "EV_article")
+topkw1<-subset(keywords1[,1],keywords1[,3]>=0.9)
+
+S_dfm <- quanteda::dfm_subset(full_dfm, quanteda::docvars(full_dfm, "classified")==0)
[…]

### 2018-08-09 other_R_code/article_selection_pilot_evaluate_keyword_methods.Rnw
implementation pilot functions

\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{Election Violence Newspaper Article Selection Process Pilot: Evaluate Keyword Selection Method}
\begin{document}
\maketitle
\section{Summary}
After the code to setup and download data (Sections \ref{sect:packages}-\ref{sect:download1832}) the document below includes:
First, an implementation of code to select of articles for coding, where initial evaluation of articles is based on keywords from the boolean searches which return those articles (Sections \ref{sect:whichdownloadocr}-\ref{sect:useonocr}). This classification is done using actual searches conducted (effectively 4 keywords) with a Naive Bayes classifier.

Second, the document then provides an evaluation of the keyword selection step based on user classified articles from the platform with Naive Bayes and other classifiers and with 4 and 10 keyword sets (Sections \ref{sect:eval4nb}-\ref{sect:eval10other}).

Finally, to provide an alternative way of evaluating the process, the document includes 10 randomly selected cases which are rejected for coding in the implementation code (Section \ref{sect:rejectnbprocess}).

\section{Packages used}
\label{sect:packages}
<<setuppath, echo=FALSE, results="hide">>=
dropbox.path<-switch (Sys.info()["nodename"],
                      "DM-GIA-051"="D:/Dropbox",
                      "DM-GIA-055"="D:/Dropbox",
                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")

project.path<-paste0(dropbox.path, "/ESRC Grant EV 19th Century")

knitr::read_chunk(paste0(project.path, "/Code/durhamevp/other_R_code/article_selection_pilot.R"))
options(tidy=TRUE, width=50)
@

<<resetdb, echo=FALSE, warning=FALSE, message=FALSE, results="hide">>=
# Is this necessary because of cached results below? Otherwise sometime get error messages like Corrupt MySQL handle
durhamevp::killDbConnections()

@

<<selection.pilot.custom.functions, echo=FALSE>>=

@

<<pilot.packages, warning=FALSE, message=FALSE>>=

@

\section{Download Classified Cases}
There is an initial set of cases which represent the concept (in this case `election violence'). We also have a set of cases which do not represent the concept (Note: King et al do not have the non-election violence cases).

I also add indicators that this material is classified (\texttt{classified==1}) and that it is not unclassified (\texttt{unclass==0}) which will be useful when added to subsequent material.
<<download.R.set, cache=TRUE>>=

@

\section{Assess Naive Bayes selection performance on 4 keywords (binary dfm)}
\label{sect:eval4nb}
Here there are four keywords (election, riot, disturbance, incident) which are either present (1) or not-present (0). Use these patterns to identify election violence articles with a Naive Bayes classifer.
<<subset.on.keywords.eval.four.words>>=

@

\section{How do other classifiers perform on 4 keywords (binary dfm)}
Is performance improved by using other classifiers than Naive Bayes? Here there are four keywords (election, riot, disturbance, incident) which are either present (1) or not-present (0). Use these patterns to identify election violence articles.
<<subset.on.keywords.eval.other.methods.four.words>>=

@

\section{Assess Naive Bayes selection performance on 10 keywords (binary dfm)}
Here there are ten keywords ((election, riot, disturbance, incident, mob, stone, window, candidate, party, hustings, magistrate) which are either present (1) or not-present (0). Use these patterns to identify election violence articles with a Naive Bayes classifer.
<<subset.on.keywords.eval.ten.words>>=

@

\section{How do other classifiers perform on 10 keywords (binary dfm)}
\label{sect:eval10other}
The same but with ten keywords (election, riot, disturbance, incident, mob, stone, window, candidate, party, hustings, magistrate) which are either present (1) or not-present (0). Use these patterns to identify election violence articles using a range of other classifiers.

<<subset.on.keywords.eval.other.methods.ten.words>>=

@

\end{document}

### 2018-08-09 other_R_code/article_selection_pilot_evaluate_keywordmethod.Rnw
implementation pilot functions

--- 2018-08-09 other_R_code/article_selection_pilot_evaluate_keyword_methods.Rnw
@@
 
+\section{Download Initial 1832 Cases}
+\label{sect:download1832}
+We run three searches on the BNA. election riot, election incident, election disturbance. The code below returns these search results (including the description text) as stored on the database.
+
+A (slightly adjusted) version of the url is used to detect and remove material which is in the classified set above.
+
+I also add indicators that this material is not classified (\texttt{classified==0}) and that it is unclassified (\texttt{unclass==1}) which will be useful when added to the classified material above.
+
+(Note: infact these searches have been run multiple times in 1832 probably for experimentation reasons - presumably because they were run very close in time to each other with no new material added the results are identical - for this reason I have just chosen one instance of each of the three searches).
+<<initial.1832.results>>=
+
+@
+
+\section{Use classifier to decide which documents to download full ocr}
+\label{sect:whichdownloadocr}
+
+<<subset.on.description>>=
+
+@
+
+\section{Use classifier to decide which of the downloaded documents to code}
+\label{sect:whichcode}
+
+<<subset.on.ocr>>=
+
+@
+\section{Use classifier on keywords only to decide which documents to download}
+<<subset.on.keywords>>=
+
+@
+
+\section{Then use classifier on ocr}
+\label{sect:useonocr}
+<<subset.on.ocr.after.keyword>>=
+
+@
+
+Using keywords only we find:
+That of \Sexpr{nrow(unclass_i_1832)} articles returned by search:
+\begin{itemize}
+  \item \Sexpr{nrow(code_these_fromkeywords_ocr)} are designated for coding
+  \item \Sexpr{nrow(do_not_code_these_fromkeywords)} are not coded
+  \item \Sexpr{nrow(download_these_fromkeywords)} are identified for download
+  \item \Sexpr{nrow(unclass_i_1832)-nrow(download_these_fromkeywords)} are rejected without downloading
+
+\end{itemize}
 \section{Assess Naive Bayes selection performance on 4 keywords (binary dfm)}
@@
 @
+\section{Some Case: These Cases have been rejected for coding using Naive Bayes (second stage on keyword classification only)}
+\label{sect:rejectnbprocess}
+<<print.random.not.code.fromkeywords.cases, results='asis'>>=
+
+@
 

### 2018-08-09 other_R_code/article_selection_pilot.R

@@ -3,6 +3,7 @@ library(reportRx) # note using this just for sanitizing LaTex output, not includ
 library(tidyverse)
 library(quanteda)
 library(durhamevp)
+library(RTextTools) # not sure if this is included as part of the durhamevp package
 
 
 ##----selection.pilot.custom.functions----
@@ -248,8 +249,8 @@ code_random_candidate_docs<-get_candidate_documents(cand_document_id = "all", c(
 
 documents_to_latex(code_random_candidate_docs)
 
-##----keyword.to.dfm----
-
+##----subset.on.keywords----
+# here need a join between archivesearches and archivesearch
 all_searches<-get_archivesearches()
 initial_1832_searches<-all_searches%>%
   dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
@@ -264,5 +265,171 @@ res_i_1832<-get_archivesearchresults(archive_search_id = c(73, 81, 85)) %>%
   left_join(all_searches, by=c("archive_search_id"="id")) %>%
   mutate(std_url = sub("download/", "", url))
 
-aa<-searches_to_dfm(res_i_1832)
+download_these_fromkeywords<-classifier_selection_keywords(classdocs[classdocs$election_article==1,], res_i_1832)
+# the unclassified archive search results don't have ocr column
+download_these_fromkeywords_ocr<-get_candidates_fromarchivesearchresults(download_these_fromkeywords)
+
+
+##----subset.on.ocr.after.keyword----
+code_these_fromkeywords_ocr <- classifier_selection_ocr(classified_boolean_returns, download_these_fromkeywords_ocr)
+code_these_fromkeywords <- unclass_i_1832[unclass_i_1832$url %in% c(code_these_fromkeywords_ocr$url, switch_url_format(code_these_fromkeywords_ocr$url)),]
+do_not_code_these_fromkeywords <- unclass_i_1832[!unclass_i_1832$url %in% code_these_fromkeywords$url,]
+
+##----subset.on.keywords.eval.four.words----
+class_corpus<-quanteda::corpus(classdocs[classdocs$election_article==1,], text_field="ocr")
+keywords<-c("election", "riot", "incident", "disturbance")
+class_dfm_4<-quanteda::dfm(class_corpus, select=keywords)
[…]

### 2018-08-10 other_R_code/article_selection_pilot_evaluate_NBkeywordmethods.Rnw
evaluation methods updates

--- 2018-08-09 other_R_code/article_selection_pilot_evaluate_keyword_methods.Rnw
@@
 
-\section{Download Classified Cases}
-There is an initial set of cases which represent the concept (in this case `election violence').
-We also have a set of cases which do not represent the concept (Note: King et al do not have the non-election violence cases).
-
-I also add indicators that this material is classified (\texttt{classified==1}) and that it is not unclassified (\texttt{unclass==0}) which will be useful when added to subsequent material.
-<<download.R.set, cache=TRUE>>=
+\section{Cases Used}
+We assess on the classified case set (items coded on the platform by users, plus items coded by Gary as non-election, and election non-violent).
+<<download.R.set, cache=TRUE, echo=FALSE>>=
 
@@
 
-\section{How do other classifiers perform on 4 keywords (binary dfm)}
-Is performance improved by using other classifiers than Naive Bayes?
-Here there are four keywords (election, riot, disturbance, incident) which are either present (1) or not-present (0).
-Use these patterns to identify election violence articles.
-<<subset.on.keywords.eval.other.methods.four.words>>=
-
-@
-
 \section{Assess Naive Bayes selection performance on 10 keywords (binary dfm)}
@@
 
-\section{How do other classifiers perform on 10 keywords (binary dfm)}
-\label{sect:eval10other}
-The same but with ten keywords (election, riot, disturbance, incident, mob, stone, window, candidate, party, hustings, magistrate) which are either present (1) or not-present (0).
-Use these patterns to identify election violence articles using a range of other classifiers.
-
-<<subset.on.keywords.eval.other.methods.ten.words>>=
+\section{Assess Naive Bayes selection performance on full set of keywords (binary dfm)}
+Here we take all the keywords in the ocr as a theoretical maximum which are either present (1) or not-present (0).
+Use these patterns to identify election violence articles with a Naive Bayes classifer.
+<<subset.on.keywords.eval.full.words>>=
 

### 2018-08-10 other_R_code/article_selection_pilot.R

@@ -276,7 +276,9 @@ code_these_fromkeywords <- unclass_i_1832[unclass_i_1832$url %in% c(code_these_f
 do_not_code_these_fromkeywords <- unclass_i_1832[!unclass_i_1832$url %in% code_these_fromkeywords$url,]
 
 ##----subset.on.keywords.eval.four.words----
-class_corpus<-quanteda::corpus(classdocs[classdocs$election_article==1,], text_field="ocr")
+cd<-classdocs
+cd<-cd[sample(nrow(cd)),] # random order cases
+class_corpus<-quanteda::corpus(cd, text_field="ocr")
 keywords<-c("election", "riot", "incident", "disturbance")
 class_dfm_4<-quanteda::dfm(class_corpus, select=keywords)
 #class_dfm<-preprocess_corpus(class_corpus, stem=FALSE, min_termfreq = 20)
@@ -287,7 +289,10 @@ quanteda::docvars(the_sets_4$testing_set, "predicted")<-predict(classifier, newd
 caret::confusionMatrix(data=quanteda::docvars(the_sets_4$testing_set, "predicted"), reference=factor(quanteda::docvars(the_sets_4$testing_set, "EV_article")), mode="prec_recall", positive="1")
 
 ##----subset.on.keywords.eval.ten.words----
-class_corpus<-quanteda::corpus(classdocs[classdocs$election_article==1,], text_field="ocr")
+#cd<-classdocs[classdocs$election_article==1,]
+cd<-classdocs
+cd<-cd[sample(nrow(cd)),]
+class_corpus<-quanteda::corpus(cd, text_field="ocr")
 keywords<-c("election", "riot", "incident", "disturbance", "mob", "stone", "window", "candidate", "party", "hustings", "magistrate")
 class_dfm_10<-quanteda::dfm(class_corpus, select=keywords)
 #class_dfm<-preprocess_corpus(class_corpus, stem=FALSE, min_termfreq = 20)
@@ -296,6 +301,18 @@ the_sets_10<-split_dfm(class_dfm_10, n_train = 1000)
 classifier_10<-quanteda::textmodel_nb(the_sets_10$training_set, y=quanteda::docvars(the_sets_10$training_set, "EV_article"), prior="docfreq", distribution="Bernoulli")
 quanteda::docvars(the_sets_10$testing_set, "predicted")<-predict(classifier_10, newdata = the_sets_10$testing_set, type="class")
[…]

### 2018-08-13 R/text_analysis.R
add xgboost methods for keyword classification stage

@@ -209,25 +209,70 @@ has_word <- function(the_dataframe, contains_words, text_col="ocr", results_col=
   return(res)
 }
 
-classifier_select_docs <- function(classifier, new_docs, text_field="description", class_to_keep=1){
+classifier_select_docs <- function(classifier, new_docs, text_field="description", return_logical=FALSE, class_to_keep=1, boolean=TRUE, xgb.cutpoint=.5, stem=FALSE, ...){
   #' Subsets a dataframe of documents based on a classifier.
   #'
-  #' @param classifier The quanteda naive bayes classifier to perform the classification
-  #' @param new_docs A data frame containing the documents to classify
+  #' @param classifier A classifier to perform the classification: either a naive bayes (quanteda) or xgboost (xgboost)
+  #' @param new_docs A data frame or dfm containing the documents to classify
   #' @param text_field The field containing the text to classify
+  #' @param return_logical Should the function return the subset of documents (FALSE) or a logical vector indicating the subset of document (TRUE).
   #' @param class_to_keep The classifier class to keep
-  #' @param ... arguments to be passed to \code{preprocess_corpus}
-  #' @return The subset of the \code{docs_df} which is classified as \code{class_to_keep}
+  #' @param stem stem words (in preprocessing)
+  #' @param ... other arguments to be passed to \code{preprocess_corpus}
+  #' @return Either the subset of the \code{docs_df} which is classified as \code{class_to_keep} or a logical vector indicating this subset (depending on value of \code{return_logical}).
   #' @export
 
-  the_corpus <- quanteda::corpus(new_docs[,c(text_field), drop=FALSE], text_field = text_field)
-  the_dfm<-durhamevp::preprocess_corpus(the_corpus)
-  the_dfm<-quanteda::dfm_select(the_dfm, classifier$x)
-  want_these<-predict(classifier, newdata = the_dfm, type="class")==class_to_keep
+  is.nb<-function(x){
+    "textmodel_nb" %in% class(x)
+  }
 
+  is.xgb<-function(x){
+    "xgb.Booster" %in% class(x)
+  }
+  if(is.dfm(new_docs)){
+    the_dfm <- new_docs
+
+  } else if(is.data.frame(new_docs)){
[…]

### 2018-08-13 other_R_code/article_selection_pilot.R
some experimental code (implementation only - not functions) to run clasifiers apart from naive bayes.

@@ -538,3 +538,154 @@ aa<-nb_keywords(the_sets$training_set, "EV_article")
 table(quanteda::docvars(the_sets$testing_set, c("predicted", "EV_article")))
 chisq.test(table(quanteda::docvars(the_sets$testing_set, c("predicted", "EV_article"))))
 
+
+##----tree----
+library(rpart)
+
+class_corpus<-quanteda::corpus(classdocs[classdocs$election_article==1,], text_field="ocr")
+keywords<-c("election", "riot", "incident", "disturbance", "mob", "stone", "window", "candidate", "party", "hustings", "magistrate")
+class_dfm<-quanteda::dfm(class_corpus, select=keywords)
+the_sets<-split_dfm(class_dfm, n_train = 1000)
+train_df<-convert(dfm_weight(the_sets$training_set, scheme="boolean"), "data.frame")
+train_df$EV_article<-docvars(the_sets$training_set, "EV_article")
+cols<-(names(train_df))
+#train_df<-train_df %>%
+#  mutate_at(cols, factor)
+test_df<-convert(dfm_weight(the_sets$testing_set, scheme="boolean"), "data.frame")
+test_df$EV_article<-docvars(the_sets$testing_set, "EV_article")
+#test_df<-test_df %>%
+#  mutate_at(cols, factor)
+
+
+fit2<-rpart(EV_article~election+disturbance+riot+incident, train_df)
+fit2<-rpart(EV_article~election+candidate+party+disturbance+riot+incident+window+stone+hustings+mob+magistrate,
+            data=train_df,
+            method="class",
+            control=rpart.control(minsplit = 0, cp=.005)
+            )
+fancyRpartPlot(fit2)
+
+test_df$predict<-predict(fit2, test_df, type="class")
+
+table(test_df$EV_article, test_df$predict)
+
+fit_rf<-randomForest(as.factor(EV_article)~document+election+candidate+party+disturbance+riot+incident+window+stone+hustings+mob+magistrate,
+                  data=train_df,
+                  method="class",
+                  ntree=100)
+test_df$predict<-predict(fit_rf, test_df)
+
+table(test_df$EV_article, test_df$predict)
+
+library(xgboost)
+
+params <- list(booster = "gbtree",
+               objective = "binary:logistic",
+               eta=.5,
[…]

### 2018-08-13 other_R_code/article_selection_pilot_evaluate_NBkeywordmethods.Rnw
minor changes to text

@@
 \section{Summary}
-After the code to setup and download data (Sections \ref{sect:packages}-\ref{sect:download1832}) the document below includes:
-First, an implementation of code to select of articles for coding, where initial evaluation of articles is based on keywords from the boolean searches which return those articles (Sections \ref{sect:whichdownloadocr}-\ref{sect:useonocr}).
-This classification is done using actual searches conducted (effectively 4 keywords) with a Naive Bayes classifier.
+The document below includes:
+Evaluates of the selection of articles using keywords with Naive Bayes with 4, 10 and all keyword sets.
 
-Second, the document then provides an evaluation of the keyword selection step based on user classified articles from the platform with Naive Bayes and other classifiers and with 4 and 10 keyword sets (Sections \ref{sect:eval4nb}-\ref{sect:eval10other}).
-
-Finally, to provide an alternative way of evaluating the process, the document includes 10 randomly selected cases which are rejected for coding in the implementation code (Section \ref{sect:rejectnbprocess}).
-
-\section{Packages used}
 \label{sect:packages}
@@
 
-<<pilot.packages, warning=FALSE, message=FALSE>>=
+<<pilot.packages, echo=FALSE, warning=FALSE, message=FALSE>>=
 

### 2018-08-14 other_R_code/article_selection_pilot.R
fix print function

@@ -7,20 +7,24 @@ library(RTextTools) # not sure if this is included as part of the durhamevp pack
 
 
 ##----selection.pilot.custom.functions----
-documents_to_latex<-function(out_docs){
+documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRUE){
   for (doc in 1:nrow(out_docs)){
-    cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (candidate\\_document\\_id: ", out_docs[doc, "id"], ")}"))
+    cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")}"))
     cat(paste0("  \n"))
-    cat(paste0("\\subsubsection{description}"))
-    cat(paste0("  \n"))
-    #cat(Hmisc::latexTranslate(out_docs[doc, "description"]))
-    #knitr::knit_print(out_docs[doc, "description"])
-    cat(reportRx::sanitizestr(out_docs[doc, "description"]))
-    cat(paste0("\\subsubsection{OCR}"))
-    cat(paste0("  \n"))
-    #knitr::knit_print(out_docs[doc, "ocr"])
-    cat(reportRx::sanitizestr(out_docs[doc, "ocr"]))
-    cat("  \n")
+    if(include_description){
+      cat(paste0("\\subsubsection{description}"))
+      cat(paste0("  \n"))
+      #cat(Hmisc::latexTranslate(out_docs[doc, "description"]))
+      #knitr::knit_print(out_docs[doc, "description"])
+      cat(reportRx::sanitizestr(out_docs[doc, "description"]))
+    }
+    if(include_ocr){
+      cat(paste0("\\subsubsection{OCR}"))
+      cat(paste0("  \n"))
+      #knitr::knit_print(out_docs[doc, "ocr"])
+      cat(reportRx::sanitizestr(out_docs[doc, "ocr"]))
+      cat("  \n")
+    }
   }
 }
 
@@ -52,12 +56,14 @@ classdocs<-classdocs %>%
   dplyr::mutate(std_url = sub("download/", "", url)) %>%
   dplyr::mutate(unclass=0, classified=1)
 
+##----download.candocs----
 # also get candidate documents for description classification purposes
 candocs<-get_candidate_documents("all")
 actdocs<-get_document("all")
 candocs$status2<-candocs$status
[…]

### 2018-08-14 other_R_code/article_selection_pilot_description_examples.Rnw
update xgboost/nb test

\documentclass{article}
\usepackage[margin=1in]{geometry}
\title{Low Hanging Fruit: Descriptions of 1841 from the results returned by the new keyword searches}
\begin{document}
\maketitle

\label{sect:packages}
<<setuppath, echo=FALSE, results="hide", echo=FALSE>>=
dropbox.path<-switch (Sys.info()["nodename"],
                      "DM-GIA-051"="D:/Dropbox",
                      "DM-GIA-055"="D:/Dropbox",
                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")

project.path<-paste0(dropbox.path, "/ESRC Grant EV 19th Century")

knitr::read_chunk(paste0(project.path, "/Code/durhamevp/other_R_code/article_selection_pilot.R"))
options(tidy=TRUE, width=50)
@

<<resetdb, echo=FALSE, results='hide', message=FALSE>>=
# Is this necessary because of cached results below? Otherwise sometime get error messages like Corrupt MySQL handle
durhamevp::killDbConnections()

@

<<selection.pilot.custom.functions, echo=FALSE>>=

@

<<pilot.packages, warning=FALSE, message=FALSE, echo=FALSE>>=

@

<<resetdbagain, echo=FALSE, results='hide', message=FALSE>>=
# Is this necessary because of cached results below? Otherwise sometime get error messages like Corrupt MySQL handle
durhamevp::killDbConnections()

@

<<download.R.set, cache=TRUE, echo=FALSE>>=

@

<<download.candocs, cache=TRUE, echo=FALSE>>=

@

<<subset.on.description.1841.data, cache=TRUE, echo=FALSE, message=FALSE, results='hide'>>=

@

Below are two randomly selected sets of articles from the two classificaiton methods. Which is the better set of articles?
\section{First Set}
<<printdoc1, results='asis', echo=FALSE>>=
doc1<-dplyr::sample_n(select_descript_xgb, 30)

documents_to_latex(doc1, include_ocr=FALSE)
@

\section{Second Set}
<<printdoc2, results='asis', echo=FALSE>>=
doc2<-dplyr::sample_n(select_descript_nb, 30)
documents_to_latex(doc2, include_ocr=FALSE)

@

\end{document}

### 2018-08-14 other_R_code/article_selection_pilot_description_nb_examples.Rnw
update xgboost/nb test

--- 2018-08-14 other_R_code/article_selection_pilot_description_examples.Rnw
@@
 doc2<-dplyr::sample_n(select_descript_nb, 30)
-documents_to_latex(doc2, include_ocr=FALSE)
+documents_to_latex(doc1, include_ocr=FALSE)
 

### 2018-08-14 other_R_code/article_selection_pilot.R

@@ -43,6 +43,10 @@ switch_url_format<-Vectorize(function(url){
   }
   switch_url
 })
+url_to_id<-function(url){
+  str_split(url, )
+
+}
 ##----initial.keywords----
 # election riot, election incident, election disturbance
 
@@ -307,11 +311,11 @@ select_descript_nb<-classifier_selection_description(candocs.r, res_i_1841, clas
 
 #select_descript_xgb$description
 #select_descript_nb$description
-# the unclassified archive search results don't have ocr column
-#xgb_cand_docs<-get_candidates_fromarchivesearchresults(select_descript_xgb)
+
+##----subset.on.description.1841.link.cand.doc----
+xgb_cand_docs<-get_candidates_fromarchivesearchresults(select_descript_xgb)
 
 #nb_cand_docs<-get_candidates_fromarchivesearchresults(select_descript_nb)
-
 
 ##----subset.on.ocr.after.keyword----
 code_these_fromkeywords_ocr <- classifier_selection_ocr(classified_boolean_returns, download_these_fromkeywords_ocr)

### 2018-08-14 other_R_code/article_selection_pilot.R
remove misleading comment

@@ -298,10 +298,7 @@ initial_1841_searches<-all_searches%>%
                             "riot", "disturbance", "incident", "mob", "rough", "adjourn",
                             "prison", "police"))
 
-# a number of precisely duplicated searches here which return precisely duplicated results - we could handle this later on but here probably simplest to just use three distinct ones
-# election riot - id 73
-# election disturbance - id 81
-# election incident - id 85
+
 res_i_1841<-get_archivesearchresults(archive_search_id = initial_1841_searches$id) %>%
   left_join(all_searches, by=c("archive_search_id"="id")) %>%
   mutate(std_url = sub("download/", "", url))

### 2018-08-14 R/database_interactivity.R
enable candidate document download without ocr

@@ -251,15 +251,23 @@ get_document<-function(document_id){
   documents
 }
 
-get_candidate_documents<-function(cand_document_id, url="all"){
+get_candidate_documents<-function(cand_document_id, url="all", include_ocr=TRUE){
   #' Returns the candidate document table filtered by candidate document id
   #'
+  #'Note that excluding the ocr from the download will significantly reduce the time for the query to execute.
   #' @param cand_document_id Candidate document id or ids to filter by.
   #' @param url document url or urls to filter by.
+  #' @param include_ocr should the ocr be downloaded.
   #' @export
 
   con <- manage_dbcons()
-  this_sql<-"SELECT * FROM portal_candidatedocument" # base query
+  if(include_ocr){
+    this_sql<-"SELECT * FROM portal_candidatedocument" # base query with ocr
+  } else {
+
+    this_sql<-"SELECT id, title, url, description, publication_title, publication_location, type, status, page, publication_date, word_count FROM portal_candidatedocument" # base query without ocr
+
+  }
 
   res<-build_where_condition("id", cand_document_id, this_sql, NULL)
   res<-build_where_condition("url", url, res$condition, res$interpolate_list)

### 2018-08-14 R/text_analysis.R
restrict cases for classification in get_candidates_fromarchivesearchresults plus some documentation cleanup

@@ -18,19 +18,6 @@ status_to_text<-function(status){
   )
 }
 
-#' preprocess_corpus<-function(the_corpus, min_termfreq=2, min_docfreq=2, max_termfreq=NULL, max_docfreq=NULL,
-#'                             remove_punct=TRUE, remove_numbers=TRUE, remove_hyphens=TRUE, termfreq_type="count", docfreq_type="count",
-#'                             dfm_tfidf=FALSE){
-#'   #' Preprocess a text corpus and return a document feature matrix (wrapper round quanteda functions).
-#'   #' @param the_corpus The text corpus to be pre-processed.
-#'   #' @export
-#'   the_dfm <- quanteda::dfm(the_corpus, stem=TRUE, remove=quanteda::stopwords("english"), remove_punct=remove_punct, remove_numbers=remove_numbers, remove_hyphens=remove_hyphens)
-#'   the_dfm <- quanteda::dfm_trim(the_dfm, min_termfreq=min_termfreq, min_docfreq = min_docfreq, termfreq_type=termfreq_type, docfreq_type=docfreq_type)
-#'   if(dfm_tfidf){
-#'     the_dfm<-quanteda::dfm_tfidf(the_dfm)
-#'   }
-#'   the_dfm
-#' }
 
 split_dfm <- function(dfm, n_train){
   #' Divide a document feature matrix into training and testing sets based on number of training items
@@ -274,8 +261,18 @@ classifier_select_docs <- function(classifier, new_docs, text_field="description
 }
 
 
-classifier_selection_description<-function(train, new_docs, text_field="description", class_to_keep=1, training_classify_var="EV_article", prior="uniform", classifier_type="xgboost", stem=TRUE, ...){
-  #' @param ... other arguments to be passed to \code{preprocess_corpus}
+classifier_selection_description<-function(train, new_docs, text_field="description", class_to_keep=1, training_classify_var="EV_article", prior="uniform", classifier_type="xgboost", stem=TRUE, return_logical=FALSE, ...){
+  #' Classifies new documents based on a labeled training set.
+  #' @param train a data frame with the training documents.
+  #' @param new_docs the documents to classify.
+  #' @param text_field the text field (must be the same in the training documents and the documents to classify).
+  #' @param class_to_keep the class (0 or 1) to keep.
+  #' @param training_classify_var the variable containing the labels in the training set.
+  #' @param prior for naive bayes classifier only.
[…]

### 2018-08-14 other_R_code/article_selection_pilot.R
workout small issues

@@ -44,8 +44,7 @@ switch_url_format<-Vectorize(function(url){
   switch_url
 })
 url_to_id<-function(url){
-  str_split(url, )
-
+  str_split(url, "bl/", simplify=TRUE)[,2]
 }
 ##----initial.keywords----
 # election riot, election incident, election disturbance
@@ -311,7 +310,14 @@ select_descript_nb<-classifier_selection_description(candocs.r, res_i_1841, clas
 
 ##----subset.on.description.1841.link.cand.doc----
 xgb_cand_docs<-get_candidates_fromarchivesearchresults(select_descript_xgb)
+xgb_cand_docs$status<-1
 
+
+dim(select_descript_xgb)
+select_descript_xgb %>%
+  group_by(bna_id) %>%
+  summarize(status=max(EV_article))
+aa<-left_join(select_descript_xgb, xgb_cand_docs, by="bna_id")
 #nb_cand_docs<-get_candidates_fromarchivesearchresults(select_descript_nb)
 
 ##----subset.on.ocr.after.keyword----

### 2018-08-14 R/text_analysis.R
comment cleanup

@@ -262,7 +262,7 @@ classifier_select_docs <- function(classifier, new_docs, text_field="description
 
 
 classifier_selection_description<-function(train, new_docs, text_field="description", class_to_keep=1, training_classify_var="EV_article", prior="uniform", classifier_type="xgboost", stem=TRUE, return_logical=FALSE, ...){
-  #' Classifies new documents based on a labeled training set.
+  #' Classifies new documents on a labeled training set (description).
   #' @param train a data frame with the training documents.
   #' @param new_docs the documents to classify.
   #' @param text_field the text field (must be the same in the training documents and the documents to classify).
@@ -286,7 +286,8 @@ classifier_selection_description<-function(train, new_docs, text_field="descript
 }
 
 classifier_selection_ocr<-function(train, new_docs, text_field="ocr", class_to_keep=1, training_classify_var="EV_article", prior="uniform", return_logical=FALSE){
-  #'
+
+  #' Classifies new documents on a labeled training set (description)
   #' @export
   train_corpus<-quanteda::corpus(train[,c(text_field, training_classify_var)], text_field = text_field)
   train_dfm<-durhamevp::preprocess_corpus(train_corpus)
@@ -343,8 +344,8 @@ classifier_selection_keywords<-function(train, archivesearchresults, class_to_ke
   #'\code{classifier_selection_keyword} uses a classifier to select document from keywords.
   #'In 'select' mode the keywords are constructed from the archivesearchresults. In 'eval' mode the keywords are taken from the eval_options and a binary dfm is constructed from the document text.
   #'@param train the training set of documents
-  #'@classifier_type The type of classifer to use ("nb" = naive bayes, "xgboost"=xgboost)
-  #'@mode Should the documents be selected ("select") or the document selection be evaluated ("eval"), (evaluation assumes search results have been classified)
+  #'@param classifier_type The type of classifer to use ("nb" = naive bayes, "xgboost"=xgboost)
+  #'@param mode Should the documents be selected ("select") or the document selection be evaluated ("eval"), (evaluation assumes search results have been classified)
   #'@export
 
 
@@ -386,6 +387,8 @@ classifier_selection_keywords<-function(train, archivesearchresults, class_to_ke
 
 evp_classifiers<-function(train_dfm, classifier_type, training_classify_var, prior){
   #' wrappers round classifiers
+  #'
+  #' @export
   if(classifier_type=="nb"){
[…]

### 2018-08-14 R/database_interactivity.R
filter candidate document by status

@@ -251,12 +251,13 @@ get_document<-function(document_id){
   documents
 }
 
-get_candidate_documents<-function(cand_document_id, url="all", include_ocr=TRUE){
+get_candidate_documents<-function(cand_document_id="all", url="all", status="all", include_ocr=TRUE){
   #' Returns the candidate document table filtered by candidate document id
   #'
   #'Note that excluding the ocr from the download will significantly reduce the time for the query to execute.
   #' @param cand_document_id Candidate document id or ids to filter by.
   #' @param url document url or urls to filter by.
+  #' @param status document classification status to filter by.
   #' @param include_ocr should the ocr be downloaded.
   #' @export
 
@@ -271,6 +272,7 @@ get_candidate_documents<-function(cand_document_id, url="all", include_ocr=TRUE)
 
   res<-build_where_condition("id", cand_document_id, this_sql, NULL)
   res<-build_where_condition("url", url, res$condition, res$interpolate_list)
+  res<-build_where_condition("status", status, res$condition, res$interpolate_list)
   res[["condition"]] <- paste(res[["condition"]], ";")
   this_sql<-res[["condition"]]
   interpolate_list <- res[["interpolate_list"]]

### 2018-08-14 R/text_analysis.R
add missing environments

@@ -393,7 +393,7 @@ evp_classifiers<-function(train_dfm, classifier_type, training_classify_var, pri
     classifier<-quanteda::textmodel_nb(train_dfm, y=quanteda::docvars(train_dfm, training_classify_var), prior=prior)
 
   } else if (classifier_type=="xgboost"){
-    train_dfms <- split_dfm(train_dfm, n_train=floor(nrow(train_dfm)*.8))
+    train_dfms <- durhamevp::split_dfm(train_dfm, n_train=floor(nrow(train_dfm)*.8))
     dtrain <- durhamevp::dfm_to_dgCMatrix(train_dfms$training_set, training_classify_var = training_classify_var)
     dval <- durhamevp::dfm_to_dgCMatrix(train_dfms$testing_set, training_classify_var = training_classify_var)
     classifier<-xgboost::xgb.train(data=dtrain, nrounds=1000, print_every_n = 20, early_stopping_rounds = 10, maximize = F, eval_metric="error", verbose = 1, watchlist=list(val=dval, train=dtrain))
@@ -407,11 +407,11 @@ dfm_to_dgCMatrix<-function(the_dfm, boolean=FALSE, training_classify_var="EV_art
   #'@export
 
   if(boolean){
-    the_dfm<-dfm_weight(the_dfm, scheme="boolean")
+    the_dfm<-quanteda::dfm_weight(the_dfm, scheme="boolean")
   }
   the_dgCMatrix<-as(the_dfm, "dgCMatrix")
 
-  the_labels<-docvars(the_dfm, training_classify_var)
+  the_labels<-quanteda::docvars(the_dfm, training_classify_var)
 
   the_dgCMatrix<-xgboost::xgb.DMatrix(data=the_dgCMatrix, label=the_labels)
 

### 2018-08-14 R/text_analysis.R
add environment

@@ -216,7 +216,7 @@ classifier_select_docs <- function(classifier, new_docs, text_field="description
   is.xgb<-function(x){
     "xgb.Booster" %in% class(x)
   }
-  if(is.dfm(new_docs)){
+  if(quanteda::is.dfm(new_docs)){
     the_dfm <- new_docs
 
   } else if(is.data.frame(new_docs)){

### 2018-08-14 R/text_analysis.R
add environment

@@ -227,7 +227,7 @@ classifier_select_docs <- function(classifier, new_docs, text_field="description
   }
 
   if(boolean){
-    the_dfm<-dfm_weight(the_dfm, scheme="boolean")
+    the_dfm<-quanteda::dfm_weight(the_dfm, scheme="boolean")
   }
 
 

### 2018-08-15 vignettes/Article_Classification.R
automated doc changes

@@ -1,0 +1,130 @@
+## ----setup, include = FALSE----------------------------------------------
+knitr::opts_chunk$set(
+  collapse = TRUE,
+  comment = "#>"
+)
+
+documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRUE, pandoc_output=FALSE){
+  for (doc in 1:nrow(out_docs)){
+    if(pandoc_output){
+      cat("\n\n")
+      cat(paste0("## ", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")"))
+      cat("\n\n")
+    } else {
+      cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")}"))
+      cat(paste0("  \n"))
+    }
+    if(include_description){
+      if(pandoc_output){      
+        cat("\n\n")
+        cat(paste0("### description"))
+        cat("\n\n")
+      } else {
+        cat(paste0("\\subsubsection{description}"))
+        cat(paste0("  \n"))
+      }
+      #cat(Hmisc::latexTranslate(out_docs[doc, "description"]))
+      #knitr::knit_print(out_docs[doc, "description"])
+      cat(reportRx::sanitizestr(out_docs[doc, "description"]))
+      cat("\n\n")
+    }
+    if(include_ocr){
+      if(pandoc_output){
+        cat("\n\n")
+        cat(paste0("### OCR"))
+        cat("\n\n")
+      } else {
+        cat(paste0("\\subsubsection{OCR}"))
+        cat(paste0("  \n"))
+      }
+
+      #knitr::knit_print(out_docs[doc, "ocr"])
+      cat(reportRx::sanitizestr(out_docs[doc, "ocr"]))
+      if(pandoc_output){
+        cat("  ")
+      } else {
+        cat("   \n")
+      }
+    }
+  }
+}
+
+
+## ----message=FALSE, warning=FALSE, echo=FALSE----------------------------
+library(durhamevp)
+
+## also using tidyverse functions
+library(tidyverse)
+
+## ------------------------------------------------------------------------
+candocs<-get_candidate_documents(status =c("0","1", "2", "3", "4", "5", "6", "7", "8"), include_ocr=FALSE)
+
+candocs$EV_article<-ifelse(candocs$status %in% c("1", "3"), 1, 0)
+
+
+## ------------------------------------------------------------------------
[…]

### 2018-08-15 R/text_analysis.R
add documents_to_latex function

@@ -417,3 +417,55 @@ dfm_to_dgCMatrix<-function(the_dfm, boolean=FALSE, training_classify_var="EV_art
 
   the_dgCMatrix
 }
+
+documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRUE, pandoc_output=FALSE){
+  #' Convert dataframe of documents to form suitable for asis printing in knitr or Rmarkdown documents.
+  #'
+  #' @param out_docs data frame containing the following fields: id, title, description (optional), ocr (optional)
+  #' @param include_description include description field in output
+  #' @param include_ocr include ocr field in output
+  #' @param pandoc_output should function produce pandoc output for Rmarkdown (if FALSE the output is LaTex output for knitr).
+  #' @export
+  for (doc in 1:nrow(out_docs)){
+    if(pandoc_output){
+      cat("\n\n")
+      cat(paste0("## ", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")"))
+      cat("\n\n")
+    } else {
+      cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")}"))
+    }
+    cat(paste0("  \n"))
+    if(include_description){
+      if(pandoc_output){
+        cat("\n\n")
+        cat(paste0("### description"))
+        cat("\n\n")
+        cat("  \n")
+      } else {
+        cat(paste0("\\subsubsection{description}"))
+        cat(paste0("  \n"))
+      }
+      #cat(Hmisc::latexTranslate(out_docs[doc, "description"]))
+      #knitr::knit_print(out_docs[doc, "description"])
+      cat(reportRx::sanitizestr(out_docs[doc, "description"]))
+    }
+    if(include_ocr){
+      if(pandoc_output){
+        cat("\n\n")
+        cat(paste0("### OCR"))
+        cat(paste0("  \n"))
+      } else {
+        cat(paste0("\\subsubsection{OCR}"))
+        cat(paste0("  \n"))
+      }
+
+      #knitr::knit_print(out_docs[doc, "ocr"])
+      cat(reportRx::sanitizestr(out_docs[doc, "ocr"]))
+      cat("\n\n")
+      cat("\n\n")
+      cat("  \n")
+    }
+  }
+}
+
+

### 2018-08-15 other_R_code/article_selection_pilot.R
minor changes to code

@@ -7,26 +7,50 @@ library(RTextTools) # not sure if this is included as part of the durhamevp pack
 
 
 ##----selection.pilot.custom.functions----
-documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRUE){
+documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRUE, pandoc_output=FALSE){
   for (doc in 1:nrow(out_docs)){
-    cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")}"))
+    if(pandoc_output){
+      cat("\n\n")
+      cat(paste0("## ", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")"))
+      cat("\n\n")
+    } else {
+      cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")}"))
+    }
     cat(paste0("  \n"))
     if(include_description){
-      cat(paste0("\\subsubsection{description}"))
-      cat(paste0("  \n"))
+      if(pandoc_output){
+        cat("\n\n")
+        cat(paste0("### description"))
+        cat("\n\n")
+        cat("  \n")
+      } else {
+        cat(paste0("\\subsubsection{description}"))
+        cat(paste0("  \n"))
+      }
       #cat(Hmisc::latexTranslate(out_docs[doc, "description"]))
       #knitr::knit_print(out_docs[doc, "description"])
       cat(reportRx::sanitizestr(out_docs[doc, "description"]))
     }
     if(include_ocr){
-      cat(paste0("\\subsubsection{OCR}"))
-      cat(paste0("  \n"))
+      if(pandoc_output){
+        cat("\n\n")
+        cat(paste0("### OCR"))
+        cat(paste0("  \n"))
+      } else {
+        cat(paste0("\\subsubsection{OCR}"))
+        cat(paste0("  \n"))
+      }
+
       #knitr::knit_print(out_docs[doc, "ocr"])
       cat(reportRx::sanitizestr(out_docs[doc, "ocr"]))
+      cat("\n\n")
+      cat("\n\n")
       cat("  \n")
     }
   }
 }
+
+
 
 get_random_candidates<-function(archivesearchresults, n_random){
   the_random<-dplyr::sample_n(archivesearchresults, n_random)

### 2018-08-15 other_R_code/article_selection_pilot.R
small doc changes plus packages

@@ -85,14 +85,11 @@ classdocs<-classdocs %>%
 
 ##----download.candocs----
 # also get candidate documents for description classification purposes
-candocs<-get_candidate_documents("all")
-actdocs<-get_document("all")
-candocs$status2<-candocs$status
-candocs$status2[(candocs$id %in% actdocs$candidate_document_id)]<-"1"
+candocs<-get_candidate_documents(status =c("0","1", "2", "4", "5", "6", "7", "8"), include_ocr=FALSE)
 
-#summary(factor(candocs$status2[(candocs$id %in% actdocs$candidate_document_id)]))
-candocs$EV_article<-ifelse(candocs$status2 %in% c("1", "3"), 1, 0)
-candocs.r<-candocs[candocs$status2 %in% c("1", "3", "7", "8", "0"),]
+candocs$EV_article<-ifelse(candocs$status %in% c("1", "3"), 1, 0)
+
+candocs.r<-candocs[candocs$status %in% c("1", "3", "7", "8", "0"),]
 
 
 ##----initial.1832.results----
@@ -326,8 +323,8 @@ res_i_1841<-get_archivesearchresults(archive_search_id = initial_1841_searches$i
   left_join(all_searches, by=c("archive_search_id"="id")) %>%
   mutate(std_url = sub("download/", "", url))
 
-select_descript_xgb<-classifier_selection_description(candocs.r, res_i_1841, classifier_type = "xgboost")
-select_descript_nb<-classifier_selection_description(candocs.r, res_i_1841, classifier_type = "nb")
+select_descript_xgb<-classifier_selection_description(candocs, res_i_1841, classifier_type = "xgboost")
+select_descript_nb<-classifier_selection_description(candocs, res_i_1841, classifier_type = "nb")
 
 #select_descript_xgb$description
 #select_descript_nb$description

### 2018-08-15 vignettes/Article_Classification.R
don't eval vignette

@@ -1,6 +1,7 @@
 ## ----setup, include = FALSE----------------------------------------------
 knitr::opts_chunk$set(
   collapse = TRUE,
+  eval=FALSE,
   comment = "#>"
 )
 
@@ -51,72 +52,72 @@ documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRU
 
 
 ## ----message=FALSE, warning=FALSE, echo=FALSE----------------------------
-library(durhamevp)
+#  library(durhamevp)
+#  
+#  ## also using tidyverse functions
+#  library(tidyverse)
 
-## also using tidyverse functions
-library(tidyverse)
+## ---- eval=FALSE---------------------------------------------------------
+#  candocs<-get_candidate_documents(status =c("0","1", "2", "4", "5", "6", "7", "8"), include_ocr=FALSE)
+#  
+#  candocs$EV_article<-ifelse(candocs$status %in% c("1", "3"), 1, 0)
+#  
 
-## ------------------------------------------------------------------------
-candocs<-get_candidate_documents(status =c("0","1", "2", "3", "4", "5", "6", "7", "8"), include_ocr=FALSE)
+## ---- eval=FALSE---------------------------------------------------------
+#  all_searches<-get_archivesearches()
+#  
 
-candocs$EV_article<-ifelse(candocs$status %in% c("1", "3"), 1, 0)
+## ---- eval=FALSE---------------------------------------------------------
+#  initial_1841_searches<-all_searches%>%
+#    dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
+#    filter(archive_date_start>lubridate::ymd("1841-01-01"), archive_date_start<lubridate::ymd("1841-12-31")) %>%
+#    filter(search_text %in% c("election", "candidate", "party", "husting", "magistrate",
+#                              "riot", "disturbance", "incident", "mob", "rough", "adjourn",
+#                              "prison", "police"))
+#  
+#  
 
+## ---- eval=FALSE---------------------------------------------------------
+#  res_i_1841<-get_archivesearchresults(archive_search_id = initial_1841_searches$id)
+#  dim(res_i_1841)
 
-## ------------------------------------------------------------------------
-all_searches<-get_archivesearches()
+## ---- eval=FALSE---------------------------------------------------------
+#  res_oneday_1832<-get_archivesearchresults(archive_search_id = c(228:255))
+#  
 
-
[…]

### 2018-08-16 R/text_analysis.R
default exclude also status 1 documents when retriving candidates from search results

@@ -302,12 +302,12 @@ get_candidates_fromarchivesearchresults<-function(archivesearchresults, include_
   #' This is somewhat challenging because sometimes the url has 'download' in sometimes it doesn't
   #' This function includes a hack to find either case.
   #' By default it excludes articles from publications in Ireland and Scotland, and documents already classified
-  #' as 3 (verbatim repeat), 4 (Ireland), 5 (Scotland), 6 (Abroad)
+  #' as 1 (already downloaded), 3 (verbatim repeat), 4 (Ireland), 5 (Scotland), 6 (Abroad)
 
   #' @param archivesearchresults The archive search results (including a url column)
   #' @param include the ocr in the download (will slow down query)
   #' @param restrict_EW remove results published in Republic of Ireland and Scotland
-  #' @param restrict_classified remove results already classified as 3, 4, 5 or 6
+  #' @param restrict_classified remove results already classified as 1, 3, 4, 5 or 6
   #' @return Candidate documents with urls matching the urls in archivesearchresults
   #' @export
 
@@ -318,7 +318,7 @@ get_candidates_fromarchivesearchresults<-function(archivesearchresults, include_
     the_candidates <- dplyr::filter(the_candidates, !grepl('Republic of Ireland|Scotland', publication_location))
   }
   if(restrict_classified){
-    the_candidates <- dplyr::filter(the_candidates, !status %in% c("3", "4", "5", "6"))
+    the_candidates <- dplyr::filter(the_candidates, !status %in% c("1", "3", "4", "5", "6"))
   }
 
   the_candidates
@@ -347,6 +347,9 @@ classifier_selection_keywords<-function(train, archivesearchresults, class_to_ke
   #'@param classifier_type The type of classifer to use ("nb" = naive bayes, "xgboost"=xgboost)
   #'@param mode Should the documents be selected ("select") or the document selection be evaluated ("eval"), (evaluation assumes search results have been classified)
   #'@export
+  #'
+
+  # This code does work but should be changed to run through evp_classifiers function
 
 
   if (mode=="select"){

### 2018-08-16 R/database_interactivity.R
add new columns to get_candidate_documents function

@@ -266,7 +266,7 @@ get_candidate_documents<-function(cand_document_id="all", url="all", status="all
     this_sql<-"SELECT * FROM portal_candidatedocument" # base query with ocr
   } else {
 
-    this_sql<-"SELECT id, title, url, description, publication_title, publication_location, type, status, page, publication_date, word_count FROM portal_candidatedocument" # base query without ocr
+    this_sql<-"SELECT id, title, url, description, publication_title, publication_location, type, status, page, publication_date, word_count, g_status, status_writer FROM portal_candidatedocument" # base query without ocr
 
   }
 

### 2018-09-11 other_R_code/article_selection_pilot_gdh.R
Gary's sandbox version of article selection pilot - for learning use only

@@ -1,0 +1,772 @@
+##----pilot.packages----
+library(reportRx) # note using this just for sanitizing LaTex output, not included in durhamevp package requirements
+library(tidyverse)
+library(quanteda)
+library(durhamevp)
+library(RTextTools) # not sure if this is included as part of the durhamevp package
+
+
+##----selection.pilot.custom.functions----
+documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRUE){
+  for (doc in 1:nrow(out_docs)){
+    cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")}"))
+    cat(paste0("  \n"))
+    if(include_description){
+      cat(paste0("\\subsubsection{description}"))
+      cat(paste0("  \n"))
+      #cat(Hmisc::latexTranslate(out_docs[doc, "description"]))
+      #knitr::knit_print(out_docs[doc, "description"])
+      cat(reportRx::sanitizestr(out_docs[doc, "description"]))
+    }
+    if(include_ocr){
+      cat(paste0("\\subsubsection{OCR}"))
+      cat(paste0("  \n"))
+      #knitr::knit_print(out_docs[doc, "ocr"])
+      cat(reportRx::sanitizestr(out_docs[doc, "ocr"]))
+      cat("  \n")
+    }
+  }
+}
+
+get_random_candidates<-function(archivesearchresults, n_random){
+  the_random<-dplyr::sample_n(archivesearchresults, n_random)
+  the_candidates<-durhamevp::get_candidates_fromarchivesearchresults(the_random)
+
+  the_candidates
+}
+
+switch_url_format<-Vectorize(function(url){
+  if(grepl("viewer/download", url)){
+    switch_url<-sub("viewer/download", "viewer", url)
+  } else if(grepl("viewer/", url)){
+    switch_url<-sub("viewer/", "viewer/download/", url)
+  }
+  switch_url
+})
+url_to_id<-function(url){
+  str_split(url, )
+
+}
+##----initial.keywords----
+# election riot, election incident, election disturbance
+
+##----download.R.set----
+# In fact we have some classified docs non-EV cases here King's R set doesn't contain any non-cases
+# I think we should use our more extensive information here
+
+classdocs<-durhamevp::get_classified_docs()
+
+classdocs<-classdocs %>%
[…]

### 2018-09-11 other_R_code/user_activity_gdh.Rmd
Gary's sandbox version of user activity document, creating user status report - for learning use only

---
title: "User Status Report"
author: "Gidon Cohen"
date: "14 June 2018"
output: html_document
runtime: shiny
---

```{r setup, include=FALSE, results='hide'}
knitr::opts_chunk$set(echo = TRUE)

library(durhamevp)
library(tidyverse)
library(knitr)
killDbConnections <- function () {

  all_cons <- DBI::dbListConnections(RMySQL::MySQL())

  print(all_cons)

  for(con in all_cons) DBI::dbDisconnect(con)

  print(paste(length(all_cons), " connections killed."))

}
killDbConnections()
con<-evdb_connect(password_method = "keyring")
activity<-DBI::dbGetQuery(con, 'select *
                from portal_useractivitylogentry')
doc_allocations<-DBI::dbGetQuery(con, 'select *
                from portal_userdocumentallocation')
documents<-DBI::dbGetQuery(con, 'select *
                from portal_document')
event_report<-DBI::dbGetQuery(con, 'select *
                from portal_eventreport')

```

## Time Taken on Documents

```{r timetaken, echo=FALSE}

inputPanel(
  selectInput("allocation_type", label = "Mode:",
              choices = c("training", "testing", "coding")),
    selectInput("facet_by", label = "Facet by:",
              choices = c("user_id", "document_id"))
)

renderPlot({
  doc_allocations$facet_col <- paste(input$facet_by, doc_allocations[,input$facet_by])

  activity %>%
    left_join(doc_allocations, by=c("allocation_id"="id", "user_id")) %>%
    filter(user_id>7) %>%
    filter(allocation_type==input$allocation_type) %>%
    filter(status=="COMPLETED") %>%
    group_by(user_id, allocation_id, facet_col) %>%
    summarize(start=min(date), end=max(date), time_taken=difftime(end, start)) %>%
    ggplot(aes(time_taken))+
    facet_wrap(~facet_col)+
    geom_histogram()

})
```

## Are Documents in Coding Mode Relevant to Election Violence?

```{r, echo=FALSE, results='asis'}

aa <- doc_allocations %>%
  filter(user_id>7) %>%
  filter(status=="COMPLETED") %>%
  filter(allocation_type=="coding") %>%
  group_by(violent_nature, violent_focus, electoral_nature, geo_relevant, time_relevant) %>%
  tally()

kable(aa)
```

## Is Time Taken in Coding Mode Related to Difficulty and/or Word Count?

```{r echo=FALSE}

time_summary<- activity %>%
  left_join(doc_allocations, by=c("allocation_id"="id", "user_id")) %>%
  left_join(documents, by=c("document_id"="id")) %>%
  filter(user_id>7) %>%
  filter(allocation_type=="coding") %>%
  filter(word_count>0) %>%
  filter(status=="COMPLETED")

time_summary %>%
  group_by(user_id, allocation_id, word_count, violent_nature) %>%
  summarize(start=min(date), end=max(date), time_taken=difftime(end, start), difficulty_ranking=mean(difficulty_ranking)) %>%
  ggplot(aes(time_taken))+
  facet_wrap(~violent_nature)+
  geom_histogram()

time_summary %>%
  group_by(user_id, allocation_id, word_count) %>%
  summarize(start=min(date), end=max(date), time_taken=difftime(end, start), difficulty_ranking=mean(difficulty_ranking)) %>%
  ggplot(aes(difficulty_ranking, time_taken))+
  #ggplot(aes(difficulty_ranking, time_taken))+
  geom_point(position = position_jitter())+
  stat_smooth(method="lm", se=FALSE, alpha=.2, colour="black", aes(group=user_id))+
  stat_smooth(method="lm", se=TRUE)

time_summary %>%
  filter(word_count>0) %>%
  group_by(user_id, allocation_id, word_count) %>%
  summarize(start=min(date), end=max(date), time_taken=difftime(end, start), difficulty_ranking=mean(difficulty_ranking)) %>%
  ggplot(aes(log(word_count), time_taken))+
  geom_point()+
  stat_smooth(method="lm", se=TRUE
  )

```

### 2018-09-11 other_R_code/random_allocations_gdh.R
For records only - each iteration of random allocation from beginning of function use to present.

@@ -1,0 +1,466 @@
+# Random allocation test
+test_coding_group <- c(7, 9)
+test_tranche_docs <- c(266:268)
+allocate_randomly(user_ids = test_coding_group,
+                  set = test_tranche_docs, coder_rate = 1,
+                  allocation_type = "coding", allocated_by = "test_for_deletion",
+                  restrict_to_actual = TRUE, make_assignments = TRUE)
+
+# Random allocation test 2
+test_coding_group <- c(7, 9)
+test_tranche_docs <- c(260:262)
+allocate_randomly(user_ids = test_coding_group,
+                  set = test_tranche_docs, coder_rate = 1,
+                  allocation_type = "coding", allocated_by = "test_for_deletion",
+                  restrict_to_actual = TRUE, make_assignments = TRUE)
+
+# Random allocation 1
+first_coding_group <- c(9, 11)
+first_tranche_docs <- c(208:217)
+allocate_randomly (user_ids = first_coding_group,
+                   set = first_tranche_docs, coder_rate = 2,
+                   allocation_type = "coding", allocated_by = "regular_random_assignment",
+                   restrict_to_actual = TRUE, make_assignments = TRUE)
+
+# Random allocation 2
+second_coding_group <- c(8:150)
+second_tranche_docs <- c(218:268)
+allocate_randomly(user_ids = second_coding_group,
+                  set = second_tranche_docs, coder_rate = 2,
+                  allocation_type = "coding", allocated_by = "regular_random_assignment",
+                  restrict_to_actual = TRUE, make_assignments = TRUE)
+
+# Random allocation 3
+third_coding_group <- c(8, 9, 11, 12, 15, 16)
+third_tranche_docs <- c(269:361)
+allocate_randomly(user_ids = third_coding_group,
+                  set = third_tranche_docs, coder_rate = 2,
+                  allocation_type = "coding", allocated_by = "regular_random_assignment",
+                  restrict_to_actual = TRUE, make_assignments = TRUE)
+
+# Random allocation 4
+fourth_coding_group <- c(8, 21, 22, 38)
+fourth_tranche_docs <- c(362:420)
+allocate_randomly(user_ids = fourth_coding_group,
+                  set = fourth_tranche_docs, coder_rate = 2,
+                  allocation_type = "coding", allocated_by = "regular_random_assignment",
+                  restrict_to_actual = TRUE, make_assignments = TRUE)
+
[…]

### 2018-09-11 other_R_code/xgboost_process_gdh.R
Iterations of the xgboost categorisation and generation process for 1841, 1832, 1835, and 1837.
Final 1837 version has minor adjustments replacing status with g_status.

@@ -1,0 +1,203 @@
+# Machine Learning 1841
+candocs<-get_candidate_documents(status =c("0","1", "2", "4", "5", "6", "7", "8"), include_ocr=FALSE)
+
+candocs$EV_article<-ifelse(candocs$status %in% c("1", "3"), 1, 0)
+
+all_searches<-get_archivesearches()
+
+initial_1841_searches<-all_searches%>%
+  dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
+  filter(archive_date_start>lubridate::ymd("1841-06-25"), archive_date_start<lubridate::ymd("1841-07-25")) %>%
+  filter(search_text %in% c("election", "candidate", "party", "husting", "magistrate",
+                            "riot", "disturbance", "incident", "mob", "rough", "adjourn",
+                            "prison", "police"))
+
+res_i_1841<-get_archivesearchresults(archive_search_id = initial_1841_searches$id)
+dim(res_i_1841)
+
+res_i_1841 <- res_i_1841 %>%
+  left_join(all_searches, by=c("archive_search_id"="id")) %>%
+  mutate(std_url = sub("download/", "", url))
+
+select_descript_xgb<-classifier_selection_description(candocs, res_i_1841, classifier_type = "xgboost")
+
+dim(select_descript_xgb)
+
+xgb_cand_docs<-get_candidates_fromarchivesearchresults(select_descript_xgb)
+
+
+knitr::kable(head(xgb_cand_docs[xgb_cand_docs$status!="1"|is.na(xgb_cand_docs$status), c("status", "description")]))
+
+xgb_cand_docs$status<-1
+
+xgb_cand_docs$status_writer<-"xgboost_description"
+
+
+
+to_csv<-xgb_cand_docs[,c("id", "url", "publication_title", "description", "status", "g_status", "title", "status_writer")]
+csv_filename<-gsub(" ", "_", paste0("britishnewspaperarchive_", Sys.time(), ".csv"))
+csv_filename<-gsub(":", "_", csv_filename)
+write.csv(to_csv, file=csv_filename, row.names=FALSE)
+
+getwd()
+
+
+
+# Write different sort of csv - see the descriptions the classifier is basing its judgement on
+write.csv(select_descript_xgb[,c("url", "description")], "checkit.csv", row.names=FALSE)
+
+
+
+
+
+
+
+
+# Machine Learning 1832
[…]

### 2018-09-11 other_R_code/database_general_gdh.R
Minor changes to basic functions.
Initial experiments for 'OTD' and 'ArticlesNeeded' functions in Sandbox area below line 147.

@@ -41,23 +41,23 @@ View(user7allocations)
 
 
 # reassign userdoc allocations
-reallocate_randomly(c(9, 16, 21), 4553:4860,
+reallocate_randomly(c(8, 11, 16, 19, 31, 39, 40), 4890:6126,
                     allocated_by = "random_reassignment", restrict_to_actual = TRUE,
                     make_assignments = TRUE, force = FALSE)
 
 
-usergroupresults2 <- get_allocation(8:47, allocation_type = "coding", document_id = 2113:2368)
+usergroupresults2 <- get_allocation(8:47, allocation_type = "coding", document_id = 2401:3608)
 View(usergroupresults2)
 
 
 # View individual user allocations (with scores)
-usergroupresults <- get_allocation(33, allocation_type = "coding", document_id = "all")
+usergroupresults <- get_allocation(27, allocation_type = "coding", document_id = "all")
 View(usergroupresults %>% filter(status == "NEW"))
 View(usergroupresults %>% filter(status == "COMPLETED"))
 View(usergroupresults)
 
 # View xgboost results
-usergroupresults <- get_allocation(8, allocation_type = "coding", document_id = 3170:3608)
+usergroupresults <- get_allocation(11, allocation_type = "coding", document_id = 3170:3608)
 View(usergroupresults %>% filter(status == "COMPLETED"))
 
 View(usergroupresults %>% filter(status == "NEW"))
@@ -76,7 +76,7 @@ View(user7)
 
 
 # Switch coders from training-testing, testing-coding, coding-checking
-set_user_mode (10,  new_mode = "training")
+set_user_mode (48,  new_mode = "testing")
 
 
 #Assign test set to user(s)
@@ -162,6 +162,45 @@ docs<-get_document(document_id="all")
 View(docs)
 
 
-eventreport <- get_event_report("ALL")
-View(eventreport)
+eventreports <- get_event_report("all")
+View(eventreports[c ("event_timeframe_quantifier", "event_start", "event_end", "summary")])
 
+OTDeventreports <- eventreports %>%
+  select(event_start, matches("01/02"))
+View(OTDeventreports)
+
+
+
+
+%>%
+  starts_with(event_start=="01/02")
+  filter(event_start=="01/02")
+
+
+
+
+
+articlesleft <- get_allocation(8:48, allocation_type = "coding", document_id = "all")
[…]

### 2018-09-21 R/Reporting/coder_matching_report.Rmd
Commit to change branch

---
title: "User Matched Scoring Report"
author: "Gidon Cohen"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output: html_document
---

```{r setup, include=FALSE, echo=FALSE, message=FALSE, results='hide', warning=FALSE}
library(magrittr)
library(tidyverse)
dropbox.path<-switch (Sys.info()["nodename"],
                      "DM-GIA-051"="D:/Dropbox",
                      "DM-GIA-055"="D:/Dropbox",
                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")

project.path<-paste0(dropbox.path, "/ESRC Grant EV 19th Century")
match_data_path<-paste0(project.path, "/Code/database_interactivity/reporting/coder_scoring/data")

knitr::read_chunk(paste0(project.path, "/Code/database_interactivity/reporting/coder_scoring/analyse_matches.R"))
```

```{r readdata, echo=FALSE, warning=FALSE}

```

## Overall Summary of Matching by Variable

```{r overallagreement, echo=FALSE, warning=FALSE}

```

## Individual Users Contribution to Coding Agreement (Document Allocation Variables)

```{r linearuserdoc, echo=FALSE, warning=FALSE}

```

## Individual Users Contribution to Coding Agreement (All Variables)

```{r linearall, echo=FALSE, warning=FALSE}

```

## Summary of agreement by user

```{r agreementsummarybyuser, results='asis', warning=FALSE, echo=FALSE}

```

### 2018-09-21 R/Reporting/analyse_matches.R

@@ -1,0 +1,93 @@
+##----readdata----
+dropbox.path<-switch (Sys.info()["nodename"],
+                      "DM-GIA-051"="D:/Dropbox",
+                      "DM-GIA-055"="D:/Dropbox",
+                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
+                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")
+
+project.path<-paste0(dropbox.path, "/ESRC Grant EV 19th Century")
+match_data_path<-paste0(project.path, "/Code/database_interactivity/reporting/coder_scoring/data")
+
+long_coding_agreements<-read.csv(paste0(match_data_path, "/long_coding_agreements.csv")) %>%
+  dplyr::mutate(match_type=factor(match_type, c("user_doc", "ev_report", "tags", "attributes")))
+
+
+##----overallagreement----
+overall_match <- long_coding_agreements %>%
+  drop_na(agree) %>%
+  dplyr::group_by(match_type, variable) %>%
+  dplyr::summarize(cases= sum(agree)+sum(!agree), agreement_rate=sum(agree)/(cases)) %>%
+  ungroup() %>%
+  dplyr::mutate(var_f=factor(variable, variable[order(agreement_rate)])) %>%
+  dplyr::mutate(match_type=factor(match_type, c("user_doc", "ev_report", "tags", "attributes")))
+
+overall_match %>%
+  ggplot(aes(var_f, agreement_rate))+
+  facet_wrap(~match_type, scales="free")+
+  geom_point(aes(size=cases, colour=match_type)) +
+  geom_point()+
+  theme_bw()+
+  ylim(0,1)+
+  theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+##----logsiticsuserdoc----
+flogisticuserdoc<-lme4::glmer(agree~variable + (1|fullname), long_coding_agreements[long_coding_agreements$match_type=="user_doc",], family = "binomial")
+
+user_effects<-cbind(lme4::ranef(flogisticuserdoc)$fullname, arm::se.ranef(flogisticuserdoc)$fullname)
+names(user_effects)<-c("estimate", "se")
+user_effects$fullname<-factor(row.names(user_effects), row.names(user_effects)[order(user_effects$estimate)])
+
+ggplot(user_effects, aes(estimate, fullname))+
+  geom_point() +
[…]

### 2018-09-21 R/Reporting/implement_scoring.R

@@ -1,0 +1,235 @@
+
+all_allocations<-durhamevp::get_allocation() %>%
+  dplyr::filter(status=="COMPLETED")
+
+
+for_analysis<-all_allocations %>%
+  dplyr::group_by(document_id, status=="COMPLETED") %>%
+  dplyr::tally() %>%
+  dplyr::filter(n>1) %>%
+  dplyr::left_join(all_allocations)
+
+# create unique pairs of respondents 
+
+coder_pairs <- for_analysis %>%
+  dplyr::filter(user_id>6) %>%
+  dplyr::filter(id>1800, allocation_type=="coding", status=="COMPLETED") %>%
+  #dplyr::filter(id>1800, allocation_type=="coding") %>%
+  dplyr::group_by(document_id) %>%
+  tidyr::expand(user_id, user_id) %>%
+  dplyr::filter(user_id < user_id1) %>%
+  tibble::rowid_to_column("pair_no")
+
+aa<-coder_pairs %>%
+  tidyr::gather(which_user, user_id, -pair_no, -document_id) %>%
+  dplyr::left_join(all_allocations) %>%
+  tidyr::gather(variable, value, -pair_no, -document_id, -which_user, -user_id, -id) %>%
+  dplyr::select(-user_id, -id) %>%
+  tidyr::spread(which_user, value) %>%
+  dplyr::filter(!variable %in% c("allocated_by", "allocation_date", "allocation_type", "ideal_coding_comments", "score", "status", "article_date_man_verify", "assigned_at", "difficulty_ranking", "last_updated", "coding_complete", "comment", "recommend_qualitative")) %>%
+  dplyr::mutate(agree = user_id == user_id1)
+
+
+all_users<-get_user("all") %>%
+  dplyr::select(id, first_name, last_name)
+analyse_this <- aa %>%
+  dplyr::select(-user_id, -user_id1) %>%
+  dplyr::left_join(coder_pairs) %>%
+  tidyr::gather(which_user, user_id, user_id, user_id1) %>%
+  dplyr::left_join(all_users, by=c("user_id"="id")) %>%
+  tidyr::unite(fullname, first_name, last_name)
+
+
+overall_match <- analyse_this %>%
+  dplyr::group_by(variable) %>%
+  dplyr::summarize(cases= sum(agree)+sum(!agree), agreement_rate=sum(agree)/(cases)) %>%
[…]

### 2018-09-21 R/Reporting/match_records.R

@@ -1,0 +1,37 @@
+dropbox.path<-switch (Sys.info()["nodename"],
+                      "DM-GIA-051"="D:/Dropbox",
+                      "DM-GIA-055"="D:/Dropbox",
+                      "GIDON-ASUS-15"="C:/Users/Gidon/Dropbox",
+                      "GID-HOME-LENOVO"="C:/Users/Gidon/Dropbox")
+
+project.path<-paste0(dropbox.path, "/ESRC Grant EV 19th Century")
+match_data_path<-paste0(project.path, "/Code/database_interactivity/reporting/coder_scoring/data")
+
+
+all_coding_matches<-extract_coding_matches()
+
+uda<-find_agreement_from_matches(all_coding_matches, "user_doc")
+eva<-find_agreement_from_matches(all_coding_matches, "ev_report")
+ta<-find_agreement_from_matches(all_coding_matches, "tags")
+atta<-find_agreement_from_matches(all_coding_matches, "attributes")
+
+coding_agreement <- bind_rows(uda,
+                              eva,
+                              ta,
+                              atta)
+
+
+all_users<-get_user("all") %>%
+  dplyr::select(id, first_name, last_name)
+
+long_coding_agreements <- coding_agreement %>%
+  tidyr::gather(which_user, user_id, user_id, user_id1) %>%
+  dplyr::left_join(all_users, by=c("user_id"="id")) %>%
+  tidyr::unite(fullname, first_name, last_name) %>%
+  dplyr::mutate(stype = substr(match_type, 1, 2)) %>%
+  tidyr::unite(variable, variable, stype)
+
+write.csv(long_coding_agreements, paste0(match_data_path, "/long_coding_agreements.csv"))
+
+nmm<-matrix(c(1,1,NA,1,2,2,3,2,3,3,3,3,3,3,3,3,2,2,2,2,1,2,3,4,4,4,4,4,
+              1,1,2,1,2,2,2,2,NA,5,5,5,NA,NA,1,1,NA,NA,3,NA),nrow=4)

### 2018-09-21 other_R_code/database_general_gdh.R

@@ -47,30 +47,31 @@ reallocate_randomly(c(29), 4890:5050,
                     make_assignments = TRUE, force = FALSE)
 
 
-usergroupresults2 <- get_allocation("all", allocation_type = "coding", document_id = 3609:3859)
+usergroupresults2 <- get_allocation("all", allocation_type = "coding", document_id = 3860:4136)
 View(usergroupresults2)
 
 
 # View individual user allocations (with scores)
-usergroupresults <- get_allocation(39, allocation_type = "coding", document_id = "all")
+usergroupresults <- get_allocation(24, allocation_type = "coding", document_id = "all")
 View(usergroupresults %>% filter(status == "NEW"))
 View(usergroupresults %>% filter(status == "COMPLETED"))
 View(usergroupresults)
 
 
-usergroupresults <- get_allocation(8:47, allocation_type = "coding", document_id = 2401:3169)
+usergroupresults <- get_allocation(8:47, allocation_type = "coding", document_id = "all")
 View(usergroupresults %>% filter(status == "NEW", allocated_by == "random_reassignment"))
 
 
 # View Individual Event Reports
 usereventreports <- get_event_report("all")
 usereventreports2 <- usereventreports %>%
-  filter(str_detect(summary, "Westport"))
+  filter(str_detect(event_start, "1885"))
 View(usereventreports2)
+View(usereventreports)
 
 
 # View xgboost results
-usergroupresults <- get_allocation("all", allocation_type = "coding", document_id = 3609:3859)
+usergroupresults <- get_allocation("all", allocation_type = "coding", document_id = 4137:4468)
 View(usergroupresults %>% filter(status == "COMPLETED"))
 
 View(usergroupresults %>% filter(status == "NEW"))

### 2018-09-21 other_R_code/random_allocations_gdh.R

@@ -525,3 +525,27 @@ allocate_randomly_with_some_double_assignment(double_coding_user_ids = sixty_dou
                                               allocation_type = "coding",
                                               allocated_by = "irregular_random_assignment",
                                               restrict_to_actual = TRUE, make_assignments = TRUE)
+
+# Random allocation 61
+sixtyone_coding_group <- c(9, 24, 26, 29, 31, 35, 42, 43)
+sixtyone_tranche_docs <- c(4291:4360)
+allocate_randomly(user_ids = sixtyone_coding_group,
+                  set = sixtyone_tranche_docs, coder_rate = 1.1,
+                  allocation_type = "coding", allocated_by = "regular_random_assignment",
+                  restrict_to_actual = TRUE, make_assignments = TRUE)
+
+# Random allocation 62
+sixtyone_coding_group <- c(24, 31, 39)
+sixtyone_tranche_docs <- c(4361:4391)
+allocate_randomly(user_ids = sixtyone_coding_group,
+                  set = sixtyone_tranche_docs, coder_rate = 1.1,
+                  allocation_type = "coding", allocated_by = "regular_random_assignment",
+                  restrict_to_actual = TRUE, make_assignments = TRUE)
+
+# Random allocation 63
+sixtythree_coding_group <- c(24, 39)
+sixtythree_tranche_docs <- c(4392:4432)
+allocate_randomly(user_ids = sixtythree_coding_group,
+                  set = sixtythree_tranche_docs, coder_rate = 1.1,
+                  allocation_type = "coding", allocated_by = "regular_random_assignment",
+                  restrict_to_actual = TRUE, make_assignments = TRUE)

### 2018-09-21 R/article_assignment.R
fix issues caused by database changes

@@ -16,7 +16,7 @@ assign_article_to_user <- function (document_id, user_id, allocation_type, alloc
   allocated_at <- as.character(Sys.time())
   for (this_user_id in user_id){
     for (this_document_id in document_id){
-      this_sql<-"INSERT INTO portal_userdocumentallocation (document_id, user_id, allocation_date, allocation_type, allocated_by, status, coding_complete, article_type, geo_relevant, time_relevant, electoral_nature, violent_nature, violent_focus, legibility, comment, recommend_qualitative, difficulty_ranking, ideal_coding_comments, score, assigned_at, last_updated) VALUES (?this_document_id, ?this_user_id, ?allocation_date, ?allocation_type, ?allocated_by, ?status, ?coding_complete, '' , '', '', '', '', '', '', '', '', -1, '', -1, ?allocated_at, ?allocated_at) ;"
+      this_sql<-"INSERT INTO portal_userdocumentallocation (document_id, user_id, allocation_date, allocation_type, allocated_by, status, coding_complete, article_type, geo_relevant, time_relevant, electoral_nature, electoralviolence_nature, violence_focus, legibility, comment_docinfo, recommend_qualitative, difficulty_ranking, ideal_coding_comments, score, assigned_at, last_updated) VALUES (?this_document_id, ?this_user_id, ?allocation_date, ?allocation_type, ?allocated_by, ?status, ?coding_complete, '' , '', '', '', '', '', '', '', '', -1, '', -1, ?allocated_at, ?allocated_at) ;"
 
       this_safe_sql<-DBI::sqlInterpolate(DBI::ANSI(), this_sql,
                                          this_document_id=this_document_id,

### 2018-09-21 R/article_assignment.R
fix error from change to database

@@ -16,7 +16,7 @@ assign_article_to_user <- function (document_id, user_id, allocation_type, alloc
   allocated_at <- as.character(Sys.time())
   for (this_user_id in user_id){
     for (this_document_id in document_id){
-      this_sql<-"INSERT INTO portal_userdocumentallocation (document_id, user_id, allocation_date, allocation_type, allocated_by, status, coding_complete, article_type, geo_relevant, time_relevant, electoral_nature, electoralviolence_nature, violence_focus, legibility, comment_docinfo, recommend_qualitative, difficulty_ranking, ideal_coding_comments, score, assigned_at, last_updated) VALUES (?this_document_id, ?this_user_id, ?allocation_date, ?allocation_type, ?allocated_by, ?status, ?coding_complete, '' , '', '', '', '', '', '', '', '', -1, '', -1, ?allocated_at, ?allocated_at) ;"
+      this_sql<-"INSERT INTO portal_userdocumentallocation (document_id, user_id, allocation_date, allocation_type, allocated_by, status, coding_complete, article_type, geo_relevant, time_relevant, electoral_nature, electoralviolence_nature, violence_nature, legibility, comment_docinfo, recommend_qualitative, difficulty_ranking, ideal_coding_comments, score, assigned_at, last_updated) VALUES (?this_document_id, ?this_user_id, ?allocation_date, ?allocation_type, ?allocated_by, ?status, ?coding_complete, '' , '', '', '', '', '', '', '', '', -1, '', -1, ?allocated_at, ?allocated_at) ;"
 
       this_safe_sql<-DBI::sqlInterpolate(DBI::ANSI(), this_sql,
                                          this_document_id=this_document_id,

### 2018-09-21 R/article_assignment.R
Another bug from database changes

@@ -16,7 +16,7 @@ assign_article_to_user <- function (document_id, user_id, allocation_type, alloc
   allocated_at <- as.character(Sys.time())
   for (this_user_id in user_id){
     for (this_document_id in document_id){
-      this_sql<-"INSERT INTO portal_userdocumentallocation (document_id, user_id, allocation_date, allocation_type, allocated_by, status, coding_complete, article_type, geo_relevant, time_relevant, electoral_nature, electoralviolence_nature, violence_nature, legibility, comment_docinfo, recommend_qualitative, difficulty_ranking, ideal_coding_comments, score, assigned_at, last_updated) VALUES (?this_document_id, ?this_user_id, ?allocation_date, ?allocation_type, ?allocated_by, ?status, ?coding_complete, '' , '', '', '', '', '', '', '', '', -1, '', -1, ?allocated_at, ?allocated_at) ;"
+      this_sql<-"INSERT INTO portal_userdocumentallocation (document_id, user_id, allocation_date, allocation_type, allocated_by, status, coding_complete, article_type, geo_relevant, time_relevant, electoral_nature, electoralviolence_nature, violence_nature, legibility, comment_docinfo, recommend_qualitative, difficulty_ranking, ideal_coding_comments, score,last_updated) VALUES (?this_document_id, ?this_user_id, ?allocation_date, ?allocation_type, ?allocated_by, ?status, ?coding_complete, '' , '', '', '', '', '', '', '', '', -1, '', -1, ?allocated_at) ;"
 
       this_safe_sql<-DBI::sqlInterpolate(DBI::ANSI(), this_sql,
                                          this_document_id=this_document_id,
@@ -53,7 +53,7 @@ reassign_article_to_user <- function (user_doc_id, user_id, allocation_type, all
 
   allocated_at <- as.character(Sys.time())
 
-  this_sql<-"UPDATE portal_userdocumentallocation SET user_id=?user_id, allocation_date=?allocation_date, allocation_type=?allocation_type, allocated_by=?allocated_by, status=?status, coding_complete=?coding_complete, assigned_at=?allocated_at, last_updated=?allocated_at WHERE id=?user_doc_id ;"
[…]

### 2018-11-26 R/text_analysis.R
Fix minor bug with namespace

@@ -374,7 +374,7 @@ classifier_selection_keywords<-function(train, archivesearchresults, class_to_ke
     search_dfm<-quanteda::dfm_select(search_dfm, train_dfm)
   } else if (mode=="eval_dfm"){
     search_dfm<-searches_to_dfm(archivesearchresults)
-    docvars(search_dfm, "EV_article")<-eval_options$eval_dfm_classifications
+    quanteda::docvars(search_dfm, "EV_article")<-eval_options$eval_dfm_classifications
     train_dfm<-search_dfm
 
   } else {

### 2019-09-05 R/clustering.R
cluster assignment functions

@@ -115,10 +115,49 @@ assign_autoclusters_to_user <- function(autocluster_ids, user_id){
 
 }
 
+assign_reallocation_to_user <- function(event_report_id, user_id, allocation_date=as.character(Sys.Date()), last_updated=as.character(Sys.time()), completed=0){
+  #' Assign single events to user for reallocation to clusters.
+  #'
+  #' \code{assign_reallocation_to_user} assigns an autodetected cluster to a user for verification.
+  #' @param event_report_id event_report_id of the single events.
+  #' @param user_id Id of the user the the cluster is to be assigned to.
+  #' @param allocation_date Date allocation made (usually today).
+  #' @param last_updated Date record last updated (usually today).
+  #' @param completed Is the cluster verification complete (usually 0 [i.e. not complete])
+
+  #' @export
+
+  con <- manage_dbcons()
+
+  this_sql <- "INSERT INTO portal_userreallocationallocation (allocation_date, completed, last_updated, event_report_id, user_id) VALUES (?allocation_date, ?completed, ?last_updated, ?event_report_id, ?user_id) ;"
+  this_safe_sql <- DBI::sqlInterpolate(DBI::ANSI(),
+                                       this_sql,
+                                       event_report_id = event_report_id,
+                                       user_id = user_id,
+                                       allocation_date = allocation_date,
+                                       last_updated=last_updated,
+                                       completed = completed)
+
+  DBI::dbGetQuery(con, this_safe_sql)
+}
+
+assign_reallocations_to_user <- function(event_report_ids, user_id){
+  #' Assigns mutiple single events for reallocation to clusters to a single user.
+  #'
+  #'@param event_report_ids The autocluster_ids to allocate.
+  #'@param user_id The user id to allocate to.
+  #'@export
+
+  for(n in seq_along(event_report_ids)){
+    assign_reallocation_to_user(event_report_ids[n], user_id)
+  }
+
+}
+
 get_autodetected_cluster_allocations<-function(user_id="all", autodetected_cluster_id="all"){
   #' Get the autodetcted cluster allocations currently allocated to the user.
   #' @param user_id The user_id to check in the database.
-  #' @param autodetected_cluster_id The set of document_ids to include in the allocation
+  #' @param autodetected_cluster_id The set of autodetected cluster ids to check in the database
   #' @return dataframe of the autodetected cluster allocations to the user.
[…]

### 2019-09-05 R/database_interactivity.R
add refs to packages properly

@@ -567,15 +567,15 @@ process_locations <- function(location_tags){
     dplyr::slice(1)
 
   locs<-processed_locationa%>%
-    select(-proximity_relative) %>%
+    dplyr::select(-proximity_relative) %>%
     tidyr::spread(tag_variable, tag_value)
 
   pr<-processed_locationa%>%
-    ungroup() %>%
-    select(-tag_value) %>%
-    mutate(tag_variable=paste0(tag_variable, "_proximity_relative")) %>%
+    dplyr::ungroup() %>%
+    dplyr::select(-tag_value) %>%
+    dplyr::mutate(tag_variable=paste0(tag_variable, "_proximity_relative")) %>%
     tidyr::spread(tag_variable, proximity_relative, fill=0)
-  processed_location <- left_join(locs, pr, by="event_report_id")
+  processed_location <- dplyr::left_join(locs, pr, by="event_report_id")
 
   processed_location
 }

### 2019-09-05 R/clustering.R
small bug fixes

@@ -212,6 +212,8 @@ assign_verified_clusters_to_user <- function(verified_cluster_ids, user_id){
   #'@param user_id The user id to allocate to.
   #'@export
 
+  con <- manage_dbcons()
+
   for(n in seq_along(verified_cluster_ids)){
     assign_verified_cluster_to_user(verified_cluster_ids[n], user_id)
   }
@@ -223,6 +225,8 @@ get_verified_clusters <- function(){
   #'
   #' \code{get_verified_clusters} reports the verified clusters and the event reports currently in that cluster.
   #' @export
+
+  con <- manage_dbcons()
 
   this_sql<-this_sql<-"Select vc.id as verified_cluster_id, user_alloc_id, latitude, longitude, event_report_id
   FROM `portal_verifiedcluster` vc LEFT JOIN `portal_verifiedclusterentry` vce ON vc.id = vce.verified_cluster_id; " # base query

### 2020-06-11 R/database_interactivity.R
database vignette first go

@@ -460,6 +460,9 @@ get_coding <- function(include_ocr=FALSE, restrict_to_coding_complete = TRUE, re
   #'  There are arguments to the function to change these defaults.
   #'
   #' The function also uses a clustering set to make a meaningful event_id, such that every event report with the same event_id is considered to be a report of the same event. In the online version of the database event_id is not implemented (in fact it always takes the value of 1). When the coding is downloaded this will be replaced with a meaningful event_id, by default the second full set of clustering is used to generate this event_id.
+  #'
+  #' For more details see the EV_Database vignette:
+  #' \code{vignette("Database", package = "durhamevp")}
   #' @param include_ocr Should results include the full ocr of the documents (will slow the download).
   #' @param restrict_to_coding_complete Should the data including only records where coding is tagged as complete?
   #' @param restrict_to_coding_mode Should the data include on the records where coders were in coding mode?
@@ -537,8 +540,8 @@ add_event_id_from_clustering <- function(evp_coding_download, event_id_from_clus
   event_reports <- dplyr::select(evp_coding_download[["event_reports"]], -event_id)
   use_clustering <- dplyr::filter(clustering, clusterattempt_id %in% event_id_from_clusterattempts)
   use_clustering <- dplyr::select(use_clustering, event_report_id, event_id = final_cluster_id)
-  use_clustering <- group_by(use_clustering, event_report_id, event_id)
-  use_clustering <- summarize(use_clustering)
+  use_clustering <- dplyr::group_by(use_clustering, event_report_id, event_id)
+  use_clustering <- dplyr::summarize(use_clustering)
 
   # check if every event_report is clustered
   unclustered_event_reports <- dplyr::pull(

### 2020-06-11 R/text_analysis.R

@@ -27,6 +27,8 @@ split_dfm <- function(dfm, n_train){
   #' @param n_train The number of documents in the training set.
   #' @export
   training_set <- quanteda::dfm_sample(dfm, n_train)
+  testing_set <- quanteda::dfm_subset()
+  dfm[setdiff(quanteda::docnames(dfm), quanteda::docnames(training_set))]
   testing_set <- dfm[setdiff(quanteda::docnames(dfm), quanteda::docnames(training_set))]
   return(list(training_set=training_set, testing_set=testing_set))
 }

### 2020-06-11 vignettes/Election_Violence_Database.R
trying to get vignette to load

@@ -1,0 +1,36 @@
+## ----setup, include=FALSE-----------------------------------------------------
+knitr::opts_chunk$set(echo = TRUE)
+# devtools::install_github("bergant/datamodelr")
+library(datamodelr)
+
+## ---- echo=FALSE, fig.height=7, fig.width=7-----------------------------------
+
+
+dm <- datamodelr::dm_read_yaml("evp_erd.yml")
+graph <- dm_create_graph(dm, view_type = "keys_only")
+dm_render_graph(graph)
+
+## ---- echo=FALSE, fig.height=7, fig.width=7-----------------------------------
+
+
+graph <- dm_create_graph(dm, rankdir="RL", focus=list(tables = c("userdocumentallocation", "event_reports", "tag", "attribute")))
+dm_render_graph(graph)
+
+## ---- echo=FALSE, fig.height=7, fig.width=7-----------------------------------
+
+
+graph <- dm_create_graph(dm, focus=list(tables = c("documents", "candidatedocument", "archivesearchsummaryonly", "archivesearchresult", "archivesearch")), rankdir="RL")
+dm_render_graph(graph)
+
+## ---- echo=FALSE--------------------------------------------------------------
+
+
+graph <- dm_create_graph(dm, focus=list(tables = c("user")))
+dm_render_graph(graph)
+
+## ---- echo=FALSE, fig.height=7, fig.width=7-----------------------------------
+
+
+graph <- dm_create_graph(dm, focus=list(tables = c("userreallocationallocation", "userautodetectedclusterallocation", "verifiedcluster", "verifiedclusterentry", "usercombinationallocation", "combinedclusterentry")))
+dm_render_graph(graph)
+

### 2020-06-11 other_R_code/old vignettes that need cleaning/Article_Classification.Rmd
broken vignettes moved to a holding folder

---
title: "Article Classification with Machine Learning 1"
author: "Gidon Cohen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Article Classification with Machine Learning 1}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval=FALSE,
  comment = "#>"
)

documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRUE, pandoc_output=FALSE){
  for (doc in 1:nrow(out_docs)){
    if(pandoc_output){
      cat("\n\n")
      cat(paste0("## ", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")"))
      cat("\n\n")
    } else {
      cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")}"))
      cat(paste0("  \n"))
    }
    if(include_description){
      if(pandoc_output){      
        cat("\n\n")
        cat(paste0("### description"))
        cat("\n\n")
      } else {
        cat(paste0("\\subsubsection{description}"))
        cat(paste0("  \n"))
      }
      #cat(Hmisc::latexTranslate(out_docs[doc, "description"]))
      #knitr::knit_print(out_docs[doc, "description"])
      cat(reportRx::sanitizestr(out_docs[doc, "description"]))
      cat("\n\n")
    }
    if(include_ocr){
      if(pandoc_output){
        cat("\n\n")
        cat(paste0("### OCR"))
        cat("\n\n")
      } else {
        cat(paste0("\\subsubsection{OCR}"))
        cat(paste0("  \n"))
      }

      #knitr::knit_print(out_docs[doc, "ocr"])
      cat(reportRx::sanitizestr(out_docs[doc, "ocr"]))
      if(pandoc_output){
        cat("  ")
      } else {
        cat("   \n")
      }
    }
  }
}

```

## Introduction

This vignette covers the process of article classification using machine learning.

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(durhamevp)

## also using tidyverse functions
library(tidyverse)
```

## Obtain Classified and Unclassified Document Sets and Relate to Systematic Searches

```{r getdocsets}

alldocs<-get_document("all")
alldocs<-alldocs %>%
  dplyr::mutate(std_url = sub("download/", "", url))

docallocs<-get_allocation("all", allocation_type = "coding")

docallocs<-left_join(docallocs, alldocs, by=c("document_id"="id"))

classdocs<-filter(docallocs, coding_complete==1, electoralviolence_nature %in% c("false", "true"))
classdocs<-classdocs %>%
  dplyr::mutate(std_url = sub("download/", "", url)) %>%
  dplyr::mutate(unclass=0, classified=1) %>%
  dplyr::mutate(EV_article=ifelse(electoralviolence_nature=="true", 1, 0))

systematic_search_terms<-c("incident",
                           "riot",
                           "mob",
                           "rough",
                           "disturbance",
                           "husting",
                           "adjourn",
                           "magistrate",
                           "police",
                           "prison",
                           "candidate",
                           "election",
                           "party")
all_searches<-get_archivesearches()
systematic_searches<-all_searches%>%
  dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
  filter(search_text %in% systematic_search_terms)

results_systematic_searches<-get_archivesearchresults(archive_search_id = systematic_searches$id) %>%
  left_join(all_searches, by=c("archive_search_id"="id")) %>%
  mutate(std_url = sub("download/", "", url))

is_classified <-results_systematic_searches$std_url %in% classdocs$std_url

classified_results<-results_systematic_searches[is_classified,]

```
## Train Keyword Classifier

```{r trainkeywordclass}
class_res_dfm<-durhamevp::searches_to_dfm(classified_results)
the_urls<-quanteda::docvars(class_res_dfm, "std_url")
ordered_cr<-classified_results[match(quanteda::docvars(class_res_dfm, "std_url"), classified_results$std_url),]

summary_class <- classdocs %>%
  group_by(std_url, document_id) %>%
  mutate(EV_article=electoralviolence_nature=="true") %>%
  summarize(EV_article=max(EV_article), sum_EV_article=sum(EV_article), n=n())

ordered_classified<-summary_class[match(quanteda::docvars(class_res_dfm, "std_url"), summary_class$std_url),]

quanteda::docvars(class_res_dfm, "EV_article")<-ordered_classified$EV_article

# use 85 per cent of the classified data to train classifier
# the other 15 per cent are used to as the testing set
n_train <- round(nrow(class_res_dfm)*.85)
the_sets<-split_dfm(class_res_dfm, n_train = n_train)
testing_urls<-quanteda::docvars(the_sets$testing_set, "std_url")
training_urls<-quanteda::docvars(the_sets$training_set, "std_url")

# train xgboost keyword classifier
classifier<-durhamevp::evp_classifiers(the_sets$training_set, "xgboost", "EV_article", "uniform")

# train naive bayes keyword classifier
classifier_nb<-durhamevp::evp_classifiers(the_sets$training_set, "nb", "EV_article", "uniform")
```
## Evaluate Classifier on Test Set

Note this step should be regularly implemented to check that performance of classifier is improving not degrading. However, it is not necessary for the process.
```{r}
# add predictions to the training and testing sets
quanteda::docvars(the_sets$training_set, "predicted_keywords")<-predict(classifier, newdata = the_sets$training_set, type="class")
quanteda::docvars(the_sets$testing_set, "predicted_keywords")<-predict(classifier, newdata = the_sets$testing_set, type="class")
quanteda::docvars(the_sets$testing_set, "predicted_keywords_nb")<-predict(classifier_nb, newdata = the_sets$testing_set, type="prob")[,2]

quanteda::docvars(the_sets$testing_set, "pred_class_keywords")<-factor(as.numeric(quanteda::docvars(the_sets$testing_set, "predicted_keywords")>.5))

results_table<-as.data.frame.matrix(caret::confusionMatrix(data=quanteda::docvars(the_sets$testing_set, "pred_class_keywords"), reference=factor(quanteda::docvars(the_sets$testing_set, "EV_article")), mode="prec_recall", positive="1")$table)

## **** probably delete****
tmp_train<-quanteda::docvars(the_sets$training_set)
p1<-ggplot(tmp_train, aes(predicted_keywords, EV_article))+
  geom_point(position=position_jitter(height=.1))+
  stat_smooth(method="glm", method.args = list(family="binomial"))+
  ggtitle("performance of the xgboost keyword classifier on the training set")

tmp_test<-quanteda::docvars(the_sets$testing_set)
p2<-ggplot(tmp_test, aes(predicted_keywords, EV_article))+
  geom_point(position=position_jitter(height=.1))+
  stat_smooth(method="glm", method.args = list(family="binomial"))+
  ggtitle("performance of the xgboost keyword classifier on the testing set")
p2

p3<-ggplot(tmp_test, aes(predicted_keywords_nb, EV_article))+
  geom_point(position=position_jitter(height=.1))+
  stat_smooth(method="glm", method.args = list(family="binomial"))+
  ggtitle("performance of the naive bayes keyword classifier on the testing set")
print(p3)
p4<-ggplot(tmp_test, aes(y=EV_article))+
  geom_point(colour="red", position=position_jitter(height=.1), aes(x=predicted_keywords_nb))+
  stat_smooth(method="glm",colour="red",  method.args = list(family="binomial"), aes(x=predicted_keywords_nb))+
  geom_point(colour="green", position=position_jitter(height=.1), aes(x=predicted_keywords))+
  stat_smooth(method="glm",colour="green",  method.args = list(family="binomial"), aes(x=predicted_keywords))+
  ggtitle("performance of the naive bayes keyword classifier on the testing set")

```

# Use Classifier on Unclassified Cases

We do not examine status 1 or status 3 documents.
```{r}
undownloaded_candidates<-get_candidate_documents(status =c("0", "2", "4", "5", "6", "7", "8", ""), include_ocr=FALSE)
undownloaded_candidates<- undownloaded_candidates %>%
  dplyr::mutate(std_url = sub("download/", "", url))

need_classifying <-results_systematic_searches$std_url %in% undownloaded_candidates$std_url

toclassify_results<-results_systematic_searches[need_classifying,]

toclass_res_dfm<-durhamevp::searches_to_dfm(toclassify_results)
classify_urls<-quanteda::docvars(toclass_res_dfm, "std_url")

toclass_othervars <- toclassify_results %>%
  select(newspaper_title, publication_date, publication_location, type, std_url) %>%
  group_by(std_url,newspaper_title, publication_date, publication_location, type) %>%
  summarize ()

ordered_tcov<-toclass_othervars[match(quanteda::docvars(toclass_res_dfm, "std_url"), toclass_othervars$std_url),]

quanteda::docvars(toclass_res_dfm, "publication_date")<-ordered_tcov$publication_date
quanteda::docvars(toclass_res_dfm, "publication_location")<-ordered_tcov$publication_location
quanteda::docvars(toclass_res_dfm, "newspaper_title")<-ordered_tcov$newspaper_title
quanteda::docvars(toclass_res_dfm, "type")<-ordered_tcov$type

# this step reorders the dfm to have the columns in the same order as the training_set dfm
toclass_res_dfm<-quanteda::dfm_select(toclass_res_dfm, the_sets$training_set)

# this step actually implements the prediction
quanteda::docvars(toclass_res_dfm, "predicted_keywords")<-predict(classifier, newdata = toclass_res_dfm, type="class")

```
# From Document Feature Matrix Results to Candidate Documents Results

The results set contains many references to the same document (perhaps with different descriptions). The next step is to identify the unique candidate documents which these results relate to. Add the classification (where this is a subset the classification is always 1)

```{r}
undownloaded_candidates_with_kwpred<-left_join(undownloaded_candidates, quanteda::docvars(toclass_res_dfm), by=c("std_url", "publication_date", "publication_location", "type"))

# add election name
undownloaded_candidates_with_kwpred<-undownloaded_candidates_with_kwpred %>%
  group_by(publication_date) %>%
  summarise() %>%
  mutate(election_name=date_to_election(publication_date)) %>%
  right_join(undownloaded_candidates_with_kwpred, by="publication_date")

##  If working by election subset to 1874 (or other desired election)

kwclass_1874<-undownloaded_candidates_with_kwpred %>%
  filter(election_name=="1874") %>%
  arrange(-predicted_keywords)

hist(kwclass_1874$predicted_keywords)

kwclass_1874_top5000<-kwclass_1874 %>% 
  slice(1:5000) %>%
  select(id, url, publication_title, description, status, g_status, title, status_writer, predicted_keywords)

kwclass_1874_top5000$status<-1
kwclass_1874_top5000$status_writer<-"xgboost_keyword"

```

## Save results
```{r, eval=FALSE}
to_csv<-kwclass_1874_top5000[,c("id", "url", "publication_title", "description", "status", "g_status", "title", "status_writer", "predicted_keywords")]

csv_filename<-gsub(" ", "_", paste0("britishnewspaperarchive_", format(Sys.time(), "%Y_%m_%d_%H_%M_%S"), ".csv"))

write.csv(to_csv, file=csv_filename, row.names = FALSE)
```

## Download OCR

Then Download OCR of Documents Identified by Keyword Classifier

## Classify OCR: Train Classifier

```{r trainocrclassifier}
#classdocs$ocr
classified_corpus<-quanteda::corpus(classdocs[,c("ocr", "EV_article")], text_field = "ocr")
ocr_class_dfm<-durhamevp::preprocess_corpus(classified_corpus, min_termfreq=20, min_docfreq=20, stem=FALSE)
ocr_sets<-durhamevp::split_dfm(ocr_class_dfm, round(nrow(ocr_class_dfm)*.85))
ocr_classifier<-durhamevp::evp_classifiers(ocr_sets$training_set, classifier_type = "xgboost", training_classify_var = "EV_article")

quanteda::docvars(ocr_sets$testing_set, "ocr_predict_xgb")<-predict(ocr_classifier, ocr_sets$testing_set)
quanteda::docvars(ocr_sets$testing_set, "ocr_predict_class_xgb")<-as.numeric(quanteda::docvars(ocr_sets$testing_set, "ocr_predict_xgb")>.5)

ggplot(quanteda::docvars(ocr_sets$testing_set), aes(ocr_predict_xgb, EV_article))+
  geom_point(position="jitter")+
  geom_smooth(method="glm", method.args=list(family="binomial"))
caret::confusionMatrix(factor(quanteda::docvars(ocr_sets$testing_set, "EV_article")), factor(quanteda::docvars(ocr_sets$testing_set, "ocr_predict_class_xgb")), mode="prec_recall")

```
## Use Classifier on New Material
```{r}
kwclass_1874_top5000$id[1:5]
needs_ocr_classify<-get_candidate_documents(cand_document_id = kwclass_1874_top5000$id, include_ocr = TRUE)

needs_classify_corpus<-quanteda::corpus(needs_ocr_classify, text_field = "ocr")
needs_classify_dfm<-durhamevp::preprocess_corpus(needs_classify_corpus, min_termfreq=20, min_docfreq=20, stem=FALSE)
needs_classify_dfm<-quanteda::dfm_select(needs_classify_dfm, ocr_sets$training_set)

# this step actually implements the prediction
quanteda::docvars(needs_classify_dfm, "predicted_ocr")<-predict(ocr_classifier, newdata = needs_classify_dfm, type="class")

hist(quanteda::docvars(needs_classify_dfm, "predicted_ocr"))

classified_by_ocr<-quanteda::docvars(needs_classify_dfm)
aa<-left_join(classified_by_ocr, select(kwclass_1874_top5000, id, url, predicted_keywords)) %>%
  dplyr::mutate(std_url = sub("download/", "", url)) %>%
  arrange(-predicted_ocr)

ggplot(aa, aes(predicted_ocr))+
  geom_histogram()

ggplot(aa, aes(predicted_keywords, predicted_ocr))+
  geom_point()+
  stat_smooth(method="lm")

bb<-aa[aa$predicted_keywords>.7&aa$predicted_ocr<.1,]

f1<-lm(predicted_ocr~predicted_keywords, aa)
stargazer::stargazer(f1, type="text")
cor(aa$predicted_keywords, aa$predicted_ocr)

importance <- xgboost::xgb.importance(feature_names = colnames(ocr_sets$training_set), model = ocr_classifier)
```
## Save results
```{r}

download_these<-classified_by_ocr[,c("id", "url", "publication_title", "description", "status", "g_status", "title", "status_writer", "predicted_ocr")] %>%
  filter(predicted_ocr>.75) %>%
  mutate(status=1, status_writer="xgb_ocr") %>%
  as_tibble()

csv_filename<-gsub(" ", "_", paste0("britishnewspaperarchive_", format(Sys.time(), "%Y_%m_%d_%H_%M_%S"), ".csv"))

write.csv(download_these, file=csv_filename, row.names = FALSE)
```

## Some more evaluation code

```{r}

top_ones<-quanteda::docvars(toclass_res_dfm, "predicted_keywords")>.9
quanteda::docvars(toclass_res_dfm, "std_url")[top_ones][1:5]

as_df<-as.tbl(quanteda::docvars(toclass_res_dfm)) %>%
  mutate(pubyear=lubridate::year(publication_date))

#system.time(as_df <- as_df %>%
#  mutate(election=date_to_election(publication_date)))

as_df<-as_df %>%
  group_by(publication_date) %>%
  summarise() %>%
  mutate(election_name=date_to_election(publication_date)) %>%
  right_join(as_df, by="publication_date") 
pp1<-as_df %>%
  left_join(election_dates, by="election_name") %>%
  filter(keywords_13_complete=="Y") %>%
  ggplot(aes(election_name, predicted_keywords, group=election_name)) +
  geom_boxplot()

pp1<-as_df %>%
  left_join(election_dates, by="election_name") %>%
  filter(keywords_13_complete=="Y") %>%
  ggplot(aes(election_name, predicted_keywords, group=election_name)) +
  geom_violin(trim=FALSE)

as_df <- as_df %>%
  mutate(electionn=as.numeric(election))

prob_class<-function(x){
  case_when(
    x>.75 ~ "highly likely (>.75)",
    x>.5  ~ "likely (>.5 & <.75)",
    x>.25 ~ "unlikely (<.5 & >.25)",
    x<.25 ~ "very unlikely(<.25)",
    TRUE ~ NA_character_
  )
}
pp4<-as_df %>%
  mutate(prob_EV_keywords=prob_class(predicted_keywords)) %>%
  mutate(electionn=as.numeric(election_name)) %>%
  filter(electionn<1875) %>%
  group_by(election_name, electionn, prob_EV_keywords) %>%
  tally() %>%
  ggplot(aes(electionn, n))+
  facet_wrap(~prob_EV_keywords, scales="free")+
  geom_point()+
  geom_line()+
  ylim(0, NA) +
  ggtitle("Number of Currently Undownloaded Articles in Each Election by EV_Article Likelihood (Keyword Classifier)")

pp2<-as_df %>%
  group_by(electionn) %>%
  tally()%>%
  ggplot(aes(electionn, n)) +
  geom_point() +
  geom_line()
pp2

dim(results_systematic_searches)
rss<-results_systematic_searches %>%
  group_by(publication_date) %>%
  summarise() %>%
  mutate(election_name=date_to_election(publication_date)) %>%
  right_join(results_systematic_searches, by="publication_date")
pp3<-rss %>%
  group_by(election_name, search_text) %>%
  tally()%>%
  mutate(electionn=as.numeric(election_name)) %>%
  left_join(durhamevp::election_dates, by="election_name") %>%
  mutate(articles_per_day=n/monthsearch_duration) %>%
  filter(keywords_13_complete=="Y") %>%
  ggplot(aes(electionn, articles_per_day)) +
  facet_wrap(~search_text, scales="free")+
  geom_point() +
  geom_line() +
  ylim(0, NA) +
  ggtitle("Articles (per day) Containing 13 Systematic Search Terms During Month Around Elections")+
  theme_bw()
pp3
#link to searchers

candocs<-get_candidate_documents(status =c("0","1", "2", "4", "5", "6", "7", "8"), include_ocr=FALSE)

candocs<-candocs %>%
  dplyr::mutate(std_url = sub("download/", "", url))
candocs$EV_article<-ifelse(candocs$g_status %in% c("1", "3"), 1, 0)

candocs_training_set<-candocs[!candocs$std_url %in% testing_urls, ]
candocs_testing_set<-candocs[candocs$std_url %in% testing_urls, ]
descript_test<-classified_results[classified_results$std_url %in% testing_urls,]

select_descript_xgb<-classifier_selection_description(candocs_training_set, descript_test, classifier_type="xgboost", return_logical = TRUE, logical_to_prob=TRUE, stem=FALSE, min_docfreq=20, min_termfreq=20)

descript_test <- descript_test %>%
  mutate(xgb_select=select_descript_xgb)

compare_docs<-descript_test%>%
  inner_join(candocs_testing_set, by="description")

table(compare_docs$xgb_select>.5, compare_docs$g_status)

ggplot(compare_docs, aes(xgb_select, as.numeric(g_status==1)))+
  geom_point(position="jitter")+
  stat_smooth(method="glm", method.args = list(family="binomial"))+
  ggtitle("Performance of the xgboost descrition classifier on the testing set")

compare_docs<-descript_test%>%
  group_by(std_url) %>%
  summarise(maxselect=max(xgb_select)) %>%
  left_join(candocs_testing_set, by="std_url")

check_descript_xgb<-classifier_selection_description(candocs_training_set, candocs_training_set, classifier_type="xgboost", return_logical = TRUE, logical_to_prob=TRUE, stem=FALSE, min_docfreq=50, min_termfreq=50)

descript_test <- candocs_training_set %>%
  mutate(xgb_select=check_descript_xgb)

compare_docs<-descript_test%>%
  inner_join(candocs_training_set, by="description")

table(compare_docs$xgb_select>.5, compare_docs$g_status.x)

ggplot(compare_docs, aes(xgb_select, as.numeric(g_status.x=="1")))+
  geom_point(position="jitter")+
  stat_smooth(method="glm", method.args = list(family="binomial"))+
  ggtitle("Performance of the xgboost descrition classifier on the training set")

```

## View classification results

```{r, results='asis'}
aa<-left_join(needs_ocr_classify, classified_by_ocr, by=c("id", "url")) %>%
  filter(predicted_ocr>.75)
documents_to_latex(sample_n(aa, 30), include_ocr=TRUE, pandoc_output=TRUE)

```

### 2020-06-11 other_R_code/old vignettes that need cleaning/Article_Classification_first_go.Rmd
broken vignettes moved to a holding folder

---
title: "Article Classification with Machine Learning 2"
author: "Gidon Cohen"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Article Classification with Machine Learning 2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  eval=FALSE,
  comment = "#>"
)

documents_to_latex<-function(out_docs, include_description=TRUE, include_ocr=TRUE, pandoc_output=FALSE){
  for (doc in 1:nrow(out_docs)){
    if(pandoc_output){
      cat("\n\n")
      cat(paste0("## ", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")"))
      cat("\n\n")
    } else {
      cat(paste0("\\subsection{", reportRx::sanitizestr(out_docs[doc, "title"]), " (id: ", out_docs[doc, "id"], ")}"))
      cat(paste0("  \n"))
    }
    if(include_description){
      if(pandoc_output){      
        cat("\n\n")
        cat(paste0("### description"))
        cat("\n\n")
      } else {
        cat(paste0("\\subsubsection{description}"))
        cat(paste0("  \n"))
      }
      #cat(Hmisc::latexTranslate(out_docs[doc, "description"]))
      #knitr::knit_print(out_docs[doc, "description"])
      cat(reportRx::sanitizestr(out_docs[doc, "description"]))
      cat("\n\n")
    }
    if(include_ocr){
      if(pandoc_output){
        cat("\n\n")
        cat(paste0("### OCR"))
        cat("\n\n")
      } else {
        cat(paste0("\\subsubsection{OCR}"))
        cat(paste0("  \n"))
      }

      #knitr::knit_print(out_docs[doc, "ocr"])
      cat(reportRx::sanitizestr(out_docs[doc, "ocr"]))
      if(pandoc_output){
        cat("  ")
      } else {
        cat("   \n")
      }
    }
  }
}

```

## Introduction

This vignette covers the process of article classification using machine learning.

```{r message=FALSE, warning=FALSE, echo=FALSE}
library(durhamevp)

## also using tidyverse functions
library(tidyverse)
```

## Get The Training Data (Description Classifications)
For classification on description we will use the manual classification information in the candidate documents table. The code below obtains data and creates the EV_article column from the status information which we want the classifier to emulate. We exclude verbatim repeats (status=3). from the classification set because this text is classified once and we don't want to overweight the particular phrases in these documents. 
```{r, eval=FALSE}
candocs<-get_candidate_documents(status =c("0","1", "2", "4", "5", "6", "7", "8"), include_ocr=FALSE)

candocs$EV_article<-ifelse(candocs$status %in% c("1", "3"), 1, 0)

```

## Get the Data to be Classified 
This is obtained based on joining search parameters to search results. The search parameters (like date and search text) are obtained by:
```{r, eval=FALSE}
all_searches<-get_archivesearches()

```

The results obtained from these search parameters can be obtained either by knowing the search ids which you are interested in in advance, or by finding these via queries. For example the code below finds the 1841 queries on the ten search terms specified:

```{r, eval=FALSE}
initial_1841_searches<-all_searches%>%
  dplyr::select(id, search_text, archive_date_start, archive_date_end) %>%
  filter(archive_date_start>lubridate::ymd("1841-01-01"), archive_date_start<lubridate::ymd("1841-12-31")) %>%
  filter(search_text %in% c("election", "candidate", "party", "husting", "magistrate",
                            "riot", "disturbance", "incident", "mob", "rough", "adjourn",
                            "prison", "police"))

```

These results can then be used to obtain the set of search results with that archive search id:
```{r, eval=FALSE}
res_i_1841<-get_archivesearchresults(archive_search_id = initial_1841_searches$id) 
dim(res_i_1841)
```

Or the search ids can be directly entered if known (for example search ids 228-255 all pertain to one day in 1832):

```{r, eval=FALSE}
res_oneday_1832<-get_archivesearchresults(archive_search_id = c(228:255))

```

This should then be joined to the search parameters:
```{r, eval=FALSE}

res_i_1841 <- res_i_1841 %>%
  left_join(all_searches, by=c("archive_search_id"="id")) %>%
  mutate(std_url = sub("download/", "", url))

res_oneday_1832 <- res_oneday_1832 %>%
  left_join(all_searches, by=c("archive_search_id"="id")) %>%
  mutate(std_url = sub("download/", "", url))

```

# Perform the Classification
The documents can be classified by xgboost. Here we classify the 1841 new data using xgboost. The default options return the subset of the search results which have been classified as Election Violence:
```{r}

select_descript_xgb<-classifier_selection_description(candocs, res_i_1841, classifier_type = "xgboost")

dim(select_descript_xgb)

```

Or by naive Bayes. The below classifies the 1841 searches using naive Bayes:
```{r}
select_descript_nb<-classifier_selection_description(candocs, res_i_1841, classifier_type = "nb")
dim(select_descript_nb)

```

# From Results to Candidate Documents

The results set contains many references to the same document (perhaps with different descriptions). The next step is to identify the unique candidate documents which these results relate to. Add the classification (where this is a subset the classification is always 1)

```{r}
xgb_cand_docs<-get_candidates_fromarchivesearchresults(select_descript_xgb)
knitr::kable(head(xgb_cand_docs[xgb_cand_docs$status!="1"|is.na(xgb_cand_docs$status), c("status", "description")]))

xgb_cand_docs$g_status<-xgb_cand_docs$status
xgb_cand_docs$status<-1

xgb_cand_docs$status_writer<-"xgboost_description"

```
## Save results
```{r, eval=FALSE}
to_csv<-xgb_cand_docs[,c("id", "url", "publication_title", "description", "status", "g_status", "title", "status_writer")]

csv_filename<-gsub(" ", "_", paste0("britishnewspaperarchive_", format(Sys.time(), "%Y_%m_%d_%H_%M_%S"), ".csv"))

write.csv(to_csv, file=csv_filename, row.names = FALSE)
```

## View classification results

```{r, results='asis'}
documents_to_latex(sample_n(select_descript_xgb, 30), include_ocr=FALSE, pandoc_output=TRUE)

```

### 2020-06-11 other_R_code/old vignettes that need cleaning/Event_Clustering_Process.Rmd
broken vignettes moved to a holding folder

---
title: "Event Clustering Process"
author: "Gidon Cohen"
date: "03/09/2019"
output: html_document
vignette: >
  %\VignetteIndexEntry{Election Violence Database Structure}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval=FALSE)
```

## Create Auto Clustering in R as Data Frame

Download coding:
```{r}

evp_data<-get_coding()
assign_coding_to_environment(evp_data)
```

```{r}
er<-event_reports %>%
  mutate(election_start_date=date_to_election(date(dmy(event_start)), election_start_col="dissolution", election_end_col="commencement"),
         election_end_date=date_to_election(date(dmy(event_end)), election_start_col="dissolution", election_end_col="commencement"),
         election = ifelse(election_start_date==election_end_date, election_start_date, "ambiguous"))

er06<-er[er$election=="1906",]
location06<-processed_locations %>% inner_join(er06, by="event_report_id")

_

reg_tv <-function(x){
  # if(!is.na(x)){
  y <- x
    x <- stringr::str_squish(x)
    x <- stringr::str_to_title(x)
    x <- paste0(x, ", UK")

    x[is.na(y)]<- NA

  x
}

locationstocode<-location06 %>%
  group_by(towns_villages) %>%
  mutate(towns_village_reg=reg_tv(towns_villages)) %>%
  group_by(towns_village_reg) %>%
  summarize() %>%
  drop_na()

```

Geocode unique locations
```{r}

locationscoded <- cbind(locationstocode, ggmap::geocode(locationstocode$towns_village_reg))
location06<-location06 %>%
  mutate(towns_village_reg=reg_tv(towns_villages)) %>%
  left_join(locationscoded)

hasloc06 <- drop_na(location06, lat, lon)
unspecificloc06<-filter(location06, is.na(lat)|is.na(lon))
hasloc06_sf<-st_as_sf(hasloc06,  crs = 4326, coords = c("lon", "lat"))

kilodist<- sf::st_distance(hasloc06_sf) %>%
  units::set_units("kilometers") %>%
  as.dist()
geoclusters<-hclust(kilodist)
threshold.in.kilometers <- 5
locationcomp06$geocluster <- cutree(geoclusters, h=threshold.in.kilometers)

```

Subset to specifically identified locations  (has town village lat lon).
Cluster on these

```{r}
loccompdatespec<-locationcomp06 %>%
  mutate(specific_date=date(dmy(event_start))==date(dmy(event_end)) & event_timeframe_quantifier=="during", event_date=date(dmy(event_start))) %>%
  filter(specific_date)

```

Within geographical locations cluster on dates:
```{r}
tc<-loccompdatespec %>%
  st_drop_geometry() %>%
  group_by(geocluster) %>%
  nest()

adddateclust <- function(x, h=8){
  if(nrow(x)<2){
    x$withingeodatecluster<-1
    return(x)
  }
  these_dates<-pull(x, event_date)
  x$withingeodatecluster =  cutree(hclust(dist(these_dates-min(these_dates))), h=h)
  x
}
tc2<-tc %>%
  mutate(data = purrr::map(data, adddateclust)) %>%
  unnest() %>%
  group_by(geocluster, withingeodatecluster) %>%
  mutate(geodatecluster=group_indices())

```

Identify singleton 
```{r}
singletons <- tc2 %>% 
  group_by(geodatecluster) %>% 
  tally() %>% 
  filter(n==1) %>% 
  inner_join(tc2, by="geodatecluster")

```

Autoclusters are non-singleton clusters

```{r}
autoclusters <- tc2 %>% 
  group_by(geodatecluster) %>% 
  tally() %>% 
  filter(n>1) %>% 
  inner_join(tc2, by="geodatecluster")
```

Need to deal with non-specific places:
Identify area where events took place in for non-specific locations (e.g. the county)

## Verification Step: Assign Auto Clusters to User

Create autoclusters on database and store created autocluster_ids in a vector:
```{r cars}
autocluster_ids<-assign_clusters_from_df(tc2)
```

Assign newly created autocluster_ids to a user (e.g. user 3) for verification:
```{r}
assign_autoclusters_to_user(autocluster_ids, 3)

```

## Reallocation Step: Assign Singletons to Clusters

Find event reports of singletons (clusters of size 1 and events not in a cluster)
```{r}
singleton_event_report_ids <- c(1) # need to write code to do this
```

Assign singletons to users for reallocation
```{r pressure}
assign_reallocations_to_user(event_report_ids = singleton_event_report_ids, user_id = 3)
```

## Combination Step: Consider verified clusters for combination

Find verified clusters
```{r}
verified_clusters<-get_verified_clusters()
verified_cluster_ids<-unique(verified_clusters$verified_cluster_id)
some_verified_cluster_ids <- verified_cluster_ids[10:20]
```

Assign verified (and combined) clusters to users for combination
```{r}

assign_verified_clusters_to_user(some_verified_cluster_ids, user_id = 6)
```
